---
title: "analysis new variables and flows"
format: 
  pdf:
    fig_height: 16
    fig_width: 50
    toc: true
    number-sections: true
    colorlinks: true
    toc-depth: 5
    toc-title: Table of Contents
editor_options: 
  chunk_output_type: console
---
# Analysis of data from february qith additional variables and flows
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning = FALSE, message = FALSE)
options(knitr.duplicate.label = "allow")
```
##  Library Charging
```{r}
#| label: library 
#| include: false

setwd("~/Documents/ns-3.45")
gc()
#source(file = "./delay_function.R")
source(file = "./scratch/ninth/real_data.R")
source(file = "./scratch/ninth/variation_generator_function.R")
source(file = "./scratch/ninth/model_function.R")
source(file = "./scratch/ninth/setup_param.R")
source(file = "./scratch/ninth/setup_function.R")

library(akima)  # Pour l'interpolation 2D
library(caret)
library(cluster)
library(cowplot) # Pour combiner les graphiques
library(data.table)
library(dbscan)
library(dplyr) # function distinct
library(e1071)
library(factoextra)
library(FactoMineR) # PCA
library(gganimate) # animated heatmap
library(ggcorrplot) # ggcorrplot
library(ggplot2)
library(ggplot2movies)
library(grid)
library(gridExtra) # grid.arrange 
library(isotree)
#library(magick)
library(mixtools)
library(proxy)
library(plyr)
library("plot3D")# Pour les graphiques 3D
library(plot3Drgl)
library(randomForest)
library(rgl)
library(readr)
library(rpart) 
library(rpart.plot)
library(xgboost) #for fitting the xgboost model
library(zeallot) # %<-% operator

library(latex2exp)

```

## Data charging

```{r}


# evolution of modele
dtf_16 <- fread ("scratch/data/final_data_192.168.186.24_2025-10-22 10:12:11.293604.csv")
dtf_NYevolutionComplete <- dtf_16[V31 == TRUE,]
dtf_Yevolution <- dtf_16[V22 == TRUE & grepl('Mbps', dtf_16$V23, fixed=TRUE)]
dtf_NevolutionComplete <- dtf_16[V22 == FALSE & grepl('Mbps', dtf_16$V23, fixed=TRUE)]
dtf_NevolutionIncomplete <- dtf_16[V22 == FALSE & V28 == TRUE]
colnames(dtf_Yevolution) <- c("nb_packets", "path_length", "nb_detour", "prop_att", 
                      "size_group",  "model", "approach",  "error", "all_err",
                      "no_err", "Recall", "Precision", "F1_score", "simulation_time",
                      "latency", "bandwidth", "data_rate", "parasite_rate", 
                      "meanexp", "parasite_meanexp", "protocol", "do_evolution",
                      "trainonparasite", "trainondetour","trainonpath",
                      "TP", "FN", "FP", "TN", "packet_length", "testattheend", "seed")
colnames(dtf_NevolutionComplete) <- c("nb_packets", "path_length", "nb_detour", "prop_att", 
                      "size_group",  "model", "approach",  "error", "all_err",
                      "no_err", "Recall", "Precision", "F1_score", "simulation_time",
                      "latency", "bandwidth", "data_rate", "parasite_rate", 
                      "meanexp", "parasite_meanexp", "protocol", "do_evolution",
                      "trainonparasite", "trainondetour","trainonpath",
                      "TP", "FN", "FP", "TN", "packet_length", "testattheend", "seed")
colnames(dtf_NevolutionIncomplete) <- c("nb_packets", "path_length", "nb_detour", "prop_att", 
                      "size_group",  "model", "approach",  "error", "all_err",
                      "no_err", "Recall", "Precision", "F1_score", "simulation_time",
                      "latency", "bandwidth", "data_rate", "parasite_rate", 
                      "meanexp", "parasite_meanexp", "protocol", "do_evolution",
                      "TP", "FN", "FP", "TN", "packet_length", "testattheend", "seed",
                      "trainonparasite", "trainondetour","trainonpath")

dtf_Nevolution = rbind(dtf_NevolutionComplete, dtf_NevolutionIncomplete)
dtf_Nevolution <- dtf_Nevolution[seed != "scratch/ninth/2025-10-16_01-53-23"| is.na(seed),]
dtf_Yevolution <- dtf_Yevolution[seed != "scratch/ninth/2025-10-16_01-53-23" | is.na(seed),]

dtf_Yevolution[, nb_packets := as.integer(nb_packets)]
dtf_Yevolution[, path_length := as.integer(path_length)]
dtf_Yevolution[, nb_detour := as.integer(nb_detour)]
dtf_Yevolution[, prop_att := as.numeric(prop_att)]
dtf_Yevolution[, size_group := as.integer(size_group)]
dtf_Yevolution[, F1_score := as.numeric(F1_score)]
dtf_Yevolution[, Precision := as.numeric(Precision)]
dtf_Yevolution[, Recall := as.numeric(Recall)]
dtf_Yevolution[, simulation_time := as.integer(simulation_time)]
dtf_Yevolution[, meanexp := as.numeric(meanexp)]
dtf_Yevolution[, parasite_meanexp := as.numeric(parasite_meanexp)]
dtf_Yevolution[, TP := as.integer(TP)]
dtf_Yevolution[, FN := as.integer(FN)]
dtf_Yevolution[, FP := as.integer(FP)]
dtf_Yevolution[, TN := as.integer(TN)]
dtf_Yevolution[, packet_length := as.integer(packet_length)]
dtf_Yevolution[, testattheend := as.logical(testattheend)]
dtf_Yevolution[, do_evolution := as.logical(do_evolution)]
dtf_Yevolution[, trainondetour := as.integer(trainondetour)]
dtf_Yevolution[, trainonpath := as.integer(trainonpath)]

dtf_Nevolution[, nb_packets := as.integer(nb_packets)]
dtf_Nevolution[, path_length := as.integer(path_length)]
dtf_Nevolution[, nb_detour := as.integer(nb_detour)]
dtf_Nevolution[, prop_att := as.numeric(prop_att)]
dtf_Nevolution[, size_group := as.integer(size_group)]
dtf_Nevolution[, F1_score := as.numeric(F1_score)]
dtf_Nevolution[, Precision := as.numeric(Precision)]
dtf_Nevolution[, Recall := as.numeric(Recall)]
dtf_Nevolution[, simulation_time := as.integer(simulation_time)]
dtf_Nevolution[, meanexp := as.numeric(meanexp)]
dtf_Nevolution[, parasite_meanexp := as.numeric(parasite_meanexp)]
dtf_Nevolution[, TP := as.integer(TP)]
dtf_Nevolution[, FN := as.integer(FN)]
dtf_Nevolution[, FP := as.integer(FP)]
dtf_Nevolution[, TN := as.integer(TN)]
dtf_Nevolution[, packet_length := as.integer(packet_length)]
dtf_Nevolution[, testattheend := as.logical(testattheend)]
dtf_Nevolution[, do_evolution := as.logical(do_evolution)]
dtf_Nevolution[, trainondetour := as.integer(trainondetour)]
dtf_Nevolution[, trainonpath := as.integer(trainonpath)]

to_distinct = c("nb_packets", "prop_att", "size_group", "path_length", 
                "nb_detour", "model", "approach", "simulation_time", 
                "latency", "bandwidth", "data_rate", "parasite_rate", 
                "F1_score", "Recall", "Precision", "TP", "TN", "FP", "FN", 
                "error","all_err","no_err", "meanexp","parasite_meanexp",
                "protocol",  "do_evolution", #"packet_length","testattheend"
                "trainonparasite", "trainondetour", "trainonpath", "seed")
dtf_Yevolution <- dtf_Yevolution[!duplicated(dtf_Yevolution[, ..to_distinct], fromLast = TRUE)]
dtf_Nevolution <- dtf_Nevolution[!duplicated(dtf_Nevolution[, ..to_distinct], fromLast = TRUE)]

# choose here between dtf_Nevolution and dtf_Yevolution
dtf <- dtf_Yevolution[, .(
  F1_score = mean(F1_score, na.rm = TRUE),
  F1_sd = sd(F1_score, na.rm = TRUE),
  F1_ci_lower = mean(F1_score, na.rm = TRUE) - qt(0.975, .N - 1) * sd(F1_score, na.rm = TRUE) / sqrt(.N),
  F1_ci_upper = mean(F1_score, na.rm = TRUE) + qt(0.975, .N - 1) * sd(F1_score, na.rm = TRUE) / sqrt(.N),
  Precision_mean = mean(Precision, na.rm = TRUE),
  Recall_mean = mean(Recall, na.rm = TRUE),
  TP_mean = mean(TP, na.rm = TRUE),
  FP_mean = mean(FP, na.rm = TRUE),
  TN_mean = mean(TN, na.rm = TRUE),
  FN_mean = mean(FN, na.rm = TRUE),
  n_elements = .N
),
by = .(path_length, nb_detour, prop_att, size_group,
       model, approach, simulation_time, latency, bandwidth,
       data_rate, parasite_rate, meanexp, parasite_meanexp,
       protocol,  do_evolution, #testattheend,packet_length, 
       trainonparasite, trainondetour, trainonpath)
]
dtf <- dtf_Nevolution[, .(
  F1_score = mean(F1_score, na.rm = TRUE),
  F1_sd = sd(F1_score, na.rm = TRUE),
  F1_ci_lower = mean(F1_score, na.rm = TRUE) - qt(0.975, .N - 1) * sd(F1_score, na.rm = TRUE) / sqrt(.N),
  F1_ci_upper = mean(F1_score, na.rm = TRUE) + qt(0.975, .N - 1) * sd(F1_score, na.rm = TRUE) / sqrt(.N),
  Precision_mean = mean(Precision, na.rm = TRUE),
  Recall_mean = mean(Recall, na.rm = TRUE),
  TP_mean = mean(TP, na.rm = TRUE),
  FP_mean = mean(FP, na.rm = TRUE),
  TN_mean = mean(TN, na.rm = TRUE),
  FN_mean = mean(FN, na.rm = TRUE),
  n_elements = .N
),
by = .(path_length, nb_detour, prop_att, size_group,
       model, approach, simulation_time, latency, bandwidth,
       data_rate, parasite_rate, meanexp, parasite_meanexp,
       protocol, packet_length, testattheend, do_evolution)
]
```

## Data charging 2
```{r}
#| label: data charging
#| echo: true


# dtf_rate <- fread ('scratch/data/final_data_172.22.216.6_2025-07-23 08:24:22.014863.csv') # parasite variation
# dtf_1 <- fread ('scratch/data/final_data_192.168.186.24_2025-08-27 18:14:27.319005.csv')
# dtf_2 <- fread ('scratch/data/final_data_192.168.186.24_2025-08-29 13:20:09.448879.csv')
# dtf_3 <- fread ("scratch/data/final_data_192.168.186.24_2025-09-01 10:47:03.715916.csv")
# dtf_4 <- fread ("scratch/data/final_data_192.168.186.24_2025-09-04 16:33:59.15041.csv")
# dtf_5 <- fread ("scratch/data/final_data_192.168.186.24_2025-09-04 18:55:38.350686.csv")
# dtf_6 <- fread ("scratch/data/final_data_192.168.186.24_2025-09-04 19:02:47.284461.csv")
# dtf_7 <- fread ("scratch/data/final_data_192.168.186.24_2025-09-04 21:22:14.951459.csv")
# dtf_8 <- fread ("scratch/data/final_data_192.168.186.24_2025-09-09 11:05:38.65594.csv")
# dtf_9 <- fread ("scratch/data/final_data_192.168.186.24_2025-09-10 08:02:26.074772.csv")
# dtf_10 <- fread ("scratch/data/final_data_192.168.186.24_2025-09-15 09:46:30.430531.csv")
# dtf_11 <-fread ("scratch/data/final_data_172.22.216.19_2025-09-15 10:26:28.387563.csv")
# dtf_12 <- fread ("scratch/data/final_data_192.168.186.24_2025-09-16 09:14:36.447012.csv")
# dtf_13 <- fread ("scratch/data/final_data_192.168.186.24_2025-09-19 15:34:25.061096.csv")
# dtf_14 <- fread ("scratch/data/final_data_192.168.186.24_2025-09-23 14:11:04.494716.csv")
# dtf_15 <-fread ("scratch/data/final_data_192.168.186.24_2025-09-25 12:36:21.002151.csv")
# dtf_path_0_60 <- fread ("scratch/data/final_data_192.168.186.24_2025-09-30 09:44:50.921539.csv")
# 
# dtf <- rbind(dtf_rate, dtf_1, dtf_2, dtf_3, dtf_4, dtf_5, 
#              dtf_6, dtf_7, dtf_8, dtf_9, dtf_10, 
#              dtf_11, dtf_12, dtf_13, dtf_14, dtf_15)
# dtf = dtf_path_0_60
# 
# dtf_17 <- fread("scratch/data/final_data_192.168.186.24_2025-10-01 11:32:59.570429.csv")
# dtf_18 <- fread("scratch/data/final_data_192.168.186.24_2025-10-02 10:43:23.573229.csv")
# dtf_19 <- fread ("scratch/data/final_data_192.168.186.24_2025-10-02 12:01:41.465127.csv")
# dtf_20 <- fread ("scratch/data/final_data_192.168.186.24_2025-10-02 13:59:50.068554.csv")
# dtf_21 <- fread ("scratch/data/final_data_192.168.186.24_2025-10-03 07:41:27.889326.csv")
# dtf_22 <- fread ("scratch/data/final_data_192.168.186.24_2025-10-06 10:14:56.247532.csv")
# dtf_23 <- fread ("scratch/data/final_data_192.168.186.24_2025-10-07 10:24:53.668964.csv")
# dtf_24 <- fread ("scratch/data/final_data_192.168.186.24_2025-10-07 15:54:32.815327.csv")
# dtf_25 <- fread ("scratch/data/final_data_192.168.186.24_2025-10-07 21:04:46.544561.csv")
# 
# 
# 
# dtf_26 <- fread ("scratch/data/final_data_192.168.186.24_2025-10-08 11:10:18.330061.csv")
# dtf_27 <- fread ("scratch/data/final_data_192.168.186.24_2025-10-08 13:21:12.673543.csv")
# dtf_28 <- fread ("scratch/data/final_data_192.168.186.24_2025-10-08 16:10:27.257053.csv")
# dtf_29 <- fread ("scratch/data/final_data_192.168.186.24_2025-10-09 08:21:13.438393.csv")
# dtf_30 <- fread ("scratch/data/final_data_192.168.186.24_2025-10-10 08:54:16.704332.csv")
# 
# 
# 
# 
# dtf_31 <- fread ("scratch/data/final_data_192.168.186.24_2025-10-10 11:35:59.285026.csv")
# dtf_32 <- fread ("scratch/data/final_data_192.168.186.24_2025-10-10 13:16:01.111335.csv")


# dtf_33 <- fread ("scratch/data/final_data_192.168.186.24_2025-10-14 08:57:42.038733.csv")
# dtf_34 <- fread ("scratch/data/final_data_192.168.186.24_2025-10-14 16:11:15.130407.csv")
# 
# 
# dtf_35 <- fread ("scratch/data/final_data_192.168.186.24_2025-10-14 17:44:49.694395.csv")
# dtf_36 <- fread ("scratch/data/final_data_192.168.186.24_2025-10-15 09:29:36.440951.csv")
# dtf_37 <- fread ("scratch/data/final_data_192.168.186.24_2025-10-15 13:54:03.22395.csv")
#dtf_38 <- fread ("scratch/data/final_data_192.168.186.24_2025-10-15 16:54:37.169542.csv")
#dtf_39 <- fread ("scratch/data/final_data_192.168.186.24_2025-10-15 22:01:53.369243.csv")
#dtf_40 <- fread ("scratch/data/final_data_192.168.186.24_2025-10-16 09:09:46.037888.csv")

#dtf_41 <- fread ("scratch/data/final_data_192.168.186.24_2025-10-16 16:35:46.569835.csv")
#dtf_42 <- fread ("scratch/data/final_data_192.168.186.24_2025-10-17 09:11:07.912923.csv")
#dtf_16 <- fread ("scratch/data/final_data_192.168.186.24_2025-10-17 11:36:06.986682.csv")


# new variables
#dtf_16 <- fread ("scratch/data/final_data_192.168.186.24_2025-10-21 09:32:19.869604.csv")
#dtf_16 <- fread ("scratch/data/final_data_192.168.186.24_2025-10-21 17:41:22.062814.csv")
#dtf_16 <- fread ("scratch/data/final_data_192.168.186.24_2025-10-21 18:10:15.203818.csv")
# 
# 
# # evolution of modele
#dtf_16 <- fread ("scratch/data/final_data_192.168.186.24_2025-10-23 08:51:58.594425.csv")

## new size of flow
#dtf_16 <- fread ("scratch/data/final_data_192.168.186.24_2025-12-08 12:21:02.524897.csv")

# training on several scenarios


#dtf_16 <- fread ("scratch/data/final_data_192.168.186.24_2025-10-30 21:32:53.853949.csv")
#dtf_16 <- fread ("scratch/data/final_data_192.168.186.24_2025-11-13 10:36:28.641658.csv")


# new size of flow
dtf_15 <- fread ("scratch/data/final_data_192.168.186.24_2025-12-15 15:01:43.799765.csv")
dtf_15 <- dtf_15[-1]
colnames(dtf_15) <- unlist(dtf_15[1])
dtf_15 <- dtf_15[-1]
dtf_15$comment = "basic"
dtf_15$dataset = "dtf_15"

# recapitulatif : 
dtf_19 <- fread ("scratch/data/final_data_192.168.186.24_2025-12-19 17:12:45.583271.csv")
dtf_19 <- dtf_19[-1]
colnames(dtf_19) <- unlist(dtf_19[1])
dtf_19 <- dtf_19[-1]
dtf_19$comment = "basic"
dtf_19$dataset = "dtf_19"


# comment: same_size_dataset: 342, 27, 9
dtf_17 <- fread ("scratch/data/final_data_192.168.186.24_2026-01-06 15:30:02.251972.csv")
dtf_17 <- dtf_17[-1]
colnames(dtf_17) <- unlist(dtf_17[1])
dtf_17 <- dtf_17[-1]
dtf_17$dataset = "dtf_17"

# comment: same_size_dataset: 27, 9
#dtf_18 <- fread ("scratch/data/final_data_192.168.186.24_2026-01-09 14:49:32.267192.csv")
#dtf_18 <- fread ("scratch/data/final_data_192.168.186.24_2026-01-14 12:00:23.671264.csv")
dtf_18 <- fread ("scratch/data/final_data_192.168.186.24_2026-01-16 15:20:02.999539.csv")
dtf_18 <- dtf_18[-1]
colnames(dtf_18) <- unlist(dtf_18[1])
dtf_18 <- dtf_18[-1]
dtf_18$dataset = "dtf_18"

# # redo from scratch
# dtf_16 <- fread ("scratch/data/final_data_192.168.186.24_2026-01-28 10:21:44.857221.csv")
dtf_20 <- fread ("scratch/data/final_data_192.168.186.24_2026-03-11 10:22:26.608198.csv")
dtf_20 <- dtf_20[-1]
colnames(dtf_20) <- unlist(dtf_20[1])
dtf_20 <- dtf_20[-1]
dtf_20$dataset = "dtf_20"

# # redo from scratch2
dtf_21 <- fread ("scratch/data/final_data_192.168.186.24_2026-04-15 09:01:24.217375.csv")
dtf_21 <- dtf_21[-1]
colnames(dtf_21) <- unlist(dtf_21[1])
dtf_21 <- dtf_21[-1]
dtf_21$dataset = "dtf_21"

# # optimized version with Claude
dtf_22 <- fread ("scratch/data/final_data_192.168.186.24_2026-05-04 10:32:28.385126.csv")
dtf_22 <- dtf_22[-1]
colnames(dtf_22) <- unlist(dtf_22[1])
dtf_22 <- dtf_22[-1]
dtf_22$dataset = "dtf_22"

# new merge file optimized with claude
dtf_23 <- fread ("scratch/data/final_data_192.168.186.24_20260512_102457.csv")
dtf_23$dataset = "dtf_23"
dtf_23[comment == "basic2", comment := "basic"]

# new NS3 configuration for parasite flows
dtf_24 <- fread ("scratch/data/final_data_192.168.186.24_20260520_171616.csv")
dtf_24$dataset = "dtf_24"
dtf_24[comment == "basic2", comment := "basic"]

# new NS3 configuration for parasite flows and corect training parasite rate
dtf_25 <- fread ("scratch/data/final_data_192.168.186.24_20260611_105805.csv")
dtf_25$temporal_cov = TRUE
dtf_25$cross_seed = FALSE
dtf_25[, FPR := FP / (FP + TN)]
dtf_25$feature_set = "full"
dtf_25$n_features_reduced = 0
dtf_25$dataset = "dtf_25"
dtf_25[comment == "basic2", comment := "basic"]

# final
dtf_16 <- fread ("scratch/data/final_data_192.168.186.24_20260724_114823.csv")
dtf_16$temporal_cov = TRUE
dtf_16$cross_seed = FALSE
dtf_16[, FPR := FP / (FP + TN)]
dtf_16$feature_set = "full"
dtf_16$n_features_reduced = 0
dtf_16$dataset = "dtf_16"
dtf_16[comment == "basic2", comment := "basic"]


dtf_26 <- fread ("scratch/data/final_data_192.168.186.24_20260727_161651.csv")
dtf_26$dataset = "dtf_26"
dtf_26$feature_set = "full"
dtf_26$n_features_reduced = 0
dtf_26[comment == "basic2", comment := "basic"]

dtf_27 <- fread ("scratch/data/final_data_192.168.186.24_20260730_185158.csv")
dtf_27$dataset = "dtf_27"
dtf_27[comment == "basic2", comment := "basic"]
# 
dtf_tmp <- rbind(#dtf_15, dtf_19, dtf_17, dtf_18, 
                 #dtf_20, dtf_21, dtf_22, dtf_23, dtf_24, 
                 dtf_25, 
                 dtf_16
                 #,dtf_26
                 , dtf_27) #, dtf_17 dtf_18 #
rm(dtf_15, dtf_19, dtf_17, dtf_18, dtf_20, dtf_21, dtf_22, dtf_23, dtf_24)
gc()
dtf_16 <- dtf_tmp
rm(dtf_tmp)
dtf_16[, nb_packets := as.integer(nb_packets)]
dtf_16[, path_length := as.integer(path_length)]
#dtf_16[, nb_detour := as.integer(nb_detour)]
dtf_16[, prop_att := as.numeric(prop_att)]
dtf_16[, size_group := as.integer(size_group)]
dtf_16[, F1_score := as.numeric(F1_score)]
dtf_16[, Precision := as.numeric(Precision)]
dtf_16[, Recall := as.numeric(Recall)]
dtf_16[, simulation_time := as.integer(simulation_time)]
dtf_16[, meanexp := as.numeric(meanexp)]
dtf_16[, parasite_meanexp := as.numeric(parasite_meanexp)]
dtf_16[, TP := as.integer(TP)]
dtf_16[, FN := as.integer(FN)]
dtf_16[, FP := as.integer(FP)]
dtf_16[, TN := as.integer(TN)]
dtf_16[, packet_length := as.integer(packet_length)]
dtf_16[, testattheend := as.logical(testattheend)]
dtf_16[, do_evolution := as.logical(do_evolution)]
#dtf_16[, trainondetour := as.integer(trainondetour)]
dtf_16[, trainonpath := as.integer(trainonpath)]
#dtf_16[, packet_length := as.numeric(as.character(packet_length)]
dtf_16[, directory := basename(dirname(seed))]

str(dtf_16)
# tmp <- dtf_16[, .(mean_F1_score = mean(F1_score)), by = c("path_length", "nb_detour", 
#                                                    "prop_att", "size_group", 
#                                                    "model", "approach", 
#                                                    "simulation_time", "latency", 
#                                                    "bandwidth", "data_rate", 
#                                                    "parasite_rate", "meanexp", 
#                                                    "parasite_meanexp", "protocol", 
#                                                    "packet_length", "testattheend"
#                                                    )]
dtf_16 = distinct(dtf_16)
# to_distinct = c("prop_att", "size_group", "path_length", "nb_detour", 
#                 "model", "approach", "simulation_time", "latency", "bandwidth", 
#                 "data_rate", "parasite_rate", "meanexp", "parasite_meanexp",
#                 "protocol", "packet_length", "testattheend", "do_evolution",
#                 "trainonparasite", "trainondetour", "trainonpath",
#                 "seed", "directory",
#                 "FPR", "temporal_cov", "cross_seed") #
to_distinct = c(#"nb_packets", 
                "prop_att", "size_group", "path_length", 
                "nb_detour", "model", "approach", "simulation_time", 
                "latency", "bandwidth", "data_rate", "parasite_rate", 
                #"F1_score", "Recall", "Precision", "TP", "TN", "FP", "FN", 
                #"error","all_err","no_err", 
                "meanexp","parasite_meanexp",
                "protocol", "packet_length","testattheend", "do_evolution", 
                "trainonparasite", "trainondetour", "trainonpath", "seed", "directory",
                #"FPR", 
                "temporal_cov", "cross_seed", "feature_set"
                #, "n_features_reduced"
                ) #
dtf_16 <- dtf_16[!duplicated(dtf_16[, ..to_distinct], fromLast = TRUE)]
#dtf_16[is.na(F1_score) & TP == 0, F1_score := 0]

dtf_16 <- dtf_16[seed != "scratch/ninth/2025-10-16_13-10-05",]
dtf_16 <- dtf_16[seed != "scratch/ninth/2025-10-16_01-53-23",]
dtf_16 <- dtf_16[as.POSIXct(sub(".*/([0-9]{4}-[0-9]{2}-[0-9]{2}_[0-9]{2}-[0-9]{2}-[0-9]{2})$", "\\1", seed),
                              format = "%Y-%m-%d_%H-%M-%S") <
                  as.POSIXct("2025-10-16_11-15-00", format = "%Y-%m-%d_%H-%M-%S") |
                   as.POSIXct(sub(".*/([0-9]{4}-[0-9]{2}-[0-9]{2}_[0-9]{2}-[0-9]{2}-[0-9]{2})$", "\\1", seed),
                              format = "%Y-%m-%d_%H-%M-%S") >
                  as.POSIXct("2025-10-17_13-30-00", format = "%Y-%m-%d_%H-%M-%S")]

seuil <- as.POSIXct("2026-04-21_11-30-00", format = "%Y-%m-%d_%H-%M-%S")
dtf_16 <- dtf_16[
  !grepl("/tenth/", seed) |
  as.POSIXct(
    sub(".*/tenth/([0-9]{4}-[0-9]{2}-[0-9]{2}_[0-9]{2}-[0-9]{2}-[0-9]{2})$", "\\1", seed),
    format = "%Y-%m-%d_%H-%M-%S"
  ) > seuil
]

seuil <- as.POSIXct("2026-05-12_11-00-00", format = "%Y-%m-%d_%H-%M-%S")
dtf_16 <- dtf_16[
  !grepl("/eleventh/", seed) |
  as.POSIXct(
    sub(".*/eleventh/([0-9]{4}-[0-9]{2}-[0-9]{2}_[0-9]{2}-[0-9]{2}-[0-9]{2})$", "\\1", seed),
    format = "%Y-%m-%d_%H-%M-%S"
  ) > seuil
]


list_repertory_short = c("scratch/ninth/2026-01-23_07-32-00",
                         "scratch/ninth/2026-01-23_08-16-58",
                         "scratch/ninth/2026-01-23_09-01-51",
                         "scratch/ninth/2026-01-23_05-12-11",
                         "scratch/ninth/2026-01-23_06-45-47",
                         "scratch/ninth/2026-01-23_05-59-10",
                         "scratch/ninth/2026-01-23_01-55-46",
                         "scratch/ninth/2026-01-23_02-45-00",
                         "scratch/ninth/2026-01-23_03-34-19",
                         "scratch/ninth/2026-01-23_04-23-28",
                         "scratch/ninth/2026-01-23_01-05-13",
                         "scratch/ninth/2026-01-23_00-13-48",
                         "scratch/ninth/2026-01-22_21-37-00",
                         "scratch/ninth/2026-01-22_23-21-49",
                         "scratch/ninth/2026-01-22_16-43-07",
                         "scratch/ninth/2026-01-22_18-43-45",
                         "scratch/ninth/2026-01-22_19-41-43",
                         "scratch/ninth/2026-01-22_22-29-56",
                         "scratch/ninth/2026-01-22_15-39-44",
                         "scratch/ninth/2026-01-22_14-37-43",
                         "scratch/ninth/2026-01-22_11-29-14",
                         "scratch/ninth/2026-01-22_12-33-57",
                         "scratch/ninth/2026-01-22_13-36-55",
                         "scratch/ninth/2026-01-22_10-24-18",
                         "scratch/ninth/2026-01-22_06-41-40",
                         "scratch/ninth/2026-01-22_05-30-26",
                         "scratch/ninth/2026-01-22_04-17-43",
                         "scratch/ninth/2026-01-22_17-45-20",
                         "scratch/ninth/2026-01-22_03-03-07",
                         "scratch/ninth/2026-01-22_20-40-07",
                         "scratch/ninth/2026-01-22_00-23-18",
                         "scratch/ninth/2026-01-22_09-14-25",
                         "scratch/ninth/2026-01-22_07-52-00",
                         "scratch/ninth/2026-01-21_23-01-33",
                         "scratch/ninth/2026-01-21_18-39-20",
                         "scratch/ninth/2026-01-21_21-38-06",
                         "scratch/ninth/2026-01-22_01-40-47",
                         "scratch/ninth/2026-01-21_20-10-54",
                         "scratch/ninth/2026-01-21_16-57-39",
                         "scratch/ninth/2026-02-26_21-30-39",
                         "scratch/ninth/2026-01-23_09-47-22",
                         "scratch/ninth/2026-01-21_05-28-19"#,
#### ATTENTION ICI A REMTTRE QUAND ANALYSES REFAITES
                         #"scratch/eleventh/2026-05-19_13-17-41",
                         #"scratch/twelveth/2026-05-20_16-35-10"
)
set_seed_short = paste0("/home/dochagnon/ns-3.45/", list_repertory_short)
dtf_16 <- dtf_16[!(seed %in% set_seed_short),]
# put back if want to do mean again
dtf <- dtf_16[, c(lapply(.SD, mean, na.rm = TRUE), .(n_elements = .N)), #, na.rm = TRUE
              by = .(path_length, nb_detour, prop_att, size_group,
                     model, approach, simulation_time, latency, bandwidth,
                     data_rate, parasite_rate, meanexp, parasite_meanexp,
                     protocol, packet_length, testattheend),
              .SDcols = c("F1_score", "Precision", "Recall")]

dtf <- dtf_16[, .(
  F1_score = mean(F1_score, na.rm = TRUE),
  F1_sd = sd(F1_score, na.rm = TRUE),
  F1_ci_lower = mean(F1_score, na.rm = TRUE) - qt(0.975, .N - 1) * sd(F1_score, na.rm = TRUE) / sqrt(.N),
  F1_ci_upper = mean(F1_score, na.rm = TRUE) + qt(0.975, .N - 1) * sd(F1_score, na.rm = TRUE) / sqrt(.N),
  Precision_mean = mean(Precision, na.rm = TRUE),
  Recall_mean = mean(Recall, na.rm = TRUE),
  TP_mean = mean(TP, na.rm = TRUE),
  FP_mean = mean(FP, na.rm = TRUE),
  TN_mean = mean(TN, na.rm = TRUE),
  FN_mean = mean(FN, na.rm = TRUE),
  n_elements = .N
),
by = .(path_length, nb_detour, prop_att, size_group,
       model, approach, simulation_time, latency, bandwidth,
       data_rate, parasite_rate, meanexp, parasite_meanexp,
       protocol, packet_length, testattheend, do_evolution
       ,trainonparasite, trainondetour, trainonpath
       )
]

# # put back if you don't want ot do mean
# to_distinct = c("prop_att", "size_group", "path_length", "nb_detour", "model", "approach", "simulation_time", "latency", "bandwidth", "data_rate", "parasite_rate")
# dtf <- unique(dtf_16, by = to_distinct,  fromLast = TRUE)

dtf_boxplot <- dtf_16
dtf[model %in% c("THRESHOLD", "INTERVAL_DELAY") , approach := "baseline"] 
dtf_boxplot[model %in% c("THRESHOLD", "INTERVAL_DELAY") , approach := "baseline"] 
dtf_ = distinct(dtf)
dtf_boxplot_ = distinct(dtf_boxplot)
## remove duplicate
to_distinct2 = c("prop_att", "size_group", "path_length", "nb_detour",
                "model", "approach", "simulation_time", "latency", "bandwidth",
                "data_rate", "parasite_rate", "meanexp", "parasite_meanexp",
                "protocol", "packet_length", "testattheend", "do_evolution",
                "trainonparasite", "trainondetour", "trainonpath"
                ) #
#doublons_complets <- dtf_[duplicated(dtf_[to_distinct]) | duplicated(dtf_[to_distinct], fromLast = TRUE), ]
#doublons_single <- dtf_[duplicated(dtf_[to_distinct]), ]
# sans_doublons <- anti_join(dtf_, doublons_single)#, by = to_distinct)
# dtf_ = sans_doublons
# dtf_ = distinct(dtf_)
# rm(doublons_complets, doublons_single, sans_doublons)


dtf_[, row_id := .I]
setorder(dtf_, -row_id)  # ordre décroissant pour prioriser les dernières lignes
dtf_ <- dtf_[!duplicated(dtf_[, ..to_distinct2], fromLast = TRUE)]
dtf_[, row_id := NULL]

# to_distinct = c("prop_att", "size_group", "path_length", "nb_detour", 
#                 "model", "approach", "simulation_time", "latency", "bandwidth", 
#                 "data_rate", "parasite_rate", "meanexp", "parasite_meanexp",
#                 "protocol", "packet_length", "testattheend", "do_evolution",
#                 "trainonparasite", "trainondetour", "trainonpath",
#                 "seed", "directory",
#                 "FPR", "temporal_cov", "cross_seed") #
dtf_boxplot_[, row_id := .I]
setorder(dtf_boxplot_, -row_id)  # ordre décroissant pour prioriser les dernières lignes
dtf_boxplot_ <- dtf_boxplot_[!duplicated(dtf_boxplot_[, ..to_distinct], fromLast = TRUE)]
dtf_boxplot_[, row_id := NULL]




min_att = min (dtf_$prop_att)
max_att = min(max(dtf_$prop_att))
#max_detour = max(dtf_$nb_detour) #10 #min(max(dtf_$nb_detour), max(dtf_pkt_3var$nb_detour))
min_path = min(dtf_$path_length)
max_path = max(dtf_$path_length) #3 #min(max(dtf_$path_length), max(dtf_pkt_3var$path_length))
prop_att = unique (dtf_$prop_att)

nb_packets = unique(dtf_$nb_packets)
dtf_[, group_id := (floor(size_group / 9) *9)]
dtf_[group_id == 0, group_id := 1]#dtf<- dtf[dtf$nb_packets == nb_packets,]
dtf_[,parasite_rate := factor(parasite_rate, levels = ordered_parasite_rate, ordered = TRUE)]

dtf_boxplot_[, group_id := (floor(size_group / 9) *9)]
dtf_boxplot_[group_id == 0, group_id := 1]#dtf<- dtf[dtf$nb_packets == nb_packets,]
dtf_boxplot_[,parasite_rate := factor(parasite_rate, levels = ordered_parasite_rate, ordered = TRUE)]
```
### Available parameters:

<!-- ```{r} -->
<!-- #| echo: false -->
<!-- keep = c("model", "prop_att", "size_group", "path_length", "nb_detour", "nb_packets", "group_id", "parasite_rate", "simulation_time") -->
<!-- # tmp_unique = apply(dtf_[,keep], 2, unique) -->
<!-- # tmp_unique = lapply(tmp_unique, sort) -->
<!-- tmp_unique <- dtf_[, lapply(.SD, function(x) sort(unique(x))), .SDcols = keep] -->
<!-- print(tmp_unique) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- # tmp_count = apply(dtf_[,keep], 2, count) -->
<!-- tmp_count <- dtf_[, lapply(.SD, function(x) count(x)), .SDcols = keep] -->
<!-- print(tmp_count) -->
<!-- ``` -->

<!-- ### regourpe size_group -->
<!-- ```{r} -->
<!-- str(dtf_$size_group) -->
<!-- dtf_ -->
<!-- ``` -->


### select specific data
```{r}
simtime_range = unique (dtf_$simulation_time)
nb_packets_range = unique(dtf_$nb_packets)

# dtf <- dtf_[dtf_$nb_detour <= max_detour,]
# dtf <- dtf[dtf$path_length <= max_path,]
# dtf <- dtf[dtf$prop_att %in% prop_att,]
# dtf <- dtf[dtf$nb_packets %in% nb_packets_range,]
# dtf <- dtf[dtf$size_group <= max_flow,]
select_detour <- c("0_1_3_5_7_9", "0", "1", "2", "3", "4","5","6", "7","8", "9")
#select_detour <- c("1_3", "1", "3")
select_detour <- seq(0,10,1)
dtf <- dtf_[
  #nb_detour <= max_detour &
  #nb_detour %in% select_detour &
    path_length <= max_path &
    prop_att %in% prop_att &
    size_group <= max_flow  
    & simulation_time == 60
  #& do_evolution == T
  & nb_packets >= 500000
]
dtf_flow <- dtf


dtf_boxplot <- dtf_boxplot_[
  #nb_detour <= max_detour &
  #nb_detour %in% select_detour &
    path_length <= max_path &
    prop_att %in% prop_att &
    size_group <= max_flow  
    & simulation_time == 60
    #& nb_packets >= 500000
  #& do_evolution == T
]
dtf_flow_boxplot <- dtf_boxplot
#dtf_flow[, nb_detour := as.integer(nb_detour)]
```

<!-- ### Available parameters: -->
<!-- ```{r} -->
<!-- #| echo: false -->
<!-- keep = c("model", "prop_att", "size_group", "path_length", "nb_detour", "nb_packets", "group_id", "parasite_rate", "simulation_time") -->
<!-- tmp_unique <- dtf[, lapply(.SD, function(x) sort(unique(x))), .SDcols = keep] -->
<!-- print(tmp_unique) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- tmp_count <- dtf[, lapply(.SD, function(x) count(x)), .SDcols = keep] -->
<!-- print(tmp_count) -->
<!-- ``` -->


### sperate data by flow and data by packet
```{r}

par(mar = c(0.5, 0,3, 0))
```


<!-- ```{r} -->
<!-- seperate_dtf_flow_by_simtime <- function(sim) -->
<!-- { -->
<!--   return (dtf_flow[simulation_time == sim]) -->
<!-- } -->

<!-- dtf_flow_simtime = lapply(simtime_range, FUN = seperate_dtf_flow_by_simtime) -->
<!-- names(dtf_flow_simtime) <- simtime_range -->
<!-- dtf_flow <- dtf_flow_simtime$`60` -->
<!-- size_group_max <- function(nb_packets) -->
<!-- { -->
<!--   tmp_size_group_prop = round((prop_att * nb_packets)) -->
<!--   tmp_size_group_inf10000 = which(tmp_size_group_prop <= max_flow) -->

<!--   tmp_comp_size_group_prop = if (length(tmp_size_group_inf10000) < length(tmp_size_group_prop)){ -->
<!--     c(tmp_size_group_prop[tmp_size_group_inf10000],  -->
<!--       round(seq.int (max(tmp_size_group_prop[tmp_size_group_inf10000]) + 100, max_flow, length.out =5))) -->
<!--   } else { -->
<!--     tmp_size_group_prop -->
<!--   } -->
<!--   size_group <- c(round(seq.int (1, (min(prop_att) * nb_packets)-1, length.out =5)), tmp_comp_size_group_prop, -1) -->

<!--   return (size_group) -->
<!-- } -->


<!-- size_group_by_nb_packets = sapply(nb_packets_range,FUN = size_group_max) -->
<!-- names(size_group_by_nb_packets)= nb_packets_range -->
<!-- ``` -->


### Get model information
```{r}
model_info <- fread("scratch/data/_model_info.csv")
model_info <- distinct(model_info)
model_info <- model_info[-2]

tmp1<- model_info[model == "SVM" 
                 & trainondetour == "5"
                 & group == "9"
                 #& trainonparasite == "60Mbps"
                 & nb_hops == "0"
                 & parasite_rate == "60Mbps"
                 & do_evolution == T]
tmp2<- model_info[model == "SVM" 
                 & trainondetour == nb_att
                 & group == "9"
                 #& trainonparasite == "60Mbps"
                 & nb_hops == "0"
                 & parasite_rate == "60Mbps"]
tmp_F <- tmp2[do_evolution == "FALSE"]
tmp_T<- tmp2[do_evolution == "TRUE"]

tmp<- model_info[model == "SVM" 
                 & trainondetour == "0"
                 & group == "9"
                 #& trainonparasite == "60Mbps"
                 & nb_hops == "0"
                 & parasite_rate == "60Mbps"]
tmp_F <- tmp[do_evolution == "FALSE"]
tmp_T<- tmp[do_evolution == "TRUE"]
```


## Description

```{r}
summary(dtf)
str(dtf)

summary(dtf_flow)
str(dtf_flow)
```

### FRP false positive rate
```{r}
#dtf_flow_boxplot[, fpr := FP / (FP + TN)]

tmp <- dtf_flow_boxplot[
  path_length == 0 & nb_detour == 0 & parasite_rate == "120Mbps" & size_group == 9 & trainondetour == 0 & do_evolution == FALSE & directory == "eleventh",]
recap_fpr <- dtf_flow_boxplot[
  path_length == 0 & nb_detour == 0 & parasite_rate == "120Mbps" 
  & size_group == 9 & trainondetour == 0 & do_evolution == FALSE 
  & directory == "eleventh" & temporal_cov == F & cross_seed == F,
  .(fpr_med = median(FPR, na.rm = TRUE),
    fpr_q1  = quantile(FPR, .25, na.rm = TRUE),
    fpr_q3  = quantile(FPR, .75, na.rm = TRUE),
    n_runs  = .N),
  by = model][order(model)]
print(recap_fpr)


```


## function de heatmap 
```{r}
# Boucle pour générer les graphiques
automate_heatmaps_nofct <- function(data, x, y, score,  facet, by_combi, output_dir = "heatmaps") { #fill = score
  # Créez un dossier pour enregistrer les graphiques
  if (!dir.exists(output_dir)) {
    dir.create(output_dir)
  }
  # Assurer que les symboles sont gérés proprement
  x_col <- deparse(substitute(x))
  y_col <- deparse(substitute(y))
  facet_col <- deparse(substitute(facet))
  by_combi_col <- deparse(substitute(by_combi))
  
  # Liste des combinaisons uniques de paramètres
  # combinations <- data %>%
  #   distinct(model, !!ensym(by_combi))
  combinations <- unique(data[, .(model, get(by_combi))])
  setnames(combinations, "V2", by_combi)
  
  data_type = "flows"
  # Générer une heatmap pour chaque combinaison
  for (i in 1:nrow(combinations)) {
    current <- combinations[i, ]
    dyn_title <- paste0("\n### ", by_combi, ": ", current[[by_combi]], "\n\n")
    cat("\n### ", by_combi, ": ", current[[by_combi]], "\n\n", sep = "")
    for (fill in score)
    {
      fill_col <- deparse(substitute(fill))
      # Filtrer les données pour la combinaison actuelle
      # to_plot <- data %>%
      #   filter(model == current$model, 
      #          #score == current$score, 
      #          !!sym(by_combi) == current[[by_combi]])
      to_plot <- data[model == current$model & !sym(by_combi) == current[[by_combi]]]
      
      # Définir le titre
      title <- paste0("Heatmap for Model: ", current$model, 
                      ", Score: ", fill, 
                      ", ",by_combi,": ", current[[by_combi]], " \ndepending on ", facet)
      
      # Créer la heatmap
      g <- ggplot(to_plot, aes(x = !!ensym(x), y = !!ensym(y), fill = !!ensym(fill))) +
        geom_tile() +
        scale_fill_gradient(low = "lightgrey", high = "#619cff", limits = c(0, 1)) +
        facet_wrap(vars(!!ensym(facet))) +
        theme_minimal() +
        ggtitle(title)
      
      # Sauvegarder la heatmap
      filename <- paste0(output_dir, "/heatmap_", 
                         current$model, "_", 
                         fill, "_",by_combi, 
                         current[[by_combi]],"_", facet, ".png")
      
      print(g)
      ggsave(filename, plot = g, width = 16, height = 12, dpi=300)
      
      if (length(score) == 1)
      {
        return (g)
      }
    }
  }
}
```

## isolation forest
### heatmap in 3D 
#### X cube coloré
```{r}
x= "path_length"
y = "prop_att"
z = "F1_score"
colvar = "nb_detour"
group = 1
my_model = "ISOF"
par(mar = c(0.5, 0,3, 0))
plot_flow <- dtf_flow[model == my_model,]

plot_pkt <- plot_flow[group_id == 1,]
plot_flow <- plot_flow[group_id == group,]

min_score = min(plot_pkt[[z]], plot_flow[[z]], na.rm = TRUE)
max_score = max(plot_pkt[[z]], plot_flow[[z]], na.rm = TRUE)
min_detour = min(plot_pkt[[colvar]], plot_flow[[colvar]], na.rm = TRUE)
max_detour = max(plot_pkt[[colvar]], plot_flow[[colvar]], na.rm = TRUE)


theta = 220
phi = 00
cex = 1
# set the plotting area into a 1*2 array 
par(mfrow = c(2,2)) 
par(mar = c(0.5, 0,3, 0))



### data with packet repartition and several more variables ####
# with (plot_pkt, scatter3D(path_length, prop_att, F1_score, colvar = nb_detour, clab = "nb_detour", 
#                           pch = 19, cex = cex, bty = "b2", 
#                           theta = theta, phi = phi, 
#                           main = paste0("Heatmap for F1_score with size_group=", unique (plot_pkt$size_group), 
#                                         "\n for a repartion by packet with more varibales"), 
#                           xlab = "path_length",
#                           ylab ="prop_att", zlab = "F1_score", ticktype = "detailed"
#                           , clim = c(min_detour, max_detour), zlim = c(min_score, max_score)
# ),
# type= "l",
# colkey = list(addlines = TRUE)
# # , nticks = 10
# )
with (plot_pkt, scatter3D(
  x = get(x), y = get(y), z = get(z), 
  colvar = get(colvar), clab = colvar, 
  pch = 19, cex = cex, bty = "b2", 
  theta = theta, phi = phi, 
  main = paste0(my_model, ": ", z, " \nwith size_group=", unique (group_id)), 
  xlab = x, ylab =y, zlab = z, 
  ticktype = "detailed"
  , clim = c(min_detour, max_detour), 
  zlim = c(min_score, max_score)
),
type= "l",
colkey = list(addlines = TRUE)
# , nticks = 10
)
#plotrgl()

### data with flow repartition and several more variables ####
# with (plot_flow, scatter3D(path_length, prop_att, F1_score, colvar = nb_detour, clab = "nb_detour", 
#                            pch = 19, cex = cex, bty = "b2", 
#                            theta = theta, phi = phi, 
#                            main = paste0("Heatmap for F1_score with size_group=", unique (size_group), 
#                                          "\n for a repartion by flow with more varibales"), 
#                            xlab = "path_length",
#                            ylab ="prop_att", zlab = "F1_score", ticktype = "detailed"
#                            , clim = c(min_detour, max_detour), zlim = c(min_score, max_score)
# ),
# type= "l",
# colkey = list(addlines = TRUE)
# # , nticks = 10
# )
with(plot_flow, scatter3D(
  x = get(x), y = get(y), z = get(z),
  colvar = get(colvar), clab = colvar,
  pch = 19, cex = cex, bty = "b2",
  theta = theta, phi = phi,
  main = paste0(my_model, " : ", z, " with size_group=", unique(group_id)),
  xlab = x, ylab = y, zlab = z,
  ticktype = "detailed",
  clim = c(min_detour, max_detour),
  zlim = c(min_score, max_score)
)
,
type = "l",
colkey = list(addlines = TRUE))
plotrgl()
```


#### cube colorée avec x= path length, y = F1_score, z = nb_detour pour isof
##### X prop  = 0.1
fixed group size and proportion of detoured packets
```{r}
# Réinitialiser les marges à leurs valeurs par défaut
par(mar = c(0.5, 0,3, 0))
x= "path_length"
y = "F1_score"
z = "nb_detour"
colvar = "F1_score"
group = 1
my_model = "ISOF"
p_att = 0.1


plot_flow <- dtf_flow[model == my_model]
plot_pkt <- plot_flow[group_id == 1 & prop_att == p_att]
plot_flow <- plot_flow[group_id == group & prop_att == p_att]

# Définir les bornes communes
min_score <- 0#min(0plot_pkt[[y]], plot_flow[[y]], na.rm = TRUE)
max_score <- 1#max(plot_pkt[[y]], plot_flow[[y]], na.rm = TRUE)
min_detour <- min(plot_pkt[[z]], plot_flow[[z]], na.rm = TRUE)
max_detour <- max(plot_pkt[[z]], plot_flow[[z]], na.rm = TRUE)

par(mfrow = c(2,2)) 
theta = 220
phi = 00
cex = 1


with(plot_pkt, scatter3D(
  x = get(x), y = get(y), z = get(z),
  colvar = get(colvar), clab = "F1 score",
  pch = 19, cex = cex, bty = "b2",
  theta = theta, phi = phi,
  main = paste0(my_model, ": F1_score with \nsize_group=", unique(group_id),
                " and prop_att=", p_att),
  xlab = x, ylab = y, zlab = z,
  ticktype = "detailed",
  clim = c(min_score, max_score),
  ylim = c(min_score, max_score)
), 
zlim = c(min_detour,max_detour),
type= "l",
colkey = list(addlines = TRUE)
)
#plotrgl()
with(plot_flow, scatter3D(
  x = get(x), y = get(y), z = get(z),
  colvar = get(colvar), clab = colvar,
  pch = 19, cex = cex, bty = "b2",
  theta = theta, phi = phi,
  main = paste0(my_model, ": ", y," with \nsize_group=", unique(group_id),
                " and prop_att=", p_att),
  xlab = x, ylab = y, zlab = z,
  ticktype = "detailed",
  clim = c(min_score, max_score),
  ylim = c(min_score, max_score)),zlim = c(min_detour,max_detour),
  type= "l",
  colkey = list(addlines = TRUE)
)
plotrgl()
```

##### prop  = 0.075
fixed group size and proportion of detoured packets
```{r}
# Réinitialiser les marges à leurs valeurs par défaut
par(mar = c(0.5, 0,3, 0))
x= "path_length"
y = "F1_score"
z = "nb_detour"
colvar = "F1_score"
group = 1
my_model = "ISOF"
p_att = 0.075

plot_flow <- dtf_flow[model == my_model]
plot_pkt <- plot_flow[group_id == 1 & prop_att == p_att]
plot_flow <- plot_flow[group_id == group & prop_att == p_att]

# Limites globales pour z (nb_detour) et couleur (F1_score)
min_score <- 0#min(plot_pkt[[y]], plot_flow[[y]], na.rm = TRUE)
max_score <- 1#max(plot_pkt[[y]], plot_flow[[y]], na.rm = TRUE)
min_detour <- min(plot_pkt[[z]], plot_flow[[z]], na.rm = TRUE)
max_detour <- max(plot_pkt[[z]], plot_flow[[z]], na.rm = TRUE)

par(mfrow = c(2,2)) 
theta = 220
phi = 00
cex = 1

with(plot_pkt, scatter3D(
  x = get(x), y = get(y), z = get(z),
  colvar = get(colvar), clab = "F1 score",
  pch = 19, cex = cex, bty = "b2",
  theta = theta, phi = phi,
  main = paste0(my_model, ": ",y," with \nsize_group=", unique(group_id),
                ", prop_att=", p_att),
  xlab = x, ylab = y, zlab = z,
  ticktype = "detailed",
  clim = c(min_score, max_score),
  ylim = c(min_score, max_score)), zlim = c(min_detour,max_detour),
  type= "l",
  colkey = list(addlines = TRUE)
)
#plotrgl()
with(plot_flow, scatter3D(
  x = get(x), y = get(y), z = get(z),
  colvar = get(colvar), clab = colvar,
  pch = 19, cex = cex, bty = "b2",
  theta = theta, phi = phi,
  main = paste0(my_model, ": ",y," \nsize_group=", unique(group_id),
                ", prop_att=", p_att),
  xlab = x, ylab = y, zlab = z,
  ticktype = "detailed",
  clim = c(min_score, max_score),
  ylim = c(min_score, max_score)), 
  zlim = c(min_detour,max_detour),
  type= "l",
  colkey = list(addlines = TRUE)
)
plotrgl()
```

##### prop  = 0.050
fixed group size and proportion of detoured packets
```{r}
# Réinitialiser les marges à leurs valeurs par défaut
par(mar = c(0.5, 0,3, 0))
x= "path_length"
y = "F1_score"
z = "nb_detour"
colvar = "F1_score"
group = 1
my_model = "ISOF"
p_att = 0.050

plot_flow <- dtf_flow[model == my_model]
plot_pkt <- plot_flow[group_id == 1 & prop_att == p_att]
plot_flow <- plot_flow[group_id == group & prop_att == p_att]

# Calculs de bornes communes
min_score <- 0#min(plot_pkt[[y]], plot_flow[[y]], na.rm = TRUE)
max_score <- 1#max(plot_pkt[[y]], plot_flow[[y]], na.rm = TRUE)
min_detour <- min(plot_pkt[[z]], plot_flow[[z]], na.rm = TRUE)
max_detour <- max(plot_pkt[[z]], plot_flow[[z]], na.rm = TRUE)

par(mfrow = c(2,2)) 
theta = 220
phi = 00
cex = 1


with(plot_pkt, scatter3D(
  x = get(x), y = get(y), z = get(z),
  colvar = get(colvar), clab = "F1 score",
  pch = 19, cex = cex, bty = "b2",
  theta = theta, phi = phi,
  main = paste0(my_model, ": ", y," \nwith group_id=", unique (group_id), " and prop_att=", p_att),
  xlab = x, ylab = y, zlab = z, ticktype = "detailed",
  ylim = c(min_score, max_score), clim = c(min_score, max_score))
  ,zlim = c(min_detour,max_detour),
  type= "l",
  colkey = list(addlines = TRUE)
)
#plotrgl()
with (plot_flow, scatter3D(x = get(x), y = get(y), z = get(z),
                           colvar = get(colvar), clab = "F1 score", 
                           pch = 19, cex = cex, bty = "b2", 
                           theta = theta, phi = phi, 
                           main = paste0("Heatmap for F1_score with size_group=", unique (group_id), " and prop_att=", p_att), 
                           xlab = x, ylab = y, zlab = z, ticktype = "detailed"
                           , ylim = c(min_score,max_score), clim = c(min_score,max_score)),zlim = c(min_detour,max_detour),
      type= "l",
      colkey = list(addlines = TRUE)
)
plotrgl()
```


##### X prop  = 0.025
fixed group size and proportion of detoured packets
```{r}
# Réinitialiser les marges à leurs valeurs par défaut
par(mar = c(0.5, 0,3, 0))
x= "path_length"
y = "F1_score"
z = "nb_detour"
colvar = "F1_score"
group = 1
my_model = "ISOF"
p_att = 0.025

plot_flow <- dtf_flow[model == my_model]
plot_pkt <- plot_flow[group_id == 1 & prop_att == p_att]
plot_flow <- plot_flow[group_id == group & prop_att == p_att]

# Calculs de bornes communes
min_score <- 0#min(plot_pkt[[y]], plot_flow[[y]], na.rm = TRUE)
max_score <- 1#max(plot_pkt[[y]], plot_flow[[y]], na.rm = TRUE)
min_detour <- min(plot_pkt[[z]], plot_flow[[z]], na.rm = TRUE)
max_detour <- max(plot_pkt[[z]], plot_flow[[z]], na.rm = TRUE)

par(mfrow = c(2,2)) 
theta = 220
phi = 00
cex = 1


with (plot_pkt, scatter3D(x = get(x), y = get(y), z = get(z), 
                          colvar = get(colvar), clab = colvar, 
                          pch = 19, cex = cex, bty = "b2", 
                          theta = theta, phi = phi, 
                          main = paste0(my_model, ": ", y, "\nwith size_group=", unique(group_id), " and prop_att=", p_att), 
                          xlab = x, ylab = y, zlab = z, ticktype = "detailed"
                          , ylim = c(min_score,max_score), clim = c(min_score,max_score)),zlim = c(min_detour,max_detour),
      type= "l",
      colkey = list(addlines = TRUE)
)
#plotrgl()
with (plot_flow, scatter3D(x = get(x), y = get(y), z = get(z), 
                           colvar = get(colvar), clab = colvar, 
                           pch = 19, cex = cex, bty = "b2", 
                           theta = theta, phi = phi, 
                           main = paste0(my_model, ": ", y, "\nwith size_group=", unique (group_id), " and prop_att=", p_att), 
                           xlab = x, ylab = y, zlab = z, ticktype = "detailed"
                           , ylim = c(min_score,max_score), clim = c(min_score,max_score)),
      type= "l",
      colkey = list(addlines = TRUE)
)
plotrgl()
```


##### X prop  = 0.001
fixed group size and proportion of detoured packets
```{r}
# Réinitialiser les marges à leurs valeurs par défaut
par(mar = c(0.5, 0,3, 0))
x= "path_length"
y = "F1_score"
z = "nb_detour"
colvar = "F1_score"
group = 1
my_model = "ISOF"
p_att = 0.001

plot_flow <- dtf_flow[model == my_model]
plot_pkt <- plot_flow[group_id == 1 & prop_att == p_att]
plot_flow <- plot_flow[group_id == group & prop_att == p_att]

# Calculs de bornes communes
min_score <- 0#min(plot_pkt[[y]], plot_flow[[y]], na.rm = TRUE)
max_score <- 1#max(plot_pkt[[y]], plot_flow[[y]], na.rm = TRUE)
min_detour <- min(plot_pkt[[z]], plot_flow[[z]], na.rm = TRUE)
max_detour <- max(plot_pkt[[z]], plot_flow[[z]], na.rm = TRUE)

par(mfrow = c(2,2)) 
theta = 220
phi = 00
cex = 1


with (plot_pkt, scatter3D(x = get(x), y = get(y), z = get(z), 
                          colvar = get(colvar), clab = colvar,
                          pch = 19, cex = cex, bty = "b2", 
                          theta = theta, phi = phi, 
                          main = paste0(my_model, ": ", y, "\nwith size_group=", unique(group_id), " and prop_att=", p_att), 
                          xlab = x, ylab = y, zlab = z, ticktype = "detailed"
                          , ylim = c(min_score,max_score), clim = c(min_score,max_score)),zlim = c(min_detour,max_detour),
      type= "l",
      colkey = list(addlines = TRUE)
)
#plotrgl()
with (plot_flow, scatter3D(x = get(x), y = get(y), z = get(z), 
                           colvar = get(colvar), clab = colvar, 
                           pch = 19, cex = cex, bty = "b2", 
                           theta = theta, phi = phi, 
                           main = paste0(my_model, ": ", y, "\nwith size_group=", group, " and prop_att=", p_att), 
                           xlab = x, ylab = y, zlab = z, ticktype = "detailed"
                           , ylim = c(min_score,max_score), clim = c(min_score,max_score)),zlim = c(min_detour,max_detour),
      type= "l",
      colkey = list(addlines = TRUE)
)
plotrgl()
```

### X heatmap by detour
```{r}
group = 1
my_model = "ISOF"

plot_flow <- dtf_flow[model == my_model]
plot_pkt <- plot_flow[group_id == 1]
plot_flow <- plot_flow[group_id == group]




scores = c("Precision", "Recall", "F1_score")

g_pkt <- automate_heatmaps_nofct(
  data = plot_pkt,
  x = "path_length", 
  y = "prop_att", 
  score = "F1_score", 
  facet = "nb_detour", 
  by_combi = "group_id",
  output_dir = "heatmaps"
)
g_flow <- automate_heatmaps_nofct(
  data = plot_flow,
  x = "path_length", 
  y = "prop_att", 
  score = "F1_score", 
  facet = "nb_detour", 
  by_combi = "group_id",
  output_dir = "heatmaps"
)
#par(mfrow = c(2,1)) 
#grid.arrange(g_pkt_3var, g_pkt, g_flow)
```
### heatmap by detour for each model
```{r}
models_dispo = unique(dtf_flow$model)
group = 1
plot_flow <- dtf_flow[group_id == group]
my_model = models_dispo[1]
for (my_model in models_dispo){
  name = my_model
  par(mar = c(0.5, 0,2.5, 0))
  
  #par(mar = c(4.1, 3.1, 3.1, 1.1))
  plot_flow_model <- plot_flow[model == my_model]
  g_flow <- automate_heatmaps_nofct(
    data = plot_flow_model,
    x = "path_length", 
    y = "prop_att", 
    score = "F1_score", 
    facet = "nb_detour", 
    by_combi = "group_id",
    output_dir = "heatmaps"
  )
}
```


### score on a plane (weird colors and planes...) -> ca ne marche pas. 
```{r}
# Ajuster les marges du graphique
par(mar = c(0.5, 0,3, 0))
# group = 1
# prop = prop_att[20]
# my_model = "isof"
# data = dtf[dtf$group_id == group,]
# data = data[data$prop_att == prop,]
# data = data[data$model == my_model,]
# Trier les données par path_length et nb_detour



# Trier les données par path_length et nb_detour
plot_flow = dtf_flow[order(F1_score )] #data_packet$F1_score, ,data_packet$nb_detour, data_packet$path_length
plot_flow = plot_flow[prop_att == 0.1]
x = unique(plot_flow$path_length)
x = x[order(x)]
y = unique(plot_flow$nb_detour)
y = y[order(y)]
z = matrix(plot_flow$F1_score, nrow = length(x), ncol = length(y))

persp3D(x = x, y = y, z = z, colvar = z, clab = "F1 score", pch = 19, cex = 2, bty = "b2", 
        theta = theta, phi = phi, main = paste0(my_model, ": F1_score \nwith size_group=", group), xlab = "path_length", zlim = c(0,1),clim = c(0,1),
        ylab = "nb_detour", zlab = "F1_score", ticktype = "detailed", colkey = list(addlines = TRUE))


plotrgl()
```

## comparison of models pour prop = 0.1
fixed group size and proportion of detoured packets

### X by flows
```{r}
# Réinitialiser les marges à leurs valeurs par défaut
x= "path_length"
y = "F1_score"
z = "nb_detour"
colvar = "F1_score"
group = 490
proto = "Udp"
my_model = "ISOF"
p_att = 0.025
models_dispo = unique(dtf_flow$model)

plot_flow <- dtf_flow[group_id == group & prop_att == p_att & protocol == proto]
models_dispo = unique(plot_flow$model)
min_score = 0#dtf_flow[, min(F1_score, na.rm = TRUE)]# min( dtf_flow$F1_score, na.rm = TRUE)
max_score = 1#max( dtf_flow$F1_score, na.rm = TRUE)

min_detour =plot_flow[, min(nb_detour, na.rm = TRUE)]#min( plot_flow$nb_detour, na.rm = TRUE)
max_detour = plot_flow[, max(nb_detour, na.rm = TRUE)]#max( plot_flow$nb_detour, na.rm = TRUE)

par(mfrow = c(4,2))
theta = 190 #180#220
phi = 320 #280
cex = 1
my_model = models_dispo[1]
for (my_model in models_dispo){
  name = my_model
  par(mar = c(0.5, 0,2.5, 0))
  
  #par(mar = c(4.1, 3.1, 3.1, 1.1))
  plot_flow_model <- plot_flow[model == my_model]
  
  with (plot_flow_model, scatter3D(path_length, F1_score, nb_detour,
                                   colvar = F1_score, clab = "F1 score",
                                   pch = 19, cex = cex, bty = "b2",
                                   theta = theta, phi = phi,
                                   main = paste0(name,": F1_score; size_group=", group, " \n;prop_att=", p_att, "\nrep_flow"),
                                   xlab = "path_length",
                                   ylab ="F1_score", zlab = "nb_detour", ticktype = "detailed"
                                   , ylim = c(min_score,max_score), clim = c(min_score,max_score)),zlim = c(min_detour,max_detour),
        type= "l",
        colkey = list(addlines = TRUE)
        # , nticks = 10
  )
  #plotrgl()
}
```



## X evolution of each model

### by flows
```{r}
# Réinitialiser les marges à leurs valeurs par défaut
par(mar = c(0.5, 0,3, 0))
#par(mar = c(5.1, 4.1, 4.1, 2.1))
x= "path_length"
y = "F1_score"
z = "nb_detour"
colvar = "F1_score"
group = 490
my_model = "ISOF"
proto = "Udp"
models_dispo = unique(dtf_flow$model)
plot_flow <- dtf_flow[group_id == group & protocol == proto]
#
min_score = 0#min( dtf_flow$F1_score, na.rm = TRUE)
max_score = 1#max(dtf_flow$F1_score, na.rm = TRUE)
min_detour = min( plot_flow$nb_detour, na.rm = TRUE)
max_detour = max( plot_flow$nb_detour, na.rm = TRUE)
#par(mfrow = c(1,length(prop_att))) 
theta = 190 #180#220
phi = 320 #280
cex = 1
for (my_model in models_dispo){
  name = my_model
  par(mfrow = c(3,2)) 
  
  plot_flow_model <- plot_flow[model == my_model]
  for (p_att in prop_att)
  {
    
    plot_flow_prop <- plot_flow_model[prop_att == p_att]
    if (!(all(is.na(plot_flow_prop$F1_score))))
    {
      with (plot_flow_prop, scatter3D(path_length, F1_score, nb_detour, 
                                      colvar = F1_score, clab = "F1 score", 
                                      pch = 19, cex = cex, bty = "b2", 
                                      theta = theta, phi = phi, 
                                      main = paste0(name,": F1_score; size_group=", unique(group_id), " \n;prop_att=", p_att), 
                                      xlab = "path_length",
                                      ylab ="F1_score", zlab = "nb_detour", ticktype = "detailed"
                                      , ylim = c(min_score,max_score), clim = c(min_score,max_score)),zlim = c(min_detour,max_detour),
            type= "l",
            colkey = list(addlines = TRUE)
            # , nticks = 10
      )
      #plotrgl()
    }
  }
  
}
```




# confusion matrix
## ISOF
```{r}
tmp_data <- dtf_flow[model == "ISOF"]
tmp_data <- tmp_data[group_id == 1]
tmp_data <- tmp_data[nb_detour == 0]
tmp_data <- tmp_data[path_length==10]

# Create the title dynamically based on selected parameters
title_text <- paste0("F1_score as a function of detoured packets proportion\n",
                     "Path length: ", unique(tmp_data$path_length)," \nNb detoured router: ",unique (tmp_data$nb_detour),"\n"
                     #,"Square: no detour ||  +: prediction"
)

# Créer le graphique avec ggplot2
ggplot(tmp_data)+#, shape = approach)) +
  geom_point( aes(x = prop_att, y = F1_score, 
                  size = group_id, color = model), alpha = 0.7) +  # Ajout d'une transparence pour mieux visualiser les points
  scale_size(range = c(1, 5))+ #c(1, 5)) +  # Ajustement de la plage de tailles
  ggtitle(title_text) +
  labs(x = "Porportion of detoured packets",
       y = "F1_score",
       size = "Size of detourned packets groups",
       color = "model")+ 
  ylim(0,1)+
  theme_minimal() #+  

# Créer le graphique avec ggplot2
title_text <- paste0("Precision as a function of detoured packets proportion\n",
                     "Path length: ", unique(tmp_data$path_length)," \nNb detoured router: ",unique (tmp_data$nb_detour),"\n")
ggplot(tmp_data)+#, shape = approach)) +
  geom_point( aes(x = prop_att, y = Precision, 
                  size = group_id, color = model), alpha = 0.7) +  # Ajout d'une transparence pour mieux visualiser les points
  scale_size(range = c(1, 5))+ #c(1, 5)) +  # Ajustement de la plage de tailles
  ggtitle(title_text) +
  labs(x = "Porportion of detoured packets",
       y = "Precision",
       size = "Size of detourned packets groups",
       color = "model")+ 
  ylim(0,1)+
  theme_minimal() #+  

# Créer le graphique avec ggplot2
title_text <- paste0("Recall as a function of detoured packets proportion\n",
                     "Path length: ", unique(tmp_data$path_length)," \nNb detoured router: ",unique (tmp_data$nb_detour),"\n")
ggplot(tmp_data)+#, shape = approach)) +
  geom_point( aes(x = prop_att, y = Recall, 
                  size = group_id, color = model), alpha = 0.7) +  # Ajout d'une transparence pour mieux visualiser les points
  scale_size(range = c(1, 5))+ #c(1, 5)) +  # Ajustement de la plage de tailles
  ggtitle(title_text) +
  labs(x = "Porportion of detoured packets",
       y = "Recall",
       size = "Size of detourned packets groups",
       color = "model")+ 
  ylim(0,1)+
  theme_minimal() #+  

tmp_data_001 <- tmp_data[prop_att == 0.001]
print(tmp_data_001[,..scores])
print_confusionmatrix(tmp_data_001, 1)


```
## KMEANS
```{r}
tmp_data <- dtf_flow[model == "KMEANS"]
tmp_data <- tmp_data[group_id == 1]
tmp_data <- tmp_data[nb_detour == 0]
tmp_data <- tmp_data[path_length==10]

# Create the title dynamically based on selected parameters
title_text <- paste0("F1_score as a function of detoured packets proportion\n",
                     "Path length: ", unique(tmp_data$path_length)," \nNb detoured router: ",unique (tmp_data$nb_detour),"\n"
                     #,"Square: no detour ||  +: prediction"
)

# Créer le graphique avec ggplot2
ggplot(tmp_data)+#, shape = approach)) +
  geom_point( aes(x = prop_att, y = F1_score, 
                  size = group_id, color = model), alpha = 0.7) +  # Ajout d'une transparence pour mieux visualiser les points
  scale_size(range = c(1, 5))+ #c(1, 5)) +  # Ajustement de la plage de tailles
  ggtitle(title_text) +
  labs(x = "Porportion of detoured packets",
       y = "F1_score",
       size = "Size of detourned packets groups",
       color = "model")+ 
  ylim(0,1)+
  theme_minimal() #+  

# Créer le graphique avec ggplot2
title_text <- paste0("Precision as a function of detoured packets proportion\n",
                     "Path length: ", unique(tmp_data$path_length)," \nNb detoured router: ",unique (tmp_data$nb_detour),"\n")
ggplot(tmp_data)+#, shape = approach)) +
  geom_point( aes(x = prop_att, y = Precision, 
                  size = group_id, color = model), alpha = 0.7) +  # Ajout d'une transparence pour mieux visualiser les points
  scale_size(range = c(1, 5))+ #c(1, 5)) +  # Ajustement de la plage de tailles
  ggtitle(title_text) +
  labs(x = "Porportion of detoured packets",
       y = "Precision",
       size = "Size of detourned packets groups",
       color = "model")+ 
  ylim(0,1)+
  theme_minimal() #+  

# Créer le graphique avec ggplot2
title_text <- paste0("Recall as a function of detoured packets proportion\n",
                     "Path length: ", unique(tmp_data$path_length)," \nNb detoured router: ",unique (tmp_data$nb_detour),"\n")
ggplot(tmp_data)+#, shape = approach)) +
  geom_point( aes(x = prop_att, y = Recall, 
                  size = group_id, color = model), alpha = 0.7) +  # Ajout d'une transparence pour mieux visualiser les points
  scale_size(range = c(1, 5))+ #c(1, 5)) +  # Ajustement de la plage de tailles
  ggtitle(title_text) +
  labs(x = "Porportion of detoured packets",
       y = "Recall",
       size = "Size of detourned packets groups",
       color = "model")+ 
  ylim(0,1)+
  theme_minimal() #+  

tmp_data_001 <- tmp_data[prop_att == 0.001]
print(tmp_data_001[,..scores])
print_confusionmatrix(tmp_data_001, 1)

tmp_data_1 <- tmp_data[prop_att == 0.1]
print(tmp_data_1[,..scores])
print_confusionmatrix(tmp_data_1, 1)

```
## PCA then KMEANS
```{r}
tmp_data <- dtf_flow[model == "PCAthenKMEANS"]
tmp_data <- tmp_data[group_id == 1]
tmp_data <- tmp_data[nb_detour == 0]
tmp_data <- tmp_data[path_length==10]

# Create the title dynamically based on selected parameters
title_text <- paste0("F1_score as a function of detoured packets proportion\n",
                     "Path length: ", unique(tmp_data$path_length)," \nNb detoured router: ",unique (tmp_data$nb_detour),"\n"
                     #,"Square: no detour ||  +: prediction"
)

# Créer le graphique avec ggplot2
ggplot(tmp_data)+#, shape = approach)) +
  geom_point( aes(x = prop_att, y = F1_score, 
                  size = group_id, color = model), alpha = 0.7) +  # Ajout d'une transparence pour mieux visualiser les points
  scale_size(range = c(1, 5))+ #c(1, 5)) +  # Ajustement de la plage de tailles
  ggtitle(title_text) +
  labs(x = "Porportion of detoured packets",
       y = "F1_score",
       size = "Size of detourned packets groups",
       color = "model")+ 
  ylim(0,1)+
  theme_minimal() #+  

# Créer le graphique avec ggplot2
title_text <- paste0("Precision as a function of detoured packets proportion\n",
                     "Path length: ", unique(tmp_data$path_length)," \nNb detoured router: ",unique (tmp_data$nb_detour),"\n")
ggplot(tmp_data)+#, shape = approach)) +
  geom_point( aes(x = prop_att, y = Precision, 
                  size = group_id, color = model), alpha = 0.7) +  # Ajout d'une transparence pour mieux visualiser les points
  scale_size(range = c(1, 5))+ #c(1, 5)) +  # Ajustement de la plage de tailles
  ggtitle(title_text) +
  labs(x = "Porportion of detoured packets",
       y = "Precision",
       size = "Size of detourned packets groups",
       color = "model")+ 
  ylim(0,1)+
  theme_minimal() #+  

# Créer le graphique avec ggplot2
title_text <- paste0("Recall as a function of detoured packets proportion\n",
                     "Path length: ", unique(tmp_data$path_length)," \nNb detoured router: ",unique (tmp_data$nb_detour),"\n")
ggplot(tmp_data)+#, shape = approach)) +
  geom_point( aes(x = prop_att, y = Recall, 
                  size = group_id, color = model), alpha = 0.7) +  # Ajout d'une transparence pour mieux visualiser les points
  scale_size(range = c(1, 5))+ #c(1, 5)) +  # Ajustement de la plage de tailles
  ggtitle(title_text) +
  labs(x = "Porportion of detoured packets",
       y = "Recall",
       size = "Size of detourned packets groups",
       color = "model")+ 
  ylim(0,1)+
  theme_minimal() #+  

tmp_data_001 <- tmp_data[prop_att == 0.001]
print(tmp_data_001[,..scores])
print_confusionmatrix(tmp_data_001, 1)

tmp_data_1 <- tmp_data[prop_att == 0.1]
print(tmp_data_1[,..scores])
print_confusionmatrix(tmp_data_1, 1)

tmp_data_05 <- tmp_data[prop_att == 0.05]
print(tmp_data_05[,..scores])
print_confusionmatrix(tmp_data_05, 1)

```

## CART
```{r}
tmp_data <- dtf_flow[model == "CART"]
tmp_data <- tmp_data[group_id == 1]
tmp_data <- tmp_data[nb_detour == 0]
tmp_data <- tmp_data[path_length==10]

# Create the title dynamically based on selected parameters
title_text <- paste0("F1_score as a function of detoured packets proportion\n",
                     "Path length: ", unique(tmp_data$path_length)," \nNb detoured router: ",unique (tmp_data$nb_detour),"\n"
                     #,"Square: no detour ||  +: prediction"
)

# Créer le graphique avec ggplot2
ggplot(tmp_data)+#, shape = approach)) +
  geom_point( aes(x = prop_att, y = F1_score, 
                  size = group_id, color = model), alpha = 0.7) +  # Ajout d'une transparence pour mieux visualiser les points
  scale_size(range = c(1, 5))+ #c(1, 5)) +  # Ajustement de la plage de tailles
  ggtitle(title_text) +
  labs(x = "Porportion of detoured packets",
       y = "F1_score",
       size = "Size of detourned packets groups",
       color = "model")+ 
  ylim(0,1)+
  theme_minimal() #+  

# Créer le graphique avec ggplot2
title_text <- paste0("Precision as a function of detoured packets proportion\n",
                     "Path length: ", unique(tmp_data$path_length)," \nNb detoured router: ",unique (tmp_data$nb_detour),"\n")
ggplot(tmp_data)+#, shape = approach)) +
  geom_point( aes(x = prop_att, y = Precision, 
                  size = group_id, color = model), alpha = 0.7) +  # Ajout d'une transparence pour mieux visualiser les points
  scale_size(range = c(1, 5))+ #c(1, 5)) +  # Ajustement de la plage de tailles
  ggtitle(title_text) +
  labs(x = "Porportion of detoured packets",
       y = "Precision",
       size = "Size of detourned packets groups",
       color = "model")+ 
  ylim(0,1)+
  theme_minimal() #+  

# Créer le graphique avec ggplot2
title_text <- paste0("Recall as a function of detoured packets proportion\n",
                     "Path length: ", unique(tmp_data$path_length)," \nNb detoured router: ",unique (tmp_data$nb_detour),"\n")
ggplot(tmp_data)+#, shape = approach)) +
  geom_point( aes(x = prop_att, y = Recall, 
                  size = group_id, color = model), alpha = 0.7) +  # Ajout d'une transparence pour mieux visualiser les points
  scale_size(range = c(1, 5))+ #c(1, 5)) +  # Ajustement de la plage de tailles
  ggtitle(title_text) +
  labs(x = "Porportion of detoured packets",
       y = "Recall",
       size = "Size of detourned packets groups",
       color = "model")+ 
  ylim(0,1)+
  theme_minimal() #+  

tmp_data_001 <- tmp_data[prop_att == 0.001]
print(tmp_data_001[,..scores])
print_confusionmatrix(tmp_data_001, 1)

tmp_data <- dtf_flow[model == "CART"]
tmp_data <- tmp_data[group_id == 1]
tmp_data <- tmp_data[nb_detour == 1]
tmp_data <- tmp_data[path_length==10]

tmp_data_001 <- tmp_data[prop_att == 0.001]
print(tmp_data_001[,..scores])
print_confusionmatrix(tmp_data_001, 1)


```
## PCA then AE_CLASS
```{r}
tmp_data <- dtf_flow[model == "PCAthenAE_CLASS"]
tmp_data <- tmp_data[group_id == 1]
tmp_data <- tmp_data[nb_detour == 0]
tmp_data <- tmp_data[path_length==1]

# Create the title dynamically based on selected parameters
title_text <- paste0("F1_score as a function of detoured packets proportion\n",
                     "Path length: ", unique(tmp_data$path_length)," \nNb detoured router: ",unique (tmp_data$nb_detour),"\n"
                     #,"Square: no detour ||  +: prediction"
)

# Créer le graphique avec ggplot2
ggplot(tmp_data)+#, shape = approach)) +
  geom_point( aes(x = prop_att, y = F1_score, 
                  size = group_id, color = model), alpha = 0.7) +  # Ajout d'une transparence pour mieux visualiser les points
  scale_size(range = c(1, 5))+ #c(1, 5)) +  # Ajustement de la plage de tailles
  ggtitle(title_text) +
  labs(x = "Porportion of detoured packets",
       y = "F1_score",
       size = "Size of detourned packets groups",
       color = "model")+ 
  ylim(0,1)+
  theme_minimal() #+  

# Créer le graphique avec ggplot2
title_text <- paste0("Precision as a function of detoured packets proportion\n",
                     "Path length: ", unique(tmp_data$path_length)," \nNb detoured router: ",unique (tmp_data$nb_detour),"\n")
ggplot(tmp_data)+#, shape = approach)) +
  geom_point( aes(x = prop_att, y = Precision, 
                  size = group_id, color = model), alpha = 0.7) +  # Ajout d'une transparence pour mieux visualiser les points
  scale_size(range = c(1, 5))+ #c(1, 5)) +  # Ajustement de la plage de tailles
  ggtitle(title_text) +
  labs(x = "Porportion of detoured packets",
       y = "Precision",
       size = "Size of detourned packets groups",
       color = "model")+ 
  ylim(0,1)+
  theme_minimal() #+  

# Créer le graphique avec ggplot2
title_text <- paste0("Recall as a function of detoured packets proportion\n",
                     "Path length: ", unique(tmp_data$path_length)," \nNb detoured router: ",unique (tmp_data$nb_detour),"\n")
ggplot(tmp_data)+#, shape = approach)) +
  geom_point( aes(x = prop_att, y = Recall, 
                  size = group_id, color = model), alpha = 0.7) +  # Ajout d'une transparence pour mieux visualiser les points
  scale_size(range = c(1, 5))+ #c(1, 5)) +  # Ajustement de la plage de tailles
  ggtitle(title_text) +
  labs(x = "Porportion of detoured packets",
       y = "Recall",
       size = "Size of detourned packets groups",
       color = "model")+ 
  ylim(0,1)+
  theme_minimal() #+  

tmp_data_05 <- tmp_data[prop_att == 0.05]
print(tmp_data_05[,..scores])
print_confusionmatrix(tmp_data_05, 1)

tmp_data <- dtf_flow[model == "PCAthenAE_CLASS"]
tmp_data <- tmp_data[group_id == 1]
tmp_data <- tmp_data[nb_detour == 3]
tmp_data <- tmp_data[path_length==9]

tmp_data_001 <- tmp_data[prop_att == 0.001]
print(tmp_data_001[,..scores])
print_confusionmatrix(tmp_data_001, 1)


```

# for 10s
```{r}
dtf_flow_10s <- dtf_flow
dtf_flow_10s <- dtf_flow_10s[path_length<= 10]
dtf_flow_10s <- dtf_flow_10s[nb_detour<= 10,]
dtf_flow_10s <- dtf_flow_10s[group_id != -1]


min_group = min( dtf_flow_10s$group_id, na.rm = TRUE)
max_group = max( dtf_flow_10s$group_id, na.rm = TRUE)

min_score = 0#min(plot_pkt_tmp$F1_score, plot_flow_tmp$F1_score, na.rm = TRUE)
max_score = 1#max(plot_pkt_tmp$F1_score, plot_flow_tmp$F1_score, na.rm = TRUE)
min_detour = min( dtf_flow_10s$nb_detour, na.rm = TRUE)
max_detour = max( dtf_flow_10s$nb_detour, na.rm = TRUE)
```
```{r}
(count(dtf_flow_10s$group_id))
```

## by flow
```{r}
### data with flow repartition and several more variables ####
my_model = "VAE"
for (my_model in unique(dtf_flow_10s$model))
{
  
  plot_flow_tmp <- dtf_flow_10s[model == my_model]
  theta = 220
  phi = 00
  cex = 1
  # set the plotting area into a 1*2 array 
  par(mar = c(0.5, 0,3, 0))
  plot.new()
  
  par(mfrow = c(2,3)) 
  par(mar = c(0.5, 0,3, 0))
  
  prop = 0.01
  tmp_model = my_model
  plot_flow <- plot_flow_tmp[prop_att == prop]
  with (plot_flow, scatter3D(path_length, group_id, F1_score, colvar = nb_detour, clab = "nb_detour", 
                             pch = 19, cex = cex, bty = "b2", 
                             theta = theta, phi = phi, 
                             main = paste0(tmp_model, ": Heatmap for F1_score with prop=", prop), 
                             xlab = "path_length",
                             ylab ="group_id", zlab = "F1_score", ticktype = "detailed"
                             , clim = c(min_detour, max_detour), zlim = c(min_score, max_score)
                             ,ylim = c(min_group, max_group)
  ),
  type= "l",
  colkey = list(addlines = TRUE)
  # , nticks = 10
  )
  
  prop = 0.025
  plot_flow <- plot_flow_tmp[prop_att == prop]
  with (plot_flow, scatter3D(path_length, group_id, F1_score, colvar = nb_detour, clab = "nb_detour", 
                             pch = 19, cex = cex, bty = "b2", 
                             theta = theta, phi = phi, 
                             main = paste0(tmp_model, ": Heatmap for F1_score with prop=", prop), 
                             xlab = "path_length",
                             ylab ="group_id", zlab = "F1_score", ticktype = "detailed"
                             , clim = c(min_detour, max_detour), zlim = c(min_score, max_score)
                             ,ylim = c(min_group, max_group)
  ),
  type= "l",
  colkey = list(addlines = TRUE)
  # , nticks = 10
  )
  
  
  prop = 0.050
  plot_flow <- plot_flow_tmp[prop_att == prop]
  with (plot_flow, scatter3D(path_length, group_id, F1_score, colvar = nb_detour, clab = "nb_detour", 
                             pch = 19, cex = cex, bty = "b2", 
                             theta = theta, phi = phi, 
                             main = paste0(tmp_model, ": Heatmap for F1_score with prop=", prop), 
                             xlab = "path_length",
                             ylab ="group_id", zlab = "F1_score", ticktype = "detailed"
                             , clim = c(min_detour, max_detour), zlim = c(min_score, max_score)
                             ,ylim = c(min_group, max_group)
  ),
  type= "l",
  colkey = list(addlines = TRUE)
  # , nticks = 10
  )
  
  prop = 0.075
  plot_flow <- plot_flow_tmp[prop_att == prop]
  with (plot_flow, scatter3D(path_length, group_id, F1_score, colvar = nb_detour, clab = "nb_detour", 
                             pch = 19, cex = cex, bty = "b2", 
                             theta = theta, phi = phi, 
                             main = paste0(tmp_model, ": Heatmap for F1_score with prop=", prop), 
                             xlab = "path_length",
                             ylab ="group_id", zlab = "F1_score", ticktype = "detailed"
                             , clim = c(min_detour, max_detour), zlim = c(min_score, max_score)
                             ,ylim = c(min_group, max_group)
  ),
  type= "l",
  colkey = list(addlines = TRUE)
  # , nticks = 10
  )
  
  prop = 0.1
  plot_flow <- plot_flow_tmp[prop_att == prop]
  with (plot_flow, scatter3D(path_length, group_id, F1_score, colvar = nb_detour, clab = "nb_detour",
                             pch = 19, cex = cex, bty = "b2",
                             theta = theta, phi = phi,
                             main = paste0(tmp_model, ": Heatmap for F1_score with prop=", prop),
                             xlab = "path_length",
                             ylab ="group_id", zlab = "F1_score", ticktype = "detailed"
                             , clim = c(min_detour, max_detour), zlim = c(min_score, max_score)
                             ,ylim = c(min_group, max_group)
  ),
  type= "l",
  colkey = list(addlines = TRUE)
  # , nticks = 10
  )
}
```


## random flow size
```{r}
dtf_flow_10s <- dtf_flow
dtf_flow_10s <- dtf_flow_10s[dtf_flow_10s$nb_detour<= 10,]
dtf_flow_10s <- dtf_flow_10s[dtf_flow_10s$group_id == -1,]
dtf_flow_10s <- dtf_flow_10s[dtf_flow_10s$path_length <= 3,]

min_group = min(dtf_flow_10s$group_id, na.rm = TRUE)
max_group = ifelse(min_group == max(dtf_flow_10s$group_id, na.rm = TRUE), min_group + 1, max(dtf_flow_10s$group_id, na.rm = TRUE))

min_score = 0#min(plot_pkt_tmp$F1_score, plot_flow_tmp$F1_score, na.rm = TRUE)
max_score = 1#max(plot_pkt_tmp$F1_score, plot_flow_tmp$F1_score, na.rm = TRUE)
min_detour = min( dtf_flow_10s$nb_detour, na.rm = TRUE)
max_detour = max(dtf_flow_10s$nb_detour, na.rm = TRUE)
```
```{r}
(count(dtf_flow_10s$group_id))

```


```{r}
### data with flow repartition and several more variables ####
for (my_model in unique(dtf_flow_10s$model))
{
  
  plot_flow_tmp <- dtf_flow_10s[dtf_flow_10s$model == my_model,]
  theta = 220
  phi = 00
  cex = 1
  # set the plotting area into a 1*2 array 
  par(mar = c(0.5, 0,3, 0))
  plot.new()
  
  par(mfrow = c(2,3)) 
  par(mar = c(0.5, 0,3, 0))
  
  prop = 0.001
  tmp_model = my_model
  plot_flow <- plot_flow_tmp[plot_flow_tmp$prop_att == prop,]
  if (!all(is.na(plot_flow$F1_score)))
  {
    with (plot_flow, scatter3D(path_length, nb_detour, F1_score, colvar = F1_score, clab = "F1 score", 
                               pch = 19, cex = cex, bty = "b2", 
                               theta = theta, phi = phi, 
                               main = paste0(tmp_model, ": Heatmap for F1_score with prop=", prop, 
                                             "\n for a repartion by flow with more variables"), 
                               xlab = "path_length",
                               ylab ="nb_detour", zlab = "F1_score", ticktype = "detailed"
                               , clim = c(min_score, max_score), zlim = c(min_score, max_score)
                               ,ylim = c(min_detour, max_detour)
    ),
    type= "l",
    colkey = list(addlines = TRUE)
    # , nticks = 10
    )
  }else{
    plot(print_confusionmatrix (plot_flow, 1))
  }
  prop = 0.026
  plot_flow <- plot_flow_tmp[plot_flow_tmp$prop_att == prop,]
  if (!all(is.na(plot_flow$F1_score)))
  {
    with (plot_flow, scatter3D(path_length, nb_detour, F1_score, colvar = F1_score, clab = "F1 score", 
                               pch = 19, cex = cex, bty = "b2", 
                               theta = theta, phi = phi, 
                               main = paste0(tmp_model, ": Heatmap for F1_score with prop=", prop, 
                                             "\n for a repartion by flow with more variables"), 
                               xlab = "path_length",
                               ylab ="nb_detour", zlab = "F1_score", ticktype = "detailed"
                               , clim = c(min_score, max_score), zlim = c(min_score, max_score)
                               ,ylim = c(min_detour, max_detour)
    ),
    type= "l",
    colkey = list(addlines = TRUE)
    # , nticks = 10
    )
  }else{
    plot(print_confusionmatrix (plot_flow, 1))
  }
  
  prop = 0.051
  plot_flow <- plot_flow_tmp[plot_flow_tmp$prop_att == prop,]
  if (!all(is.na(plot_flow$F1_score)))
  {
    with (plot_flow, scatter3D(path_length, nb_detour, F1_score, colvar = F1_score, clab = "F1 score", 
                               pch = 19, cex = cex, bty = "b2", 
                               theta = theta, phi = phi, 
                               main = paste0(tmp_model, ": Heatmap for F1_score with prop=", prop, 
                                             "\n for a repartion by flow with more variables"), 
                               xlab = "path_length",
                               ylab ="nb_detour", zlab = "F1_score", ticktype = "detailed"
                               , clim = c(min_score, max_score), zlim = c(min_score, max_score)
                               ,ylim = c(min_detour, max_detour)
    ),
    type= "l",
    colkey = list(addlines = TRUE)
    # , nticks = 10
    )
  }else{
    plot(print_confusionmatrix (plot_flow, 1))
  }
  
  prop = 0.076
  plot_flow <- plot_flow_tmp[plot_flow_tmp$prop_att == prop,]
  if (!all(is.na(plot_flow$F1_score)))
  {
    with (plot_flow, scatter3D(path_length, nb_detour, F1_score, colvar = F1_score, clab = "F1 score", 
                               pch = 19, cex = cex, bty = "b2", 
                               theta = theta, phi = phi, 
                               main = paste0(tmp_model, ": Heatmap for F1_score with prop=", prop, 
                                             "\n for a repartion by flow with more variables"), 
                               xlab = "path_length",
                               ylab ="nb_detour", zlab = "F1_score", ticktype = "detailed"
                               , clim = c(min_score, max_score), zlim = c(min_score, max_score)
                               ,ylim = c(min_detour, max_detour)
    ),
    type= "l",
    colkey = list(addlines = TRUE)
    # , nticks = 10
    )
  }else{
    plot(print_confusionmatrix (plot_flow, 1))
  }
  
  prop = 0.096
  plot_flow <- plot_flow_tmp[plot_flow_tmp$prop_att == prop,]
  if (!all(is.na(plot_flow$F1_score)))
  {
    with (plot_flow, scatter3D(path_length, nb_detour, F1_score, colvar = F1_score, clab = "F1 score", 
                               pch = 19, cex = cex, bty = "b2", 
                               theta = theta, phi = phi, 
                               main = paste0(tmp_model, ": Heatmap for F1_score with prop=", prop, 
                                             "\n for a repartion by flow with more variables"), 
                               xlab = "path_length",
                               ylab ="nb_detour", zlab = "F1_score", ticktype = "detailed"
                               , clim = c(min_score, max_score), zlim = c(min_score, max_score)
                               ,ylim = c(min_detour, max_detour)
    ),
    type= "l",
    colkey = list(addlines = TRUE)
    # , nticks = 10
    )
  }else{
    plot(print_confusionmatrix (plot_flow, 1))
  }
  
}
```



# graphe en fonction du flux parasite. 
## comparison of models pour prop = 0.1
fixed group size and proportion of detoured packets


```{r}
# Réinitialiser les marges à leurs valeurs par défaut
library(patchwork)
library(dplyr)
library(tidyr)
library(ggplot2)

x= "parasite_rate"
y = "F1_score"
#z = "nb_detour"
colvar = "approach"
group = 9
my_model = "ISOF"
p_att = 0.1
detour = 0
path = 0
proto= "Udp"
models_dispo = unique(dtf_flow$model)
models_dispo = models_dispo[! models_dispo %in% c("AE_CONTRACTIVE", "PCAthenAE_CONTRACTIVE",  "AE_SIMPLE",  "PCAthenAE_SIMPLE", "INTERVAL", "PCAthenINTERVAL", "OCSVM", "PCAthenOCSVM")] #"AE_CLASS", "PCAthenAE_CLASS"
models_dispo = c( "THRESHOLD", "INTERVAL_DELAY",
  "SVM",  "REGLOG", # "CART", "XGBOOST",
                  "DAE", "VAE") #"KMEANS", "ISOF",, "AE_SPARSE", "AE_LSTM", "AE_CONV1D"

names_no_pca <- models_dispo[!grepl("^PCAthen", models_dispo)]
names_pca <- models_dispo[grepl("^PCAthen", models_dispo)]

plot_flow <- dtf_flow[group_id == group 
                      & prop_att == p_att 
                      & path_length == path
                      &  nb_detour == detour 
                      & protocol == proto 
                      & !is.na(parasite_rate)
                      & model %in% models_dispo]
#plot_flow <- plot_flow[!duplicated(plot_flow[, ..to_distinct], fromLast = TRUE)]

#plot_flow <- plot_flow[-222,]
min_score = 0#dtf_flow[, min(F1_score, na.rm = TRUE)]# min( dtf_flow$F1_score, na.rm = TRUE)
max_score = 1#max( dtf_flow$F1_score, na.rm = TRUE)

min_detour =plot_flow[, min(nb_detour, na.rm = TRUE)]#min( plot_flow$nb_detour, na.rm = TRUE)
max_detour = plot_flow[, max(nb_detour, na.rm = TRUE)]#max( plot_flow$nb_detour, na.rm = TRUE)

par(mfrow = c(4,2))
theta = 190 #180#220
phi = 320 #280
cex = 1
my_model = models_dispo[3]
plots_no_pca <- list()
plots_pca <- list()
for (my_model in models_dispo){
  name = my_model
  par(mar = c(0.5, 0,2.5, 0))
  
  #par(mar = c(4.1, 3.1, 3.1, 1.1))
  plot_flow_model <- plot_flow[model == my_model]
  #unique (plot_flow_model$parasite_rate)
  
  
  
#   plot_long <- plot_flow_model %>%
#   pivot_longer(
#     cols = c(F1_score, Precision_mean, Recall_mean),
#     names_to = "metric",
#     values_to = "score"
#   )
# 
# p <- ggplot(plot_long, aes(x = parasite_rate, y = score, color = approach)) +
#   geom_point(aes(shape = interaction(metric, approach)), size = 2, stroke = 1, 
#              show.legend = c(color = FALSE, shape = FALSE)) +
#   geom_errorbar(
#     data = subset(plot_long, metric == "F1_score"),
#     aes(ymin = F1_ci_lower, ymax = F1_ci_upper, color = approach),
#     width = 1,
#     alpha = 0.6
#     , show.legend = c(color = FALSE)
#   ) +
#   scale_color_manual(values = c(
#     "supervised" = "red",
#     "unsupervised" = "#619cff",
#     "baseline" = "#00ba38"
#   )) +
#   scale_shape_manual(values = c(
#     "F1_score.supervised" = 15,
#     "F1_score.unsupervised" = 16,
#     "F1_score.baseline" = 17,
#     "Precision_mean.supervised" = 0,
#     "Precision_mean.unsupervised" = 1,
#     "Precision_mean.baseline" = 2,
#     "Recall_mean.supervised" = 12,
#     "Recall_mean.unsupervised" = 10,
#     "Recall_mean.baseline" = 8
#   )) +
#   coord_cartesian(ylim = c(min_score, max_score)) +
#   labs(
#     title = paste0(name),
#     x = "Parasite Rate (Mbps)",
#     y = "Score"
#   ) +
#   theme_minimal() +
#   theme(
#     axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)
#   )
  
  

  p <- ggplot(plot_flow_model, aes(x = parasite_rate, y = F1_score, color= approach, shape = approach)) +
    #geom_point(aes(x = parasite_rate, y = Precision_mean, color= approach, shape = approach)) +
    #geom_point(aes(x = parasite_rate, y = Recall_mean, color= approach, shape = approach)) +
    geom_point(size = 1,stroke = 2, show.legend = c(color = FALSE, shape = FALSE)) +
    scale_color_manual(
      values = c(
        "supervised" = "red",
        "unsupervised" = "#619cff",
        "baseline" = "#00ba38"
      )) +

  # #geom_point(size = 2, stroke = 1.2, show.legend = c(color = FALSE, shape = FALSE)) +
  geom_errorbar(aes(
      ymin = F1_ci_lower,
      ymax = F1_ci_upper,
      color = "black"
    ),
    width = 1, # controls horizontal width of the bar
    alpha = 0.6, show.legend = c(color = FALSE, shape = FALSE),

  ) +
    scale_shape_manual(
      values = c(
        "supervised" = 15,
        "unsupervised" = 16,
        "baseline" = 17
      )) +
    coord_cartesian(ylim = c(min_score, max_score)) +  # ← la bonne méthode
    labs(
      title = paste0(name), #,":\nPath length=", path+4, "; Detour length=", detour+5),
      #\nsize_group=", group, "  \nprop_att=", p_att, " F1_score; ;
      x = "Parasite Rate (Mbps)",
      y = TeX("$F_1$-Score")
      ) +
    theme_minimal()+ #base_size = 15
  theme(
    #plot.title = element_text(size = 30),
    #legend.title = element_text(size = 28),
    #legend.text = element_text(size = 25),
    #axis.title = element_text(size = 25),
    axis.text.x = element_text( angle = 90, hjust = 1, vjust = 0.5)
    #,legend.key.size = unit(5, "lines")  # or "cm", "pt", etc.
  ) +
  guides(
    shape = guide_legend(order = 1),
    color = guide_legend(order = 2),
    fill  = guide_legend(order = 3)
  )
  if (my_model %in% names_pca){
    plots_pca[[my_model]] <- p
  }else
  {
    plots_no_pca[[my_model]] <- p
  }
  
  #print(p)
}
#wrap_plots(plots_pca)
design <- "AB
           CD
           EF"
design <- "ACE
           BDF"
wrap_plots(plots_no_pca, design = design)

```


### X by flows with CI
```{r}
# Réinitialiser les marges à leurs valeurs par défaut
library(patchwork)
library(dplyr)
library(tidyr)
library(ggplot2)

x= "parasite_rate"
y = "F1_score"
#z = "nb_detour"
colvar = "approach"
group = 9
my_model = "ISOF"
p_att = 0.1
detour = "0" #0_1_3_5_7_9"
path = 0
proto= "Udp"
models_dispo = unique(dtf_flow$model)
models_dispo = models_dispo[! models_dispo %in% c("AE_CONTRACTIVE", "PCAthenAE_CONTRACTIVE",  "AE_SIMPLE",  "PCAthenAE_SIMPLE", "INTERVAL", "PCAthenINTERVAL", "OCSVM", "PCAthenOCSVM")] #"AE_CLASS", "PCAthenAE_CLASS"
models_dispo = c( "THRESHOLD", "INTERVAL_DELAY",
  "SVM",  "REGLOG", # "CART", "XGBOOST","XGBOOST",
                  "DAE", "VAE") #"KMEANS", "ISOF",, "AE_SPARSE", "AE_LSTM", "AE_CONV1D"

names_no_pca <- models_dispo[!grepl("^PCAthen", models_dispo)]
names_pca <- models_dispo[grepl("^PCAthen", models_dispo)]

plot_flow <- dtf_flow[group_id == group 
                      & prop_att == p_att 
                      & path_length == path
                      &  nb_detour == detour 
                      & protocol == proto 
                      & !is.na(parasite_rate)
                      & model %in% models_dispo
                      & do_evolution == F
                      ]
#plot_flow <- plot_flow[!duplicated(plot_flow[, ..to_distinct], fromLast = TRUE)]

#plot_flow <- plot_flow[-222,]
min_score = 0#dtf_flow[, min(F1_score, na.rm = TRUE)]# min( dtf_flow$F1_score, na.rm = TRUE)
max_score = 1#max( dtf_flow$F1_score, na.rm = TRUE)

#min_detour =plot_flow[, min(nb_detour, na.rm = TRUE)]#min( plot_flow$nb_detour, na.rm = TRUE)
#max_detour = plot_flow[, max(nb_detour, na.rm = TRUE)]#max( plot_flow$nb_detour, na.rm = TRUE)

par(mfrow = c(4,2))
theta = 190 #180#220
phi = 320 #280
cex = 1

plot_flow[approach == "baseline", approach := "Baseline"]
plot_flow[approach == "unsupervised", approach := "Unsupervised"]
plot_flow[approach == "supervised", approach := "Supervised"]
plot_flow[, facet_label := paste(approach, model, sep = ": ")]
plot_flow[, facet_label := factor(facet_label, levels = c(
  "Baseline: THRESHOLD",
  "Supervised: SVM",
  "Unsupervised: DAE",
  "Baseline: INTERVAL_DELAY",
  "Supervised: REGLOG",
  "Unsupervised: VAE"
,"Supervised: XGBOOST"
))]
# Create the faceted plot
ggplot(plot_flow, aes(x = parasite_rate, y = F1_score, color= approach, shape = approach)) +
  geom_point(size = 1,stroke = 2, show.legend = c(color = FALSE, shape = FALSE)) +
  geom_errorbar(aes(
      ymin = F1_ci_lower,
      ymax = F1_ci_upper,
      color = "black"
    ),
    width = 0.7, # controls horizontal width of the bar
    alpha = 0.6, show.legend = c(color = FALSE, shape = FALSE),

  ) +
    scale_color_manual(
      values = c(
        "Supervised" = "red",
        "Unsupervised" = "#619cff",
        "Baseline" = "#00ba38"
      )) +
  scale_shape_manual(
      values = c(
        "Supervised" = 15,
        "Unsupervised" = 16,
        "Baseline" = 17
      )) +
    coord_cartesian(ylim = c(min_score, max_score)) +  # ← la bonne méthode
    labs(
      #title = paste0(name), #,":\nPath length=", path+4, "; Detour length=", detour+5),
      #\nsize_group=", group, "  \nprop_att=", p_att, " F1_score; ;
      x = "Parasite Rate (Mbps)",
      y = TeX("$F_1$-Score")
      ) +
  facet_wrap(~ facet_label, nrow = 3, ncol = 3)+
  # facet_wrap(~ interaction(approach, model), nrow = 2, ncol = 3,
  #          labeller = labeller(`interaction(approach, model)` = my_labels)
  #            )+
  # facet_grid( rows = vars(model),col = vars(approach)
  #             ,scales = "free", space = "free") + # or facet_wrap(~group)
  theme_minimal(base_size = 20)+
  theme(
    #plot.title = element_text(size = 30),
    #legend.title = element_text(size = 28),
    #legend.text = element_text(size = 25),
    #axis.title = element_text(size = 20),
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, size = 15),
    axis.text.y = element_text(size = 15),
    panel.background = element_rect(fill = "transparent", color = NA),
  plot.background = element_rect(fill = "transparent", color = NA),
  panel.grid.major = element_line(color = "grey", linewidth = 0.1),
  panel.grid.minor = element_line(color = "grey", linewidth = 0.1)
    #,legend.key.size = unit(5, "lines")  # or "cm", "pt", etc.
  )
length(unique(plot_flow$seed))
```

### X by flows with boxplot
```{r}
# Réinitialiser les marges à leurs valeurs par défaut
library(patchwork)
library(dplyr)
library(tidyr)
library(ggplot2)

x= "parasite_rate"
y = "F1_score"
#z = "nb_detour"
colvar = "approach"
group = 9
my_model = "ISOF"
p_att = 0.1
detour = "0" #0_1_3_5_7_9"
path = 0
proto= "Udp"
models_dispo = unique(dtf_flow_boxplot$model)
models_dispo = models_dispo[! models_dispo %in% c("AE_CONTRACTIVE", "PCAthenAE_CONTRACTIVE",  "AE_SIMPLE",  "PCAthenAE_SIMPLE", "INTERVAL", "PCAthenINTERVAL", "OCSVM", "PCAthenOCSVM")] #"AE_CLASS", "PCAthenAE_CLASS"
models_dispo = c( "THRESHOLD", "INTERVAL_DELAY",
  "SVM",  "REGLOG", # "CART", "XGBOOST","XGBOOST",
                  "DAE", "VAE") #"KMEANS", "ISOF",, "AE_SPARSE", "AE_LSTM", "AE_CONV1D"

names_no_pca <- models_dispo[!grepl("^PCAthen", models_dispo)]
names_pca <- models_dispo[grepl("^PCAthen", models_dispo)]

plot_flow <- dtf_flow_boxplot[group_id == group 
                      & prop_att == p_att 
                      & path_length == path
                      &  nb_detour == detour 
                      & protocol == proto 
                      & !is.na(parasite_rate)
                      & model %in% models_dispo
                      & do_evolution == F
                      & directory == "eleventh" #"ninth"
                      & comment == "basic"
                      #& ( dataset == "dtf_16")
                      ]
#plot_flow <- plot_flow[!duplicated(plot_flow[, ..to_distinct], fromLast = TRUE)]

#plot_flow <- plot_flow[-222,]
min_score = 0#dtf_flow[, min(F1_score, na.rm = TRUE)]# min( dtf_flow$F1_score, na.rm = TRUE)
max_score = 1#max( dtf_flow$F1_score, na.rm = TRUE)

#min_detour =plot_flow[, min(nb_detour, na.rm = TRUE)]#min( plot_flow$nb_detour, na.rm = TRUE)
#max_detour = plot_flow[, max(nb_detour, na.rm = TRUE)]#max( plot_flow$nb_detour, na.rm = TRUE)

par(mfrow = c(4,2))
theta = 190 #180#220
phi = 320 #280
cex = 1

plot_flow[approach == "baseline", approach := "Baseline"]
plot_flow[approach == "unsupervised", approach := "Unsupervised"]
plot_flow[approach == "supervised", approach := "Supervised"]
plot_flow[, facet_label := paste(approach, model, sep = ": ")]
plot_flow[, facet_label := factor(facet_label, levels = c(
  "Baseline: THRESHOLD",
  "Supervised: SVM",
  "Unsupervised: DAE",
  "Baseline: INTERVAL_DELAY",
  "Supervised: REGLOG",
  "Unsupervised: VAE"
,"Supervised: XGBOOST"
))]
# Create the faceted plot
ggplot(plot_flow, aes(x = parasite_rate, y = F1_score, color= approach, shape = approach)) +
  #geom_point(size = 1,stroke = 2, show.legend = c(color = FALSE, shape = FALSE)) +
  # geom_errorbar(aes(
  #     ymin = F1_ci_lower,
  #     ymax = F1_ci_upper,
  #     color = "black"
  #   ),
  #   width = 0.7, # controls horizontal width of the bar
  #   alpha = 0.6, show.legend = c(color = FALSE, shape = FALSE),
  # 
  # ) +
  #geom_violin(aes(color = approach), show.legend = F)+
  geom_boxplot(outlier.color = "black", show.legend = F, notch = F
               , staplewidth = 0.7, varwidth = T, aes(fill = approach), color = "black"
               #,coef = 0
               #,width = 0.4
               )+
  
    scale_color_manual(
      values = c(
        "Supervised" = "#f8766d",
        "Unsupervised" = "#619cff",
        "Baseline" = "#00ba38"
      )) +
  scale_fill_manual(
      values = c(
        "Supervised" = "#f8766d",
        "Unsupervised" = "#619cff",
        "Baseline" = "#00ba38"
      )) +
  scale_shape_manual(
      values = c(
        "Supervised" = 15,
        "Unsupervised" = 16,
        "Baseline" = 17
      )) +
    coord_cartesian(ylim = c(min_score, max_score)) +  # ← la bonne méthode
    labs(
      #title = paste0(name), #,":\nPath length=", path+4, "; Detour length=", detour+5),
      #\nsize_group=", group, "  \nprop_att=", p_att, " F1_score; ;
      x = "Parasite Rate (Mbps)",
      y = TeX("$F_1$-Score")
      ) +
  facet_wrap(~ facet_label, nrow = 3, ncol = 3)+
  # facet_wrap(~ interaction(approach, model), nrow = 2, ncol = 3,
  #          labeller = labeller(`interaction(approach, model)` = my_labels)
  #            )+
  # facet_grid( rows = vars(model),col = vars(approach)
  #             ,scales = "free", space = "free") + # or facet_wrap(~group)
  theme_minimal(base_size = 20)+
  theme(
    #plot.title = element_text(size = 30),
    #legend.title = element_text(size = 28),
    #legend.text = element_text(size = 25),
    #axis.title = element_text(size = 20),
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, size = 15),
    axis.text.y = element_text(size = 15),
    panel.background = element_rect(fill = "transparent", color = NA),
  plot.background = element_rect(fill = "transparent", color = NA),
  panel.grid.major = element_line(color = "grey", linewidth = 0.1),
  panel.grid.minor = element_line(color = "grey", linewidth = 0.1)
    #,legend.key.size = unit(5, "lines")  # or "cm", "pt", etc.
  )
length(unique(plot_flow$seed))
```


### X by flows with trainondetour
```{r}
# Réinitialiser les marges à leurs valeurs par défaut
library(patchwork)
library(dplyr)
library(tidyr)
library(ggplot2)

x= "parasite_rate"
y = "F1_score"
#z = "nb_detour"
colvar = "approach"
group = 342#9,27,342
my_model = "ISOF"
p_att = 0.1
detour = "0_1_3_5_7_9"#"0_1_3_5_7_9"
path = 0
cmt = "basic" #"same_size_dataset" #"basic" #"same_size_dataset"
proto= "Udp"
models_dispo = unique(dtf_flow_boxplot$model)
models_dispo = models_dispo[! models_dispo %in% c("AE_CONTRACTIVE", "PCAthenAE_CONTRACTIVE",  "AE_SIMPLE",  "PCAthenAE_SIMPLE", "INTERVAL", "PCAthenINTERVAL", "OCSVM", "PCAthenOCSVM")] #"AE_CLASS", "PCAthenAE_CLASS"
models_dispo = c( "THRESHOLD", "INTERVAL_DELAY",
  "SVM",  "REGLOG", # "CART", "XGBOOST","XGBOOST",
                  "DAE", "VAE") #"KMEANS", "ISOF",, "AE_SPARSE", "AE_LSTM", "AE_CONV1D"

names_no_pca <- models_dispo[!grepl("^PCAthen", models_dispo)]
names_pca <- models_dispo[grepl("^PCAthen", models_dispo)]

plot_flow <- dtf_flow_boxplot[group_id == group 
                      & prop_att == p_att 
                      & path_length == path
                      &  nb_detour == detour 
                      & protocol == proto 
                      & !is.na(parasite_rate)
                      & model %in% models_dispo
                      & do_evolution == F
                      & comment == cmt
                      & directory == "eleventh" #"ninth"
                     # & dataset == "dtf_16"
                      ]
#plot_flow <- plot_flow[!duplicated(plot_flow[, ..to_distinct], fromLast = TRUE)]

#plot_flow <- plot_flow[-222,]
min_score = 0#dtf_flow[, min(F1_score, na.rm = TRUE)]# min( dtf_flow$F1_score, na.rm = TRUE)
max_score = 1#max( dtf_flow$F1_score, na.rm = TRUE)

#min_detour =plot_flow[, min(nb_detour, na.rm = TRUE)]#min( plot_flow$nb_detour, na.rm = TRUE)
#max_detour = plot_flow[, max(nb_detour, na.rm = TRUE)]#max( plot_flow$nb_detour, na.rm = TRUE)

par(mfrow = c(4,2))
theta = 190 #180#220
phi = 320 #280
cex = 1

plot_flow[approach == "baseline", approach := "Baseline"]
plot_flow[approach == "unsupervised", approach := "Unsupervised"]
plot_flow[approach == "supervised", approach := "Supervised"]
plot_flow[, facet_label := paste(approach, model, sep = ": ")]
plot_flow[, facet_label := factor(facet_label, levels = c(
  "Baseline: THRESHOLD",
  "Supervised: SVM",
  "Unsupervised: DAE",
  "Baseline: INTERVAL_DELAY",
  "Supervised: REGLOG",
  "Unsupervised: VAE"
,"Supervised: XGBOOST"
))]
# Create the faceted plot
ggplot(plot_flow, aes(x = parasite_rate, y = F1_score, color= approach, shape = approach)) +
  #geom_point(size = 1,stroke = 2, show.legend = c(color = FALSE, shape = FALSE)) +
  # geom_errorbar(aes(
  #     ymin = F1_ci_lower,
  #     ymax = F1_ci_upper,
  #     color = "black"
  #   ),
  #   width = 0.7, # controls horizontal width of the bar
  #   alpha = 0.6, show.legend = c(color = FALSE, shape = FALSE),
  # 
  # ) +
  #geom_violin(aes(color = approach), show.legend = F)+
  geom_boxplot(outlier.color = "black", show.legend = F, notch = F
               , staplewidth = 0.7, varwidth = T, aes(fill = approach), color = "black"
               #,coef = 0
               #,width = 0.4
               )+
  
    scale_color_manual(
      values = c(
        "Supervised" = "#f8766d",
        "Unsupervised" = "#619cff",
        "Baseline" = "#00ba38"
      )) +
  scale_fill_manual(
      values = c(
        "Supervised" = "#f8766d",
        "Unsupervised" = "#619cff",
        "Baseline" = "#00ba38"
      )) +
  scale_shape_manual(
      values = c(
        "Supervised" = 15,
        "Unsupervised" = 16,
        "Baseline" = 17
      )) +
    coord_cartesian(ylim = c(min_score, max_score)) +  # ← la bonne méthode
    labs(
      #title = paste0(name), #,":\nPath length=", path+4, "; Detour length=", detour+5),
      #\nsize_group=", group, "  \nprop_att=", p_att, " F1_score; ;
      x = "Parasite Rate (Mbps)",
      y = TeX("$F_1$-Score")
      ) +
  facet_wrap(~ facet_label, nrow = 3, ncol = 3)+
  # facet_wrap(~ interaction(approach, model), nrow = 2, ncol = 3,
  #          labeller = labeller(`interaction(approach, model)` = my_labels)
  #            )+
  # facet_grid( rows = vars(model),col = vars(approach)
  #             ,scales = "free", space = "free") + # or facet_wrap(~group)
  theme_minimal(base_size = 20)+
  theme(
    #plot.title = element_text(size = 30),
    #legend.title = element_text(size = 28),
    #legend.text = element_text(size = 25),
    #axis.title = element_text(size = 20),
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, size = 15),
    axis.text.y = element_text(size = 15),
    panel.background = element_rect(fill = "transparent", color = NA),
  plot.background = element_rect(fill = "transparent", color = NA),
  panel.grid.major = element_line(color = "grey", linewidth = 0.1),
  panel.grid.minor = element_line(color = "grey", linewidth = 0.1)
    #,legend.key.size = unit(5, "lines")  # or "cm", "pt", etc.
  )
length(unique(plot_flow$seed))
```



# longueur du chemin : graphe en fonction de la longueur du chemin.
fixed group size and proportion of detoured packets


```{r}
# Réinitialiser les marges à leurs valeurs par défaut
library(patchwork)

x= "path_length"
y = "F1_score"
#z = "nb_detour"
colvar = "approach"
group = 9
my_model = "ISOF"
p_att = 0.1
detour = 0
path = 0
para_rate ="60Mbps"
proto= "Udp"
models_dispo = unique(dtf_flow$model)
models_dispo = models_dispo[! models_dispo %in% c("AE_CONTRACTIVE", "PCAthenAE_CONTRACTIVE", "AE_CLASS", "PCAthenAE_CLASS",  "AE_SIMPLE",  "PCAthenAE_SIMPLE", "INTERVAL", "PCAthenINTERVAL", "OCSVM", "PCAthenOCSVM")]
models_dispo = c( "THRESHOLD", "INTERVAL_DELAY",
  "SVM",  "REGLOG", # "CART","XGBOOST",
                  "DAE", "VAE") #"KMEANS", "ISOF",, "AE_SPARSE", "AE_LSTM", "AE_CONV1D"


names_no_pca <- models_dispo[!grepl("^PCAthen", models_dispo)]
names_pca <- models_dispo[grepl("^PCAthen", models_dispo)]

plot_flow <- dtf_flow[group_id == group & prop_att == p_att 
                      &  nb_detour == detour & protocol == proto
                      & parasite_rate == para_rate
                      & model %in% models_dispo]
plot_flow <- plot_flow[!duplicated(plot_flow[, ..to_distinct], fromLast = TRUE)]

min_score = 0#dtf_flow[, min(F1_score, na.rm = TRUE)]# min( dtf_flow$F1_score, na.rm = TRUE)
max_score = 1#max( dtf_flow$F1_score, na.rm = TRUE)

min_detour =plot_flow[, min(nb_detour, na.rm = TRUE)]#min( plot_flow$nb_detour, na.rm = TRUE)
max_detour = plot_flow[, max(nb_detour, na.rm = TRUE)]#max( plot_flow$nb_detour, na.rm = TRUE)

par(mfrow = c(4,2))
theta = 190 #180#220
phi = 320 #280
cex = 1
my_model = models_dispo[3]
plots_no_pca <- list()
plots_pca <- list()
for (my_model in models_dispo){
  name = my_model
  par(mar = c(0.5, 0,2.5, 0))
  
  #par(mar = c(4.1, 3.1, 3.1, 1.1))
  plot_flow_model <- plot_flow[model == my_model]
  #unique (plot_flow_model$parasite_rate)
  
  # plot_long <- plot_flow_model %>%
  # pivot_longer(
  #   cols = c(F1_score, Precision_mean, Recall_mean),
  #   names_to = "metric",
  #   values_to = "score"
  # )

# p <- ggplot(plot_long, aes(x = path_length, y = score, color = approach)) +
#   geom_point(aes(shape = interaction(metric, approach)), size = 2, stroke = 1, 
#              show.legend = c(color = FALSE, shape = FALSE)) +
#   geom_errorbar(
#     data = subset(plot_long, metric == "F1_score"),
#     aes(ymin = F1_ci_lower, ymax = F1_ci_upper, color = approach),
#     width = 1,
#     alpha = 0.6
#     , show.legend = c(color = FALSE)
#   ) +
#   scale_color_manual(values = c(
#     "supervised" = "#f8766d",
#     "unsupervised" = "#619cff",
#     "baseline" = "#00ba38"
#   )) +
#   scale_shape_manual(values = c(
#     "F1_score.supervised" = 15,
#     "F1_score.unsupervised" = 16,
#     "F1_score.baseline" = 17,
#     "Precision_mean.supervised" = 0,
#     "Precision_mean.unsupervised" = 1,
#     "Precision_mean.baseline" = 2,
#     "Recall_mean.supervised" = 12,
#     "Recall_mean.unsupervised" = 10,
#     "Recall_mean.baseline" = 8
#   )) +
#   coord_cartesian(ylim = c(min_score, max_score)) +
#   labs(
#     title = paste0(name),
#     x = "Number of additional on-path routers",
#     y = "Score"
#   ) +
#   theme_minimal() +
#   theme(
#     axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)
#   )
  
  p <- ggplot(plot_flow_model, aes(x = path_length, y = F1_score, color= approach, shape = approach)) +
    geom_point(size = 2,stroke = 1, show.legend = c(color = FALSE, shape = F)) +
    geom_errorbar(aes(
      ymin = F1_ci_lower,
      ymax = F1_ci_upper,
      color = "black"
    ),
    width = 0.5, # controls horizontal width of the bar
    alpha = 0.6, show.legend = c(color = FALSE, shape = FALSE),

  ) +
    scale_color_manual(
      values = c(
        "supervised" = "#f8766d",
        "unsupervised" = "#619cff",
        "baseline" = "#00ba38"
      )) +
    scale_shape_manual(
      values = c(
        "supervised" = 15,
        "unsupervised" = 16,
        "baseline" = 17
      )) +
    coord_cartesian(ylim = c(min_score, max_score)) +  # ← la bonne méthode
    labs(
      title = paste0(name), #,": \nParasite rate=", para_rate, "; Detour length=", detour+1),
      #F1_score; \nsize_group=", group, " \nprop_att=", p_att, ";
      x = "Number of additional on-path routers",
      y = TeX("$F_1$-Score")) +
    scale_x_discrete(breaks = seq(0,10,1), labels = seq(0,10,1), limits = seq(0,10,1))+
    theme_minimal()#+
    #theme(axis.text.x = element_text( angle = 90, hjust = 1, vjust = 0.5))
  if (my_model %in% names_pca){
    plots_pca[[my_model]] <- p
  }else
  {
    plots_no_pca[[my_model]] <- p
  }
  
  #print(p)
}
#wrap_plots(plots_pca)
# design <- "#AB#
#            CDEF
#            GHIJ
#            KLM#"
wrap_plots(plots_no_pca, design = design)
length(unique(plot_flow$seed))
```

### X by flows with CI
```{r}
# Réinitialiser les marges à leurs valeurs par défaut
library(patchwork)
library(dplyr)
library(tidyr)
library(ggplot2)

library(patchwork)

x= "path_length"
y = "F1_score"
#z = "nb_detour"
colvar = "approach"
group = 9
my_model = "ISOF"
p_att = 0.1
detour = "0" #0_1_3_5_7_9"
path = 0
para_rate ="60Mbps"
proto= "Udp"
models_dispo = unique(dtf_flow$model)
models_dispo = models_dispo[! models_dispo %in% c("AE_CONTRACTIVE", "PCAthenAE_CONTRACTIVE", "AE_CLASS", "PCAthenAE_CLASS",  "AE_SIMPLE",  "PCAthenAE_SIMPLE", "INTERVAL", "PCAthenINTERVAL", "OCSVM", "PCAthenOCSVM")]
models_dispo = c( "THRESHOLD", "INTERVAL_DELAY",
  "SVM",  "REGLOG", # "CART","XGBOOST",
                  "DAE", "VAE") #"KMEANS", "ISOF",, "AE_SPARSE", "AE_LSTM", "AE_CONV1D"


names_no_pca <- models_dispo[!grepl("^PCAthen", models_dispo)]
names_pca <- models_dispo[grepl("^PCAthen", models_dispo)]
graduation = c(0,2,4,6,8,10) #,1,3,5,7,9 )#, )
plot_flow <- dtf_flow[group_id == group & prop_att == p_att 
                      &  nb_detour == detour & protocol == proto
                      & parasite_rate == para_rate
                      & model %in% models_dispo
                      & path_length %in% graduation
                      &do_evolution == F
                      ]
#plot_flow <- plot_flow[!duplicated(plot_flow[, ..to_distinct], fromLast = TRUE)]

min_score = 0#dtf_flow[, min(F1_score, na.rm = TRUE)]# min( dtf_flow$F1_score, na.rm = TRUE)
max_score = 1#max( dtf_flow$F1_score, na.rm = TRUE)

min_detour =plot_flow[, min(nb_detour, na.rm = TRUE)]#min( plot_flow$nb_detour, na.rm = TRUE)
max_detour = plot_flow[, max(nb_detour, na.rm = TRUE)]#max( plot_flow$nb_detour, na.rm = TRUE)

par(mfrow = c(4,2))
theta = 190 #180#220
phi = 320 #280
cex = 1

plot_flow[approach == "baseline", approach := "Baseline"]
plot_flow[approach == "unsupervised", approach := "Unsupervised"]
plot_flow[approach == "supervised", approach := "Supervised"]
plot_flow[, facet_label := paste(approach, model, sep = ": ")]
plot_flow[, facet_label := factor(facet_label, levels = c(
  "Baseline: THRESHOLD",
  "Supervised: SVM",
  "Unsupervised: DAE",
  "Baseline: INTERVAL_DELAY",
  "Supervised: REGLOG",
  "Unsupervised: VAE",
  "Supervised: XGBOOST"
))]
# Create the faceted plot
ggplot(plot_flow, aes(x = path_length, y = F1_score, color= approach, shape = approach)) +
  geom_point(size = 1,stroke = 2, show.legend = c(color = FALSE, shape = FALSE)) +
  geom_errorbar(aes(
      ymin = F1_ci_lower,
      ymax = F1_ci_upper,
      color = "black"
    ),
    width = 0.5, # controls horizontal width of the bar
    alpha = 0.6, show.legend = c(color = FALSE, shape = FALSE),

  ) +
    scale_color_manual(
      values = c(
        "Supervised" = "#f8766d",
        "Unsupervised" = "#619cff",
        "Baseline" = "#00ba38"
      )) +
  scale_shape_manual(
      values = c(
        "Supervised" = 15,
        "Unsupervised" = 16,
        "Baseline" = 17
      )) +
    coord_cartesian(ylim = c(min_score, max_score)) +  # ← la bonne méthode
    labs(
      x = "Number of on-path routers",
      y = TeX("$F_1$-Score")) +
    scale_x_discrete(breaks = graduation, labels = graduation + 4, limits = graduation)+
  facet_wrap(~ facet_label, nrow = 3, ncol = 3)+
  # facet_wrap(~ interaction(approach, model), nrow = 2, ncol = 3,
  #          labeller = labeller(`interaction(approach, model)` = my_labels)
  #            )+
  # facet_grid( rows = vars(model),col = vars(approach)
  #             ,scales = "free", space = "free") + # or facet_wrap(~group)
  theme_minimal(base_size = 20)+
  theme(
    #plot.title = element_text(size = 30),
    #legend.title = element_text(size = 28),
    #legend.text = element_text(size = 25),
    #axis.title = element_text(size = 25),
    #axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1),
    axis.text.y = element_text(size = 15),
    panel.background = element_rect(fill = "transparent", color = NA),
  plot.background = element_rect(fill = "transparent", color = NA),
  panel.grid.major = element_line(color = "grey", linewidth = 0.1),
  panel.grid.minor = element_line(color = "grey", linewidth = 0.1)
    #,legend.key.size = unit(5, "lines")  # or "cm", "pt", etc.
  )
length(unique(plot_flow$seed))
```


### X by flows with boxplot
```{r}
# Réinitialiser les marges à leurs valeurs par défaut
library(patchwork)
library(dplyr)
library(tidyr)
library(ggplot2)

library(patchwork)

x= "path_length"
y = "F1_score"
#z = "nb_detour"
colvar = "approach"
group = 9 #342
my_model = "ISOF"
p_att = 0.1
detour = "0" #0_1_3_5_7_9"
path = 0
para_rate ="120Mbps"
proto= "Udp"
models_dispo = unique(dtf_flow_boxplot$model)
models_dispo = models_dispo[! models_dispo %in% c("AE_CONTRACTIVE", "PCAthenAE_CONTRACTIVE", "AE_CLASS", "PCAthenAE_CLASS",  "AE_SIMPLE",  "PCAthenAE_SIMPLE", "INTERVAL", "PCAthenINTERVAL", "OCSVM", "PCAthenOCSVM")]
models_dispo = c( "THRESHOLD", "INTERVAL_DELAY",
  "SVM",  "REGLOG", # "CART","XGBOOST",
                  "DAE", "VAE") #"KMEANS", "ISOF",, "AE_SPARSE", "AE_LSTM", "AE_CONV1D"


names_no_pca <- models_dispo[!grepl("^PCAthen", models_dispo)]
names_pca <- models_dispo[grepl("^PCAthen", models_dispo)]
graduation = c(0,2,4,6,8,10) #,1,3,5,7,9 )#, )
plot_flow <- dtf_flow_boxplot[group_id == group & prop_att == p_att 
                      &  nb_detour == detour & protocol == proto
                      & parasite_rate == para_rate
                      & model %in% models_dispo
                      & path_length %in% graduation
                      &do_evolution == F
                      & directory == "eleventh" #"ninth"
                      & (comment == "basic" | comment == "basic2")
                      #& dataset == "dtf_16"
                      ]
plot_flow$nb_detour = as.numeric(plot_flow$nb_detour)
plot_flow$path_length = as.factor(plot_flow$path_length)
#plot_flow <- plot_flow[!duplicated(plot_flow[, ..to_distinct], fromLast = TRUE)]

min_score = 0#dtf_flow[, min(F1_score, na.rm = TRUE)]# min( dtf_flow$F1_score, na.rm = TRUE)
max_score = 1#max( dtf_flow$F1_score, na.rm = TRUE)

min_detour =plot_flow[, min(nb_detour, na.rm = TRUE)]#min( plot_flow$nb_detour, na.rm = TRUE)
max_detour = plot_flow[, max(nb_detour, na.rm = TRUE)]#max( plot_flow$nb_detour, na.rm = TRUE)

par(mfrow = c(4,2))
theta = 190 #180#220
phi = 320 #280
cex = 1

plot_flow[approach == "baseline", approach := "Baseline"]
plot_flow[approach == "unsupervised", approach := "Unsupervised"]
plot_flow[approach == "supervised", approach := "Supervised"]
plot_flow[, facet_label := paste(approach, model, sep = ": ")]
plot_flow[, facet_label := factor(facet_label, levels = c(
  "Baseline: THRESHOLD",
  "Supervised: SVM",
  "Unsupervised: DAE",
  "Baseline: INTERVAL_DELAY",
  "Supervised: REGLOG",
  "Unsupervised: VAE",
  "Supervised: XGBOOST"
))]
# Create the faceted plot
ggplot(plot_flow, aes(x = path_length, y = F1_score, color= approach, shape = approach)) +
  #geom_point(size = 1,stroke = 2, show.legend = c(color = FALSE, shape = FALSE)) +
  # geom_errorbar(aes(
  #     ymin = F1_ci_lower,
  #     ymax = F1_ci_upper,
  #     color = "black"
  #   ),
  #   width = 0.5, # controls horizontal width of the bar
  #   alpha = 0.6, show.legend = c(color = FALSE, shape = FALSE),
  # 
  # ) +
  #geom_violin(aes(color = approach), show.legend = F)+
  geom_boxplot(outlier.color = "black", show.legend = F, notch = F
               , staplewidth = 0.7, varwidth = T
               , aes(fill = approach)
               , color = "black"
               #,coef = 0
               ,width = 0.4
               )+
    scale_color_manual(
      values = c(
        "Supervised" = "#f8766d",
        "Unsupervised" = "#619cff",
        "Baseline" = "#00ba38"
      )) +
  scale_fill_manual(
      values = c(
        "Supervised" = "#f8766d",
        "Unsupervised" = "#619cff",
        "Baseline" = "#00ba38"
      )) +
  scale_shape_manual(
      values = c(
        "Supervised" = 15,
        "Unsupervised" = 16,
        "Baseline" = 17
      )) +
    coord_cartesian(ylim = c(min_score, max_score)) +  # ← la bonne méthode
    labs(
      x = "Number of on-path routers",
      y = TeX("$F_1$-Score")) +
    scale_x_discrete(#breaks = graduation, 
                     labels = graduation + 4
                     #, limits = graduation
                     )+
  facet_wrap(~ facet_label, nrow = 3, ncol = 3)+
  # facet_wrap(~ interaction(approach, model), nrow = 2, ncol = 3,
  #          labeller = labeller(`interaction(approach, model)` = my_labels)
  #            )+
  # facet_grid( rows = vars(model),col = vars(approach)
  #             ,scales = "free", space = "free") + # or facet_wrap(~group)
  theme_minimal(base_size = 20)+
  theme(
    #plot.title = element_text(size = 30),
    #legend.title = element_text(size = 28),
    #legend.text = element_text(size = 25),
    #axis.title = element_text(size = 25),
    #axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1),
    axis.text.y = element_text(size = 15),
    panel.background = element_rect(fill = "transparent", color = NA),
  plot.background = element_rect(fill = "transparent", color = NA),
  panel.grid.major = element_line(color = "grey", linewidth = 0.1),
  panel.grid.minor = element_line(color = "grey", linewidth = 0.1)
    #,legend.key.size = unit(5, "lines")  # or "cm", "pt", etc.
  )
length(unique(plot_flow$seed))
```


### X by flows with trainondetour
```{r}
# Réinitialiser les marges à leurs valeurs par défaut
library(patchwork)
library(dplyr)
library(tidyr)
library(ggplot2)

library(patchwork)

x= "path_length"
y = "F1_score"
#z = "nb_detour"
colvar = "approach"
group = 9 #9,27,342
my_model = "ISOF"
p_att = 0.1
detour = "0_1_3_5_7_9"
path = 0
para_rate ="120Mbps"
proto= "Udp"
models_dispo = unique(dtf_flow_boxplot$model)
models_dispo = models_dispo[! models_dispo %in% c("AE_CONTRACTIVE", "PCAthenAE_CONTRACTIVE", "AE_CLASS", "PCAthenAE_CLASS",  "AE_SIMPLE",  "PCAthenAE_SIMPLE", "INTERVAL", "PCAthenINTERVAL", "OCSVM", "PCAthenOCSVM")]
models_dispo = c( "THRESHOLD", "INTERVAL_DELAY",
  "SVM",  "REGLOG", # "CART","XGBOOST",
                  "DAE", "VAE") #"KMEANS", "ISOF",, "AE_SPARSE", "AE_LSTM", "AE_CONV1D"


names_no_pca <- models_dispo[!grepl("^PCAthen", models_dispo)]
names_pca <- models_dispo[grepl("^PCAthen", models_dispo)]
graduation = c(0,2,4,6,8,10) #,1,3,5,7,9 )#, )
plot_flow <- dtf_flow_boxplot[group_id == group & prop_att == p_att 
                      &  nb_detour == detour 
                      & protocol == proto
                      & parasite_rate == para_rate
                      & model %in% models_dispo
                      & path_length %in% graduation
                      #& trainondetour == "0_1_3_5_7_9"
                      &do_evolution == F
                      & directory == "eleventh" #"ninth"
                      & comment == "basic" 
                      #& dataset == "dtf_16"
                      ]
#plot_flow$nb_detour = as.numeric(plot_flow$nb_detour)
plot_flow$path_length = as.factor(plot_flow$path_length)
#plot_flow <- plot_flow[!duplicated(plot_flow[, ..to_distinct], fromLast = TRUE)]

min_score = 0#dtf_flow[, min(F1_score, na.rm = TRUE)]# min( dtf_flow$F1_score, na.rm = TRUE)
max_score = 1#max( dtf_flow$F1_score, na.rm = TRUE)

#min_detour =plot_flow[, min(nb_detour, na.rm = TRUE)]#min( plot_flow$nb_detour, na.rm = TRUE)
#max_detour = plot_flow[, max(nb_detour, na.rm = TRUE)]#max( plot_flow$nb_detour, na.rm = TRUE)

par(mfrow = c(4,2))
theta = 190 #180#220
phi = 320 #280
cex = 1

plot_flow[approach == "baseline", approach := "Baseline"]
plot_flow[approach == "unsupervised", approach := "Unsupervised"]
plot_flow[approach == "supervised", approach := "Supervised"]
plot_flow[, facet_label := paste(approach, model, sep = ": ")]
plot_flow[, facet_label := factor(facet_label, levels = c(
  "Baseline: THRESHOLD",
  "Supervised: SVM",
  "Unsupervised: DAE",
  "Baseline: INTERVAL_DELAY",
  "Supervised: REGLOG",
  "Unsupervised: VAE",
  "Supervised: XGBOOST"
))]
# Create the faceted plot
ggplot(plot_flow, aes(x = path_length, y = F1_score, color= approach, shape = approach)) +
  #geom_point(size = 1,stroke = 2, show.legend = c(color = FALSE, shape = FALSE)) +
  # geom_errorbar(aes(
  #     ymin = F1_ci_lower,
  #     ymax = F1_ci_upper,
  #     color = "black"
  #   ),
  #   width = 0.5, # controls horizontal width of the bar
  #   alpha = 0.6, show.legend = c(color = FALSE, shape = FALSE),
  # 
  # ) +
  #geom_violin(aes(color = approach), show.legend = F)+
  geom_boxplot(outlier.color = "black", show.legend = F, notch = F
               , staplewidth = 0.7, varwidth = T
               , aes(fill = approach)
               , color = "black"
               #,coef = 0
               ,width = 0.4
               )+
    scale_color_manual(
      values = c(
        "Supervised" = "#f8766d",
        "Unsupervised" = "#619cff",
        "Baseline" = "#00ba38"
      )) +
  scale_fill_manual(
      values = c(
        "Supervised" = "#f8766d",
        "Unsupervised" = "#619cff",
        "Baseline" = "#00ba38"
      )) +
  scale_shape_manual(
      values = c(
        "Supervised" = 15,
        "Unsupervised" = 16,
        "Baseline" = 17
      )) +
    coord_cartesian(ylim = c(min_score, max_score)) +  # ← la bonne méthode
    labs(
      x = "Number of on-path routers",
      y = TeX("$F_1$-Score")) +
    scale_x_discrete(#breaks = graduation, 
                     labels = graduation + 4
                     #, limits = graduation
                     )+
  facet_wrap(~ facet_label, nrow = 3, ncol = 3)+
  # facet_wrap(~ interaction(approach, model), nrow = 2, ncol = 3,
  #          labeller = labeller(`interaction(approach, model)` = my_labels)
  #            )+
  # facet_grid( rows = vars(model),col = vars(approach)
  #             ,scales = "free", space = "free") + # or facet_wrap(~group)
  theme_minimal(base_size = 20)+
  theme(
    #plot.title = element_text(size = 30),
    #legend.title = element_text(size = 28),
    #legend.text = element_text(size = 25),
    #axis.title = element_text(size = 25),
    #axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1),
    axis.text.y = element_text(size = 15),
    panel.background = element_rect(fill = "transparent", color = NA),
  plot.background = element_rect(fill = "transparent", color = NA),
  panel.grid.major = element_line(color = "grey", linewidth = 0.1),
  panel.grid.minor = element_line(color = "grey", linewidth = 0.1)
    #,legend.key.size = unit(5, "lines")  # or "cm", "pt", etc.
  )
```




# longueur du detour: graphe en fonction de la longueur du detour.

```{r}
# Réinitialiser les marges à leurs valeurs par défaut
library(patchwork)

x= "nb_detour"
y = "F1_score"
#z = "nb_detour"
colvar = "approach"
group = 9
my_model = "ISOF"
p_att = 0.1
detour = 0
path = 0
para_rate ="60Mbps"
proto= "Udp"
models_dispo = unique(dtf_flow$model)
models_dispo = models_dispo[! models_dispo %in% c("AE_CONTRACTIVE", "PCAthenAE_CONTRACTIVE",  "AE_SIMPLE",  "PCAthenAE_SIMPLE", "INTERVAL", "PCAthenINTERVAL", "OCSVM", "PCAthenOCSVM")] #, "AE_CLASS", "PCAthenAE_CLASS"
models_dispo = c( "THRESHOLD", "INTERVAL_DELAY",
  "SVM",  "REGLOG", # "CART","XGBOOST",
                  "DAE", "VAE") #"KMEANS", "ISOF",, "AE_SPARSE", "AE_LSTM", "AE_CONV1D"

names_no_pca <- models_dispo[!grepl("^PCAthen", models_dispo)]
names_pca <- models_dispo[grepl("^PCAthen", models_dispo)]

plot_flow <- dtf_flow[group_id == group & prop_att == p_att 
                      &  path_length == path & protocol == proto
                      & parasite_rate == para_rate & nb_detour <= 10
                      & model %in% models_dispo]
plot_flow <- plot_flow[!duplicated(plot_flow[, ..to_distinct], fromLast = TRUE)]

min_score = 0#dtf_flow[, min(F1_score, na.rm = TRUE)]# min( dtf_flow$F1_score, na.rm = TRUE)
max_score = 1#max( dtf_flow$F1_score, na.rm = TRUE)

min_detour =plot_flow[, min(nb_detour, na.rm = TRUE)]#min( plot_flow$nb_detour, na.rm = TRUE)
max_detour = plot_flow[, max(nb_detour, na.rm = TRUE)]#max( plot_flow$nb_detour, na.rm = TRUE)

par(mfrow = c(4,2))
theta = 190 #180#220
phi = 320 #280
cex = 1
my_model = models_dispo[3]
plots_no_pca <- list()
plots_pca <- list()
for (my_model in models_dispo){
  name = my_model
  par(mar = c(0.5, 0,2.5, 0))
  
  #par(mar = c(4.1, 3.1, 3.1, 1.1))
  plot_flow_model <- plot_flow[model == my_model]
  #unique (plot_flow_model$parasite_rate)
  
  # plot_long <- plot_flow_model %>%
  # pivot_longer(
  #   cols = c(F1_score, Precision_mean, Recall_mean),
  #   names_to = "metric",
  #   values_to = "score"
  # )

# p <- ggplot(plot_long, aes(x = nb_detour, y = score, color = approach)) +
#   geom_point(aes(shape = interaction(metric, approach)), size = 2, stroke = 1, 
#              show.legend = c(color = FALSE, shape = FALSE)) +
#   geom_errorbar(
#     data = subset(plot_long, metric == "F1_score"),
#     aes(ymin = F1_ci_lower, ymax = F1_ci_upper, color = approach),
#     width = 1,
#     alpha = 0.6
#     , show.legend = c(color = FALSE)
#   ) +
#   scale_color_manual(values = c(
#     "supervised" = "#f8766d",
#     "unsupervised" = "#619cff",
#     "baseline" = "#00ba38"
#   )) +
#   scale_shape_manual(values = c(
#     "F1_score.supervised" = 15,
#     "F1_score.unsupervised" = 16,
#     "F1_score.baseline" = 17,
#     "Precision_mean.supervised" = 0,
#     "Precision_mean.unsupervised" = 1,
#     "Precision_mean.baseline" = 2,
#     "Recall_mean.supervised" = 12,
#     "Recall_mean.unsupervised" = 10,
#     "Recall_mean.baseline" = 8
#   )) +
#   coord_cartesian(ylim = c(min_score, max_score)) +
#   labs(
#     title = paste0(name),
#     x = "Number of on-detour routers",
#     y = "Score"
#   ) +
#   theme_minimal() +
#   theme(
#     axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)
#   )


# 
#   
  p <- ggplot(plot_flow_model, aes(x = nb_detour, y = F1_score, color= approach, shape = approach)) +
    geom_point(size = 1,stroke = 2, show.legend = c(color = FALSE)) +
    geom_errorbar(aes(
      ymin = F1_ci_lower,
      ymax = F1_ci_upper,
      color = "black"
    ),
    width = 0.5, # controls horizontal width of the bar
    alpha = 0.6, show.legend = c(color = FALSE, shape = FALSE),

  ) +
    scale_color_manual(
      values = c(
        "supervised" = "#f8766d",
        "unsupervised" = "#619cff",
        "baseline" = "#00ba38"
      )) +
    scale_shape_manual(
      values = c(
        "supervised" = 15,
        "unsupervised" = 16,
        "baseline" = 17
      )) +
    coord_cartesian(ylim = c(min_score, max_score)) +  # ← la bonne méthode
    labs(
      title = paste0(name), #,":  \nParasite Rate=", para_rate, "; Path length=", path+4),
      #F1_score; \nsize_group=", group, " \nprop_att=", p_att, ";
      x = "Number of on-detour routers",
      y = TeX("$F_1$-Score")) +
    scale_x_discrete(breaks = seq(-1,10,1), labels = seq(0,11,1), limits = seq(-1,10,1))+
    theme_minimal()#+
    #theme(axis.text.x = element_text( angle = 90, hjust = 1, vjust = 0.5))
  if (my_model %in% names_pca){
    plots_pca[[my_model]] <- p
  }else
  {
    plots_no_pca[[my_model]] <- p
  }
  
  #print(p)
}
#wrap_plots(plots_pca)
# design <- "ACE
#            BDF"
wrap_plots(plots_no_pca, design = design)

```

### X by flows with CI
```{r}
# Réinitialiser les marges à leurs valeurs par défaut
library(patchwork)

x= "nb_detour"
y = "F1_score"
#z = "nb_detour"
colvar = "approach"
group = 9
my_model = "ISOF"
p_att = 0.1
detour = 0
path = 0
para_rate ="60Mbps"
proto= "Udp"
models_dispo = unique(dtf_flow$model)
models_dispo = models_dispo[! models_dispo %in% c("AE_CONTRACTIVE", "PCAthenAE_CONTRACTIVE",  "AE_SIMPLE",  "PCAthenAE_SIMPLE", "INTERVAL", "PCAthenINTERVAL", "OCSVM", "PCAthenOCSVM")] #, "AE_CLASS", "PCAthenAE_CLASS"
models_dispo = c( "THRESHOLD", "INTERVAL_DELAY",
  "SVM",  "REGLOG", # "CART","XGBOOST",
                  "DAE", "VAE") #"KMEANS", "ISOF",, "AE_SPARSE", "AE_LSTM", "AE_CONV1D"

names_no_pca <- models_dispo[!grepl("^PCAthen", models_dispo)]
names_pca <- models_dispo[grepl("^PCAthen", models_dispo)]

graduation <- c("0","1","3","5","7","9") #, 2,4,6,8,10)
plot_flow <- dtf_flow[group_id == group & prop_att == p_att 
                      &  path_length == path & protocol == proto
                      & parasite_rate == para_rate #& nb_detour <= 10
                      & model %in% models_dispo
                      #& nb_detour %in% graduation
                      &nb_detour == trainondetour
                      & do_evolution == F
                      ]
plot_flow <- plot_flow[nb_detour %in% graduation]
plot_flow$nb_detour = as.numeric(plot_flow$nb_detour)
graduation = as.numeric(graduation)
#plot_flow <- plot_flow[!duplicated(plot_flow[, ..to_distinct], fromLast = TRUE)]

min_score = 0#dtf_flow[, min(F1_score, na.rm = TRUE)]# min( dtf_flow$F1_score, na.rm = TRUE)
max_score = 1#max( dtf_flow$F1_score, na.rm = TRUE)

min_detour =plot_flow[, min(nb_detour, na.rm = TRUE)]#min( plot_flow$nb_detour, na.rm = TRUE)
max_detour = plot_flow[, max(nb_detour, na.rm = TRUE)]#max( plot_flow$nb_detour, na.rm = TRUE)

par(mfrow = c(4,2))
theta = 190 #180#220
phi = 320 #280
cex = 1

plot_flow[approach == "baseline", approach := "Baseline"]
plot_flow[approach == "unsupervised", approach := "Unsupervised"]
plot_flow[approach == "supervised", approach := "Supervised"]
plot_flow[, facet_label := paste(approach, model, sep = ": ")]
plot_flow[, facet_label := factor(facet_label, levels = c(
  "Baseline: THRESHOLD",
  "Supervised: SVM",
  "Unsupervised: DAE",
  "Baseline: INTERVAL_DELAY",
  "Supervised: REGLOG",
  "Unsupervised: VAE"
))]
plot_flow[, facet_label := factor(facet_label, levels = c(
  "Baseline: THRESHOLD",
  "Baseline: INTERVAL_DELAY",
  "Supervised: SVM",
  "Supervised: REGLOG",
  "Unsupervised: DAE",
  "Unsupervised: VAE"
))]
# Create the faceted plot
ggplot(plot_flow, aes(x = nb_detour, y = F1_score, color= approach, shape = approach)) +
  geom_point(size = 1,stroke = 2, show.legend = c(color = FALSE, shape = FALSE)) +
  geom_errorbar(aes(
      ymin = F1_ci_lower,
      ymax = F1_ci_upper,
      color = "black"
    ),
    width = 0.5, # controls horizontal width of the bar
    alpha = 0.6, show.legend = c(color = FALSE, shape = FALSE),

  ) +
    scale_color_manual(
      values = c(
        "Supervised" = "#f8766d",
        "Unsupervised" = "#619cff",
        "Baseline" = "#00ba38"
      )) +
  scale_shape_manual(
      values = c(
        "Supervised" = 15,
        "Unsupervised" = 16,
        "Baseline" = 17
      )) +
    coord_cartesian(ylim = c(min_score, max_score)) +  # ← la bonne méthode
    labs(
      x = "Number of on-detour routers",
      y = TeX("$F_1$-Score")) +
    scale_x_discrete(breaks = graduation, labels = as.numeric(graduation) +1, limits = graduation)+
  facet_wrap(~ facet_label, nrow = 3, ncol = 2)+
  # facet_wrap(~ interaction(approach, model), nrow = 2, ncol = 3,
  #          labeller = labeller(`interaction(approach, model)` = my_labels)
  #            )+
  # facet_grid( rows = vars(model),col = vars(approach)
  #             ,scales = "free", space = "free") + # or facet_wrap(~group)
  theme_minimal(base_size = 20)+
  theme(
    #plot.title = element_text(size = 30),
    #legend.title = element_text(size = 28),
    #legend.text = element_text(size = 25),
    #axis.title = element_text(size = 25),
    #axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1),
    axis.text.y = element_text(size = 15),
    panel.background = element_rect(fill = "transparent", color = NA),
  plot.background = element_rect(fill = "transparent", color = NA),
  panel.grid.major = element_line(color = "grey", linewidth = 0.1),
  panel.grid.minor = element_line(color = "grey", linewidth = 0.1)
    #,legend.key.size = unit(5, "lines")  # or "cm", "pt", etc.
  )
length(unique(plot_flow$seed))
```


### X by flows with boxplot
```{r}
# Réinitialiser les marges à leurs valeurs par défaut
library(patchwork)

x= "nb_detour"
y = "F1_score"
#z = "nb_detour"
colvar = "approach"
group = 9
my_model = "ISOF"
p_att = 0.1
detour = 0
path = 0
para_rate ="120Mbps"
proto= "Udp"
models_dispo = unique(dtf_flow_boxplot$model)
models_dispo = models_dispo[! models_dispo %in% c("AE_CONTRACTIVE", "PCAthenAE_CONTRACTIVE",  "AE_SIMPLE",  "PCAthenAE_SIMPLE", "INTERVAL", "PCAthenINTERVAL", "OCSVM", "PCAthenOCSVM")] #, "AE_CLASS", "PCAthenAE_CLASS"
models_dispo = c( "THRESHOLD", "INTERVAL_DELAY",
  "SVM",  "REGLOG", # "CART","XGBOOST",
                  "DAE", "VAE") #"KMEANS", "ISOF",, "AE_SPARSE", "AE_LSTM", "AE_CONV1D"

names_no_pca <- models_dispo[!grepl("^PCAthen", models_dispo)]
names_pca <- models_dispo[grepl("^PCAthen", models_dispo)]

graduation <- c("0","1","3","5","7","9") #, 2,4,6,8,10)
plot_flow <- dtf_flow_boxplot[group_id == group & prop_att == p_att 
                      &  path_length == path & protocol == proto
                      & parasite_rate == para_rate #& nb_detour <= 10
                      & model %in% models_dispo
                      #& nb_detour %in% graduation
                      &nb_detour == trainondetour
                      & do_evolution == F
                      & comment == "basic"
                      & directory == "eleventh" #"ninth"
                      #& dataset == "dtf_16"
                      ]
plot_flow <- plot_flow[nb_detour %in% graduation]
plot_flow$nb_detour = as.factor(plot_flow$nb_detour)
graduation = as.numeric(graduation)
#plot_flow <- plot_flow[!duplicated(plot_flow[, ..to_distinct], fromLast = TRUE)]

min_score = 0#dtf_flow[, min(F1_score, na.rm = TRUE)]# min( dtf_flow$F1_score, na.rm = TRUE)
max_score = 1#max( dtf_flow$F1_score, na.rm = TRUE)

# min_detour =plot_flow[, min(nb_detour, na.rm = TRUE)]#min( plot_flow$nb_detour, na.rm = TRUE)
# max_detour = plot_flow[, max(nb_detour, na.rm = TRUE)]#max( plot_flow$nb_detour, na.rm = TRUE)

par(mfrow = c(4,2))
theta = 190 #180#220
phi = 320 #280
cex = 1

plot_flow[approach == "baseline", approach := "Baseline"]
plot_flow[approach == "unsupervised", approach := "Unsupervised"]
plot_flow[approach == "supervised", approach := "Supervised"]
plot_flow[, facet_label := paste(approach, model, sep = ": ")]
plot_flow[, facet_label := factor(facet_label, levels = c(
  "Baseline: THRESHOLD",
  "Supervised: SVM",
  "Unsupervised: DAE",
  "Baseline: INTERVAL_DELAY",
  "Supervised: REGLOG",
  "Unsupervised: VAE"
))]
# Create the faceted plot
ggplot(plot_flow, aes(x = nb_detour, y = F1_score, color= approach, shape = approach)) +
  #geom_point(size = 1,stroke = 2, show.legend = c(color = FALSE, shape = FALSE)) +
  # geom_errorbar(aes(
  #     ymin = F1_ci_lower,
  #     ymax = F1_ci_upper,
  #     color = "black"
  #   ),
  #   width = 0.5, # controls horizontal width of the bar
  #   alpha = 0.6, show.legend = c(color = FALSE, shape = FALSE),
  # 
  # ) +
  #geom_violin(aes(color = approach), show.legend = F)+
  geom_boxplot(outlier.color = "black", show.legend = F, notch = F
               , staplewidth = 0.7, varwidth = T
               , aes(fill = approach)
               , color = "black"
               #,coef = 0
               ,width = 0.4
               )+
    scale_color_manual(
      values = c(
        "Supervised" = "#f8766d",
        "Unsupervised" = "#619cff",
        "Baseline" = "#00ba38"
      )) +
  scale_fill_manual(
      values = c(
        "Supervised" = "#f8766d",
        "Unsupervised" = "#619cff",
        "Baseline" = "#00ba38"
      )) +
  scale_shape_manual(
      values = c(
        "Supervised" = 15,
        "Unsupervised" = 16,
        "Baseline" = 17
      )) +
    coord_cartesian(ylim = c(min_score, max_score)) +  # ← la bonne méthode
    labs(
      x = "Number of on-detour routers",
      y = TeX("$F_1$-Score")) +
    scale_x_discrete(#breaks = graduation, 
                     labels = as.numeric(graduation) +1
                    # , limits = graduation
                    )+
  facet_wrap(~ facet_label, nrow = 2, ncol = 3)+
  # facet_wrap(~ interaction(approach, model), nrow = 2, ncol = 3,
  #          labeller = labeller(`interaction(approach, model)` = my_labels)
  #            )+
  # facet_grid( rows = vars(model),col = vars(approach)
  #             ,scales = "free", space = "free") + # or facet_wrap(~group)
  theme_minimal(base_size = 20)+
  theme(
    #plot.title = element_text(size = 30),
    #legend.title = element_text(size = 28),
    #legend.text = element_text(size = 25),
    #axis.title = element_text(size = 25),
    #axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1),
    axis.text.y = element_text(size = 15),
    panel.background = element_rect(fill = "transparent", color = NA),
  plot.background = element_rect(fill = "transparent", color = NA),
  panel.grid.major = element_line(color = "grey", linewidth = 0.1),
  panel.grid.minor = element_line(color = "grey", linewidth = 0.1)
    #,legend.key.size = unit(5, "lines")  # or "cm", "pt", etc.
  )
length(unique(plot_flow$seed))
```



### X several training with CI
```{r}
# Réinitialiser les marges à leurs valeurs par défaut
library(patchwork)

x= "nb_detour"
y = "F1_score"
#z = "nb_detour"
colvar = "approach"
group = 9
my_model = "ISOF"
p_att = 0.1
detour = 0
path = 0
para_rate ="60Mbps"
proto= "Udp"
models_dispo = unique(dtf_flow$model)
models_dispo = models_dispo[! models_dispo %in% c("AE_CONTRACTIVE", "PCAthenAE_CONTRACTIVE",  "AE_SIMPLE",  "PCAthenAE_SIMPLE", "INTERVAL", "PCAthenINTERVAL", "OCSVM", "PCAthenOCSVM")] #, "AE_CLASS", "PCAthenAE_CLASS"
models_dispo = c( "THRESHOLD", "INTERVAL_DELAY",
  "SVM","REGLOG", # "CART","XGBOOST",
                  "DAE", "VAE") #"KMEANS", "ISOF",, "AE_SPARSE", "AE_LSTM", "AE_CONV1D"

names_no_pca <- models_dispo[!grepl("^PCAthen", models_dispo)]
names_pca <- models_dispo[grepl("^PCAthen", models_dispo)]

graduation <- c("0_1_3_5_7_9", "0","1","3","5","7","9") #2,4,6,8,10, #"0","1","3","5","7","9")#,
plot_flow <- dtf_flow[group_id == group & prop_att == p_att 
                      &  path_length == path & protocol == proto
                      & parasite_rate == para_rate #& nb_detour <= 10
                      & model %in% models_dispo
                      & nb_detour %in% graduation
                     & trainondetour == "0" #nb_detour #"5" #
                     & do_evolution == T
                     ]
#plot_flow <- plot_flow[!duplicated(plot_flow[, ..to_distinct], fromLast = TRUE)]

min_score = 0#dtf_flow[, min(F1_score, na.rm = TRUE)]# min( dtf_flow$F1_score, na.rm = TRUE)
max_score = 1#max( dtf_flow$F1_score, na.rm = TRUE)

#min_detour =plot_flow[, min(nb_detour, na.rm = TRUE)]#min( plot_flow$nb_detour, na.rm = TRUE)
#max_detour = plot_flow[, max(nb_detour, na.rm = TRUE)]#max( plot_flow$nb_detour, na.rm = TRUE)

par(mfrow = c(4,2))
theta = 190 #180#220
phi = 320 #280
cex = 1

plot_flow[approach == "baseline", approach := "Baseline"]
plot_flow[approach == "unsupervised", approach := "Unsupervised"]
plot_flow[approach == "supervised", approach := "Supervised"]
plot_flow[, facet_label := paste(approach, model, sep = ": ")]
plot_flow[, facet_label := factor(facet_label, levels = c(
  "Baseline: THRESHOLD",
  "Supervised: SVM",
  "Unsupervised: DAE",
  "Baseline: INTERVAL_DELAY",
  "Supervised: REGLOG",
  "Unsupervised: VAE",
  "Supervised: XGBOOST"
))]
# Create the faceted plot
ggplot(plot_flow, aes(x = nb_detour, y = F1_score, color= approach, shape = approach)) +
  geom_point(size = 1,stroke = 2, show.legend = c(color = FALSE, shape = FALSE)) +
  geom_errorbar(aes(
      ymin = F1_ci_lower,
      ymax = F1_ci_upper,
      color = "black"
    ),
    width = 0.5, # controls horizontal width of the bar
    alpha = 0.6, show.legend = c(color = FALSE, shape = FALSE),

  ) +
    scale_color_manual(
      values = c(
        "Supervised" = "#f8766d",
        "Unsupervised" = "#619cff",
        "Baseline" = "#00ba38"
      )) +
  scale_shape_manual(
      values = c(
        "Supervised" = 15,
        "Unsupervised" = 16,
        "Baseline" = 17
      )) +
    coord_cartesian(ylim = c(min_score, max_score)) +  # ← la bonne méthode
    labs(
      x = "Number of on-detour routers",
      y = TeX("$F_1$-Score")) +
    #scale_x_discrete(breaks = graduation, labels = graduation +1, limits = graduation)+
  scale_x_discrete( labels = c(1,2,4,6,8,10))+
  facet_wrap(~ facet_label, nrow = 3, ncol = 3)+
  # facet_wrap(~ interaction(approach, model), nrow = 2, ncol = 3,
  #          labeller = labeller(`interaction(approach, model)` = my_labels)
  #            )+
  # facet_grid( rows = vars(model),col = vars(approach)
  #             ,scales = "free", space = "free") + # or facet_wrap(~group)
  theme_minimal(base_size = 20)+
  theme(
    #plot.title = element_text(size = 30),
    #legend.title = element_text(size = 28),
    #legend.text = element_text(size = 25),
    #axis.title = element_text(size = 25),
    #axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1),
    axis.text.y = element_text(size = 15),
    panel.background = element_rect(fill = "transparent", color = NA),
  plot.background = element_rect(fill = "transparent", color = NA),
  panel.grid.major = element_line(color = "grey", linewidth = 0.1),
  panel.grid.minor = element_line(color = "grey", linewidth = 0.1)
    #,legend.key.size = unit(5, "lines")  # or "cm", "pt", etc.
  )
length(unique(plot_flow$seed))
```


### X several training with boxplot
```{r}
# Réinitialiser les marges à leurs valeurs par défaut
library(patchwork)

x= "nb_detour"
y = "F1_score"
#z = "nb_detour"
colvar = "approach"
group = 9
my_model = "ISOF"
p_att = 0.1
detour = "0" #"0_1_3_5_7_9" # "0" #"5" #"0_1_3_5_7_9"
path = 0
para_rate ="120Mbps"
proto= "Udp"
models_dispo = unique(dtf_flow_boxplot$model)
models_dispo = models_dispo[! models_dispo %in% c("AE_CONTRACTIVE", "PCAthenAE_CONTRACTIVE",  "AE_SIMPLE",  "PCAthenAE_SIMPLE", "INTERVAL", "PCAthenINTERVAL", "OCSVM", "PCAthenOCSVM")] #, "AE_CLASS", "PCAthenAE_CLASS"
models_dispo = c( "THRESHOLD", "INTERVAL_DELAY",
  "SVM","REGLOG", # "CART","XGBOOST",
                  "DAE", "VAE") #"KMEANS", "ISOF",, "AE_SPARSE", "AE_LSTM", "AE_CONV1D"

names_no_pca <- models_dispo[!grepl("^PCAthen", models_dispo)]
names_pca <- models_dispo[grepl("^PCAthen", models_dispo)]

graduation <- c("0_1_3_5_7_9", "0","1","3","5","7","9") #2,4,6,8,10, #"0","1","3","5","7","9")#,
plot_flow <- dtf_flow_boxplot[group_id == group & prop_att == p_att 
                      &  path_length == path & protocol == proto
                      & parasite_rate == para_rate #& nb_detour <= 10
                      & model %in% models_dispo
                      & nb_detour %in% graduation
                     & trainondetour == detour  #nb_detour #"5" #
                     & do_evolution == T #F#T
                     & (comment == "basic" | comment == "basic2")
                      & directory == "eleventh" #"ninth"
                      #& dataset == "dtf_16"
                     ]
#plot_flow <- plot_flow[!duplicated(plot_flow[, ..to_distinct], fromLast = TRUE)]

min_score = 0#dtf_flow[, min(F1_score, na.rm = TRUE)]# min( dtf_flow$F1_score, na.rm = TRUE)
max_score = 1#max( dtf_flow$F1_score, na.rm = TRUE)

#min_detour =plot_flow[, min(nb_detour, na.rm = TRUE)]#min( plot_flow$nb_detour, na.rm = TRUE)
#max_detour = plot_flow[, max(nb_detour, na.rm = TRUE)]#max( plot_flow$nb_detour, na.rm = TRUE)

par(mfrow = c(4,2))
theta = 190 #180#220
phi = 320 #280
cex = 1

plot_flow[approach == "baseline", approach := "Baseline"]
plot_flow[approach == "unsupervised", approach := "Unsupervised"]
plot_flow[approach == "supervised", approach := "Supervised"]
plot_flow[, facet_label := paste(approach, model, sep = ": ")]
plot_flow[, facet_label := factor(facet_label, levels = c(
  "Baseline: THRESHOLD",
  "Supervised: SVM",
  "Unsupervised: DAE",
  "Baseline: INTERVAL_DELAY",
  "Supervised: REGLOG",
  "Unsupervised: VAE",
  "Supervised: XGBOOST"
))]
# Create the faceted plot
ggplot(plot_flow, aes(x = nb_detour, y = F1_score, color= approach, shape = approach)) +
  # geom_point(size = 1,stroke = 2, show.legend = c(color = FALSE, shape = FALSE)) +
  # geom_errorbar(aes(
  #     ymin = F1_ci_lower,
  #     ymax = F1_ci_upper,
  #     color = "black"
  #   ),
  #   width = 0.5, # controls horizontal width of the bar
  #   alpha = 0.6, show.legend = c(color = FALSE, shape = FALSE),
  # 
  # ) +
  #geom_violin(aes(color = approach), show.legend = F)+
  geom_boxplot(outlier.color = "black", show.legend = F, notch = F
               , staplewidth = 0.7, varwidth = T
               , aes(fill = approach)
               , color = "black"
               #,coef = 0
               ,width = 0.4
               )+
    scale_color_manual(
      values = c(
        "Supervised" = "#f8766d",
        "Unsupervised" = "#619cff",
        "Baseline" = "#00ba38"
      )) +
  scale_fill_manual(
      values = c(
        "Supervised" = "#f8766d",
        "Unsupervised" = "#619cff",
        "Baseline" = "#00ba38"
      )) +
  scale_shape_manual(
      values = c(
        "Supervised" = 15,
        "Unsupervised" = 16,
        "Baseline" = 17
      )) +
    coord_cartesian(ylim = c(min_score, max_score)) +  # ← la bonne méthode
    labs(
      x = "Number of on-detour routers",
      y = TeX("$F_1$-Score")) +
    #scale_x_discrete(breaks = graduation, labels = graduation +1, limits = graduation)+
  scale_x_discrete( labels = c(1,2,4,6,8,10))+
  facet_wrap(~ facet_label, nrow = 3, ncol = 3)+
  # facet_wrap(~ interaction(approach, model), nrow = 2, ncol = 3,
  #          labeller = labeller(`interaction(approach, model)` = my_labels)
  #            )+
  # facet_grid( rows = vars(model),col = vars(approach)
  #             ,scales = "free", space = "free") + # or facet_wrap(~group)
  theme_minimal(base_size = 20)+
  theme(
    #plot.title = element_text(size = 30),
    #legend.title = element_text(size = 28),
    #legend.text = element_text(size = 25),
    #axis.title = element_text(size = 25),
    #axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1),
    axis.text.y = element_text(size = 15),
    panel.background = element_rect(fill = "transparent", color = NA),
  plot.background = element_rect(fill = "transparent", color = NA),
  panel.grid.major = element_line(color = "grey", linewidth = 0.1),
  panel.grid.minor = element_line(color = "grey", linewidth = 0.1)
    #,legend.key.size = unit(5, "lines")  # or "cm", "pt", etc.
  )
length(unique(plot_flow$seed))
```

### X several training with boxplot generic model 1
```{r}
# Réinitialiser les marges à leurs valeurs par défaut
library(patchwork)

x= "nb_detour"
y = "F1_score"
#z = "nb_detour"
colvar = "approach"
group = 9
my_model = "ISOF"
p_att = 0.1
detour = "0_1_3_5_7_9" #"0_1_3_5_7_9" # "0" #"5" #"0_1_3_5_7_9"
path = 0
para_rate ="120Mbps"
proto= "Udp"
models_dispo = unique(dtf_flow_boxplot$model)
models_dispo = models_dispo[! models_dispo %in% c("AE_CONTRACTIVE", "PCAthenAE_CONTRACTIVE",  "AE_SIMPLE",  "PCAthenAE_SIMPLE", "INTERVAL", "PCAthenINTERVAL", "OCSVM", "PCAthenOCSVM")] #, "AE_CLASS", "PCAthenAE_CLASS"
models_dispo = c( "THRESHOLD", "INTERVAL_DELAY",
  "SVM","REGLOG", # "CART","XGBOOST",
                  "DAE", "VAE") #"KMEANS", "ISOF",, "AE_SPARSE", "AE_LSTM", "AE_CONV1D"

names_no_pca <- models_dispo[!grepl("^PCAthen", models_dispo)]
names_pca <- models_dispo[grepl("^PCAthen", models_dispo)]

trainingdetour = "0_1_3_5_7_9"
trainingdetourplus = "1_2_4_6_8_10"
graduation <- c(trainingdetour, "0","1","3","5","7","9")
plot_flow <- dtf_flow_boxplot[group_id == group & prop_att == p_att 
                      &  path_length == path & protocol == proto
                      & parasite_rate == para_rate #& nb_detour <= 10
                      & model %in% models_dispo
                      & nb_detour %in% graduation
                     & trainondetour == nb_detour  #nb_detour #"5" #
                     & do_evolution == F #F#T
                     & (comment == "basic" | comment == "basic2")
                      & directory == "eleventh" #"ninth"
                      #& dataset == "dtf_16"
                     ]
#plot_flow <- plot_flow[!duplicated(plot_flow[, ..to_distinct], fromLast = TRUE)]

min_score = 0#dtf_flow[, min(F1_score, na.rm = TRUE)]# min( dtf_flow$F1_score, na.rm = TRUE)
max_score = 1#max( dtf_flow$F1_score, na.rm = TRUE)

#min_detour =plot_flow[, min(nb_detour, na.rm = TRUE)]#min( plot_flow$nb_detour, na.rm = TRUE)
#max_detour = plot_flow[, max(nb_detour, na.rm = TRUE)]#max( plot_flow$nb_detour, na.rm = TRUE)

par(mfrow = c(4,2))
theta = 190 #180#220
phi = 320 #280
cex = 1

plot_flow[approach == "baseline", approach := "Baseline"]
plot_flow[approach == "unsupervised", approach := "Unsupervised"]
plot_flow[approach == "supervised", approach := "Supervised"]
plot_flow[, facet_label := paste(approach, model, sep = ": ")]
plot_flow[, facet_label := factor(facet_label, levels = c(
  "Baseline: THRESHOLD",
  "Supervised: SVM",
  "Unsupervised: DAE",
  "Baseline: INTERVAL_DELAY",
  "Supervised: REGLOG",
  "Unsupervised: VAE",
  "Supervised: XGBOOST"
))]

plot_flow[,nb_detour := factor(nb_detour, 
                               levels = c(trainingdetour,"0","1","3","5","7","9"), #,"0_1_3_5_7","0_1_3_5","0_1_3","0_1"
                               labels = c(trainingdetourplus, "1","2","4","6","8","10"), ordered = T)]
# Create the faceted plot
ggplot(plot_flow, aes(x = nb_detour, y = F1_score, color= approach, shape = approach)) +
  # geom_point(size = 1,stroke = 2, show.legend = c(color = FALSE, shape = FALSE)) +
  # geom_errorbar(aes(
  #     ymin = F1_ci_lower,
  #     ymax = F1_ci_upper,
  #     color = "black"
  #   ),
  #   width = 0.5, # controls horizontal width of the bar
  #   alpha = 0.6, show.legend = c(color = FALSE, shape = FALSE),
  # 
  # ) +
  #geom_violin(aes(color = approach), show.legend = F)+
  geom_boxplot(outlier.color = "black", show.legend = F, notch = F
               , staplewidth = 0.7, varwidth = T
               , aes(fill = approach)
               , color = "black"
               #,coef = 0
               ,width = 0.4
               )+
    scale_color_manual(
      values = c(
        "Supervised" = "#f8766d",
        "Unsupervised" = "#619cff",
        "Baseline" = "#00ba38"
      )) +
  scale_fill_manual(
      values = c(
        "Supervised" = "#f8766d",
        "Unsupervised" = "#619cff",
        "Baseline" = "#00ba38"
      )) +
  scale_shape_manual(
      values = c(
        "Supervised" = 15,
        "Unsupervised" = 16,
        "Baseline" = 17
      )) +
    coord_cartesian(ylim = c(min_score, max_score)) +  # ← la bonne méthode
    labs(
      x = "Number of on-detour routers",
      y = TeX("$F_1$-Score")) +
    #scale_x_discrete(breaks = graduation, labels = graduation +1, limits = graduation)+
  scale_x_discrete( labels = c("1_2_4_6_8_10", "1","2","4",6,8,10))+
  facet_wrap(~ facet_label, nrow = 3, ncol = 3)+
  # facet_wrap(~ interaction(approach, model), nrow = 2, ncol = 3,
  #          labeller = labeller(`interaction(approach, model)` = my_labels)
  #            )+
  # facet_grid( rows = vars(model),col = vars(approach)
  #             ,scales = "free", space = "free") + # or facet_wrap(~group)
  theme_minimal(base_size = 20)+
  theme(
    #plot.title = element_text(size = 30),
    #legend.title = element_text(size = 28),
    #legend.text = element_text(size = 25),
    #axis.title = element_text(size = 25),
    axis.text.x = element_text(angle = 40,  hjust = 1), 
    axis.text.y = element_text(size = 15),
    panel.background = element_rect(fill = "transparent", color = NA),
  plot.background = element_rect(fill = "transparent", color = NA),
  panel.grid.major = element_line(color = "grey", linewidth = 0.1),
  panel.grid.minor = element_line(color = "grey", linewidth = 0.1)
    #,legend.key.size = unit(5, "lines")  # or "cm", "pt", etc.
  )
length(unique(plot_flow$seed))
```


### X several training with boxplot for several trainingdetour
```{r}
# Réinitialiser les marges à leurs valeurs par défaut
library(patchwork)

x= "nb_detour"
y = "F1_score"
#z = "nb_detour"
colvar = "approach"
group = 9 #9,27,342
my_model = "ISOF"
p_att = 0.1
detour = 0
path = 0
para_rate ="120Mbps"
proto= "Udp"
models_dispo = unique(dtf_flow_boxplot$model)
models_dispo = models_dispo[! models_dispo %in% c("AE_CONTRACTIVE", "PCAthenAE_CONTRACTIVE",  "AE_SIMPLE",  "PCAthenAE_SIMPLE", "INTERVAL", "PCAthenINTERVAL", "OCSVM", "PCAthenOCSVM")] #, "AE_CLASS", "PCAthenAE_CLASS"
models_dispo = c( "THRESHOLD", "INTERVAL_DELAY",
  "SVM","REGLOG", # "CART","XGBOOST",
                  "DAE", "VAE") #"KMEANS", "ISOF",, "AE_SPARSE", "AE_LSTM", "AE_CONV1D"

names_no_pca <- models_dispo[!grepl("^PCAthen", models_dispo)]
names_pca <- models_dispo[grepl("^PCAthen", models_dispo)]
trainingdetour = "0_1_3_5_7_9"
trainingdetourplus = "1_2_4_6_8_10"
graduation <- c(trainingdetour, "0","1","3","5","7","9") # ,"2","4","6","8","10") #, #"0","1","3","5","7","9")#, "0_1_3_5_7","0_1_3_5","0_1_3","0_1",
plot_flow <- dtf_flow_boxplot[group_id == group & prop_att == p_att 
                      &  path_length == path & protocol == proto
                      & parasite_rate == para_rate #& nb_detour <= 10
                      & model %in% models_dispo
                      & nb_detour %in% graduation
                     & trainondetour  %in% c(trainingdetour) #%in% c(trainingdetour) #==  nb_detour 
                     & do_evolution == T #T #F #T#F
                     & (comment == "basic")
                      & directory == "eleventh" #"ninth"
                      #& dataset == "dtf_16"
                     ]
#plot_flow <- plot_flow[!duplicated(plot_flow[, ..to_distinct], fromLast = TRUE)]

min_score = 0#dtf_flow[, min(F1_score, na.rm = TRUE)]# min( dtf_flow$F1_score, na.rm = TRUE)
max_score = 1#max( dtf_flow$F1_score, na.rm = TRUE)

#min_detour =plot_flow[, min(nb_detour, na.rm = TRUE)]#min( plot_flow$nb_detour, na.rm = TRUE)
#max_detour = plot_flow[, max(nb_detour, na.rm = TRUE)]#max( plot_flow$nb_detour, na.rm = TRUE)

par(mfrow = c(4,2))
theta = 190 #180#220
phi = 320 #280
cex = 1

plot_flow[approach == "baseline", approach := "Baseline"]
plot_flow[approach == "unsupervised", approach := "Unsupervised"]
plot_flow[approach == "supervised", approach := "Supervised"]
plot_flow[, facet_label := paste(approach, model, sep = ": ")]
plot_flow[, facet_label := factor(facet_label, levels = c(
  "Baseline: THRESHOLD",
  "Supervised: SVM",
  "Unsupervised: DAE",
  "Baseline: INTERVAL_DELAY",
  "Supervised: REGLOG",
  "Unsupervised: VAE",
  "Supervised: XGBOOST"
))]
#plot_flow[nb_detour == "0_1_3_5_7_9", nb_detour := "1_2_4_6_8_10"]
#plot_flow[nb_detour %in% c("0","1","3","5","7","9"), nb_detour := as.numeric(nb_detour)+1]
plot_flow[,nb_detour := factor(nb_detour, 
                               levels = c(trainingdetour,"0","1","3","5","7","9"), #,"0_1_3_5_7","0_1_3_5","0_1_3","0_1"
                               labels = c(trainingdetourplus, "1","2","4","6","8","10"), ordered = T)] #,"1_2_4_6_8","1_2_4_6","1_2_4","1_2"
#graduation = c("1_2_4_6_8_10", "1","2","4","6","8","10")
# Create the faceted plot
ggplot(plot_flow, aes(x = nb_detour, y = F1_score, color= approach, shape = approach)) +
  # geom_point(size = 1,stroke = 2, show.legend = c(color = FALSE, shape = FALSE)) +
  # geom_errorbar(aes(
  #     ymin = F1_ci_lower,
  #     ymax = F1_ci_upper,
  #     color = "black"
  #   ),
  #   width = 0.5, # controls horizontal width of the bar
  #   alpha = 0.6, show.legend = c(color = FALSE, shape = FALSE),
  # 
  # ) +
  #geom_violin(aes(color = approach), show.legend = F)+
  geom_boxplot(outlier.color = "black", show.legend = F, notch = F
               , staplewidth = 0.7
               #, varwidth = T
               , aes(fill = approach)
               , color = "black"
               #,coef = 0
               ,width = 0.4
               # ,position = position_dodge2(preserve = "single"
               #                             , padding = 1)
               )+
    scale_color_manual(
      values = c(
        "Supervised" = "#f8766d",
        "Unsupervised" = "#619cff",
        "Baseline" = "#00ba38"
      )) +
  scale_fill_manual(
      values = c(
        "Supervised" = "#f8766d",
        "Unsupervised" = "#619cff",
        "Baseline" = "#00ba38"
      )) +
  scale_shape_manual(
      values = c(
        "Supervised" = 15,
        "Unsupervised" = 16,
        "Baseline" = 17
      )) +
    coord_cartesian(ylim = c(min_score, max_score)) +  # ← la bonne méthode
    labs(
      x = "Number of on-detour routers",
      y = TeX("$F_1$-Score")) +
    #scale_x_discrete(breaks = graduation, labels = graduation +1, limits = graduation)+
   # scale_x_discrete(# breaks = graduation
   #                  # ,labels = graduation
   #                  expand = c(0,0, 0,1) 
   #                   )+
  facet_wrap(~ facet_label, nrow = 3, ncol = 3)+
  # facet_wrap(~ interaction(approach, model), nrow = 2, ncol = 3,
  #          labeller = labeller(`interaction(approach, model)` = my_labels)
  #            )+
  # facet_grid( rows = vars(model),col = vars(approach)
  #             ,scales = "free", space = "free") + # or facet_wrap(~group)
  theme_minimal(base_size = 20)+
  theme(
    #plot.title = element_text(size = 30),
    #legend.title = element_text(size = 28),
    #legend.text = element_text(size = 25),
    #axis.title = element_text(size = 25),
    axis.text.x = element_text(angle = 40,  hjust = 1), #vjust = 0.5,
    axis.text.y = element_text(size = 15),
    panel.background = element_rect(fill = "transparent", color = NA),
  plot.background = element_rect(fill = "transparent", color = NA),
  panel.grid.major = element_line(color = "grey", linewidth = 0.1),
  panel.grid.minor = element_line(color = "grey", linewidth = 0.1)
    #,legend.key.size = unit(5, "lines")  # or "cm", "pt", etc.
  )
length(unique(plot_flow$seed))
```


### X several training with boxplot for several trainingdetour and several parasite rate
```{r}
# Réinitialiser les marges à leurs valeurs par défaut
library(patchwork)

x= "nb_detour"
y = "F1_score"
#z = "nb_detour"
colvar = "approach"
group = 9 #9,27,342
my_model = "ISOF"
p_att = 0.1
detour = 0
path = 0
para_rate ="120Mbps"
proto= "Udp"
models_dispo = unique(dtf_flow_boxplot$model)
models_dispo = models_dispo[! models_dispo %in% c("AE_CONTRACTIVE", "PCAthenAE_CONTRACTIVE",  "AE_SIMPLE",  "PCAthenAE_SIMPLE", "INTERVAL", "PCAthenINTERVAL", "OCSVM", "PCAthenOCSVM")] #, "AE_CLASS", "PCAthenAE_CLASS"
models_dispo = c( "THRESHOLD", "INTERVAL_DELAY",
  "SVM","REGLOG", # "CART","XGBOOST",
                  "DAE", "VAE") #"KMEANS", "ISOF",, "AE_SPARSE", "AE_LSTM", "AE_CONV1D"

names_no_pca <- models_dispo[!grepl("^PCAthen", models_dispo)]
names_pca <- models_dispo[grepl("^PCAthen", models_dispo)]
trainingdetour = "0_1_3_5_7_9"
trainingdetourplus = "1_2_4_6_8_10"
graduation <- c(trainingdetour, "0","1","3","5","7","9") # ,"2","4","6","8","10") #, #"0","1","3","5","7","9")#, "0_1_3_5_7","0_1_3_5","0_1_3","0_1",
plot_flow <- dtf_flow_boxplot[group_id == group & prop_att == p_att 
                      &  path_length == path 
                      & protocol == proto
                      #& parasite_rate == para_rate #& nb_detour <= 10
                      #
                      & model %in% models_dispo
                      & nb_detour %in% graduation
                     & trainondetour  %in% c(trainingdetour) #%in% c(trainingdetour) #==  nb_detour # #"0_1_3_5_7_9" #"5" # ,"0_1_3_5_7","0_1_3_5","0_1_3","0_1"
                     & do_evolution == T #F #F #T#F
                     & directory == "twelveth" #"tenth"
                     & comment == "basic"
                     #& dataset == "dtf_16"
                     ]
#plot_flow <- plot_flow[!duplicated(plot_flow[, ..to_distinct], fromLast = TRUE)]

min_score = 0#dtf_flow[, min(F1_score, na.rm = TRUE)]# min( dtf_flow$F1_score, na.rm = TRUE)
max_score = 1#max( dtf_flow$F1_score, na.rm = TRUE)

#min_detour =plot_flow[, min(nb_detour, na.rm = TRUE)]#min( plot_flow$nb_detour, na.rm = TRUE)
#max_detour = plot_flow[, max(nb_detour, na.rm = TRUE)]#max( plot_flow$nb_detour, na.rm = TRUE)

par(mfrow = c(4,2))
theta = 190 #180#220
phi = 320 #280
cex = 1

plot_flow[approach == "baseline", approach := "Baseline"]
plot_flow[approach == "unsupervised", approach := "Unsupervised"]
plot_flow[approach == "supervised", approach := "Supervised"]
plot_flow[, facet_label := paste(approach, model, sep = ": ")]
plot_flow[, facet_label := factor(facet_label, levels = c(
  "Baseline: THRESHOLD",
  "Supervised: SVM",
  "Unsupervised: DAE",
  "Baseline: INTERVAL_DELAY",
  "Supervised: REGLOG",
  "Unsupervised: VAE",
  "Supervised: XGBOOST"
))]
#plot_flow[nb_detour == "0_1_3_5_7_9", nb_detour := "1_2_4_6_8_10"]
#plot_flow[nb_detour %in% c("0","1","3","5","7","9"), nb_detour := as.numeric(nb_detour)+1]
plot_flow[,nb_detour := factor(nb_detour, 
                               levels = c(trainingdetour,"0","1","3","5","7","9"), #,"0_1_3_5_7","0_1_3_5","0_1_3","0_1"
                               labels = c(trainingdetourplus, "1","2","4","6","8","10"), ordered = T)] #,"1_2_4_6_8","1_2_4_6","1_2_4","1_2"
#graduation = c("1_2_4_6_8_10", "1","2","4","6","8","10")
# Create the faceted plot
ggplot(plot_flow, aes(x = nb_detour, y = F1_score, color= approach, shape = approach)) +
  # geom_point(size = 1,stroke = 2, show.legend = c(color = FALSE, shape = FALSE)) +
  # geom_errorbar(aes(
  #     ymin = F1_ci_lower,
  #     ymax = F1_ci_upper,
  #     color = "black"
  #   ),
  #   width = 0.5, # controls horizontal width of the bar
  #   alpha = 0.6, show.legend = c(color = FALSE, shape = FALSE),
  # 
  # ) +
  #geom_violin(aes(color = approach), show.legend = F)+
  geom_boxplot(outlier.color = "black", show.legend = F, notch = F
               , staplewidth = 0.7
               #, varwidth = T
               , aes(fill = approach)
               , color = "black"
               #,coef = 0
               ,width = 0.4
               # ,position = position_dodge2(preserve = "single"
               #                             , padding = 1)
               )+
    scale_color_manual(
      values = c(
        "Supervised" = "#f8766d",
        "Unsupervised" = "#619cff",
        "Baseline" = "#00ba38"
      )) +
  scale_fill_manual(
      values = c(
        "Supervised" = "#f8766d",
        "Unsupervised" = "#619cff",
        "Baseline" = "#00ba38"
      )) +
  scale_shape_manual(
      values = c(
        "Supervised" = 15,
        "Unsupervised" = 16,
        "Baseline" = 17
      )) +
    coord_cartesian(ylim = c(min_score, max_score)) +  # ← la bonne méthode
    labs(
      x = "Number of on-detour routers",
      y = TeX("$F_1$-Score")) +
    #scale_x_discrete(breaks = graduation, labels = graduation +1, limits = graduation)+
   # scale_x_discrete(# breaks = graduation
   #                  # ,labels = graduation
   #                  expand = c(0,0, 0,1) 
   #                   )+
  facet_wrap(~ facet_label, nrow = 3, ncol = 3)+
  # facet_wrap(~ interaction(approach, model), nrow = 2, ncol = 3,
  #          labeller = labeller(`interaction(approach, model)` = my_labels)
  #            )+
  # facet_grid( rows = vars(model),col = vars(approach)
  #             ,scales = "free", space = "free") + # or facet_wrap(~group)
  theme_minimal(base_size = 20)+
  theme(
    #plot.title = element_text(size = 30),
    #legend.title = element_text(size = 28),
    #legend.text = element_text(size = 25),
    #axis.title = element_text(size = 25),
    axis.text.x = element_text(angle = 40,  hjust = 1), #vjust = 0.5,
    axis.text.y = element_text(size = 15),
    panel.background = element_rect(fill = "transparent", color = NA),
  plot.background = element_rect(fill = "transparent", color = NA),
  panel.grid.major = element_line(color = "grey", linewidth = 0.1),
  panel.grid.minor = element_line(color = "grey", linewidth = 0.1)
    #,legend.key.size = unit(5, "lines")  # or "cm", "pt", etc.
  )
length(unique(plot_flow$seed))
```




# specific for poster
## parasite
```{r}
# Réinitialiser les marges à leurs valeurs par défaut
library(patchwork)

x= "parasite_rate"
y = "F1_score"
#z = "nb_detour"
colvar = "approach"
group = 9
my_model = "ISOF"
p_att = 0.1
detour = 0
path = 0
proto= "Udp"
models_dispo = unique(dtf_flow$model)
models_dispo = c("XGBOOST", "DAE") #models_dispo[ models_dispo %in% c("XGBOOST", "DAE")]
names_no_pca <- models_dispo[!grepl("^PCAthen", models_dispo)]

plot_flow <- dtf_flow[group_id == group & prop_att == p_att & path_length == path &  nb_detour == detour & protocol == proto& !is.na(parasite_rate)]
min_score = 0#dtf_flow[, min(F1_score, na.rm = TRUE)]# min( dtf_flow$F1_score, na.rm = TRUE)
max_score = 1#max( dtf_flow$F1_score, na.rm = TRUE)

min_detour =plot_flow[, min(nb_detour, na.rm = TRUE)]#min( plot_flow$nb_detour, na.rm = TRUE)
max_detour = plot_flow[, max(nb_detour, na.rm = TRUE)]#max( plot_flow$nb_detour, na.rm = TRUE)

par(mfrow = c(4,2))
theta = 190 #180#220
phi = 320 #280
cex = 1
my_model = models_dispo[1]
plots_no_pca <- list()
for (my_model in models_dispo){
  name = my_model
  par(mar = c(0.5, 0,2.5, 0))
  
  #par(mar = c(4.1, 3.1, 3.1, 1.1))
  plot_flow_model <- plot_flow[model == my_model]
  #unique (plot_flow_model$parasite_rate)
  p <- ggplot(plot_flow_model, aes(x = parasite_rate, y = F1_score, color= approach)) +
    geom_point(shape=4, size = 4, stroke = 4) +  #, color = "#619cff"
    scale_color_manual(
      values = c(
        "supervised" = "#f8766d",
        "unsupervised" = "#619cff"
      )) +
    coord_cartesian(ylim = c(min_score, max_score)) +  # ← la bonne méthode
    labs(
      #title = paste0(name), #,": F1_score; \nsize_group=", group, " \nprop_att=", p_att, "; nb_path=", path, "; \nnb_detour=", detour),
      x = "Parasite Rate (Mbps)", 
      y = TeX("$F_1$-Score")) +  
    theme_minimal(base_size = 25)+ 
    theme(axis.text.x = element_text( angle = 90, hjust = 1, vjust = 0.5),
    plot.title = element_text(size = 30),
    legend.title = element_text(size = 28),
    legend.text = element_text(size = 25),
    axis.title = element_text(size = 25)
    #,legend.key.size = unit(5, "lines")  # or "cm", "pt", etc.
  )+ guides(
  color = "none" 
)
  
    plots_no_pca[[my_model]] <- p
  
  
  #print(p)
}
wrap_plots(plots_no_pca)

```

## path
```{r}
# Réinitialiser les marges à leurs valeurs par défaut
library(patchwork)

x= "path_length"
y = "F1_score"
#z = "nb_detour"
colvar = "approach"
group = 9
my_model = "ISOF"
p_att = 0.1
detour = 0
path = 0
para_rate ="120Mbps"
proto= "Udp"
models_dispo = unique(dtf_flow$model)
models_dispo = c("XGBOOST", "DAE") #models_dispo[ models_dispo %in% c("XGBOOST", "DAE")]

names_no_pca <- models_dispo[!grepl("^PCAthen", models_dispo)]

plot_flow <- dtf_flow[group_id == group & prop_att == p_att 
                      &  nb_detour == detour & protocol == proto
                      & parasite_rate == para_rate]
min_score = 0#dtf_flow[, min(F1_score, na.rm = TRUE)]# min( dtf_flow$F1_score, na.rm = TRUE)
max_score = 1#max( dtf_flow$F1_score, na.rm = TRUE)

min_detour =plot_flow[, min(nb_detour, na.rm = TRUE)]#min( plot_flow$nb_detour, na.rm = TRUE)
max_detour = plot_flow[, max(nb_detour, na.rm = TRUE)]#max( plot_flow$nb_detour, na.rm = TRUE)

par(mfrow = c(4,2))
theta = 190 #180#220
phi = 320 #280
cex = 1
my_model = models_dispo[3]
plots_no_pca <- list()
for (my_model in models_dispo){
  name = my_model
  par(mar = c(0.5, 0,2.5, 0))
  
  #par(mar = c(4.1, 3.1, 3.1, 1.1))
  plot_flow_model <- plot_flow[model == my_model]
  #unique (plot_flow_model$parasite_rate)
  p <- ggplot(plot_flow_model, aes(x = path_length, y = F1_score, color= approach)) +
    geom_point(shape=4, size = 4, stroke = 4) +  
    scale_color_manual(
      values = c(
        "supervised" = "#f8766d",
        "unsupervised" = "#619cff"
      )) +
    coord_cartesian(ylim = c(min_score, max_score)) +  # ← la bonne méthode
    labs(
      #title = paste0(name,": F1_score; \nsize_group=", group, " \nprop_att=", p_att, "; parasite_rate=", para_rate, "; \nnb_detour=", detour),
      x = "Number of additional on-path routers", #Path Length (Number of routers)", 
      y = TeX("$F_1$-Score")) +  
    theme_minimal(base_size = 25)+ 
    theme(axis.text.x = element_text( angle = 90, hjust = 1, vjust = 0.5),
    plot.title = element_text(size = 30),
    legend.title = element_text(size = 28),
    legend.text = element_text(size = 25),
    axis.title = element_text(size = 25)
    #,legend.key.size = unit(5, "lines")  # or "cm", "pt", etc.
  )+ guides(
  color = "none" 
)
    plots_no_pca[[my_model]] <- p
  
  
  #print(p)
}
wrap_plots(plots_no_pca)

```

## detour
```{r}
# Réinitialiser les marges à leurs valeurs par défaut
library(patchwork)

x= "nb_detour"
y = "F1_score"
#z = "nb_detour"
colvar = "approach"
group = 9
my_model = "ISOF"
p_att = 0.1
detour = 0
path = 0
para_rate ="120Mbps"
proto= "Udp"
models_dispo = unique(dtf_flow$model)
models_dispo = c("XGBOOST", "DAE") #models_dispo[models_dispo %in% c("XGBOOST", "DAE")]

names_no_pca <- models_dispo[!grepl("^PCAthen", models_dispo)]

plot_flow <- dtf_flow[group_id == group & prop_att == p_att 
                      &  path_length == path & protocol == proto
                      & parasite_rate == para_rate & nb_detour <= 8]
min_score = 0#dtf_flow[, min(F1_score, na.rm = TRUE)]# min( dtf_flow$F1_score, na.rm = TRUE)
max_score = 1#max( dtf_flow$F1_score, na.rm = TRUE)

min_detour =plot_flow[, min(nb_detour, na.rm = TRUE)]#min( plot_flow$nb_detour, na.rm = TRUE)
max_detour = plot_flow[, max(nb_detour, na.rm = TRUE)]#max( plot_flow$nb_detour, na.rm = TRUE)

par(mfrow = c(4,2))
theta = 190 #180#220
phi = 320 #280
cex = 1
my_model = models_dispo[3]
plots_no_pca <- list()
for (my_model in models_dispo){
  name = my_model
  par(mar = c(0.5, 0,2.5, 0))
  
  #par(mar = c(4.1, 3.1, 3.1, 1.1))
  plot_flow_model <- plot_flow[model == my_model]
  #unique (plot_flow_model$parasite_rate)
  p <- ggplot(plot_flow_model, aes(x = nb_detour, y = F1_score, color= approach)) + #
    geom_point(shape=4, size = 4,stroke = 4) +  
    scale_color_manual(
      values = c(
        "supervised" = "#f8766d",
        "unsupervised" = "#619cff"
      )) +
    coord_cartesian(ylim = c(min_score, max_score)) +  # ← la bonne méthode
    labs(
      title = paste0(name),#,": F1_score; \nsize_group=", group, " \nprop_att=", p_att, "; \nparasite_rate=", para_rate, "; \npath_length=", path),
      x = "Number of additional detour", 
      y = TeX("$F_1$-Score")) +  
    theme_minimal(base_size = 25)+ 
    theme(axis.text.x = element_text( angle = 90, hjust = 1, vjust = 0.5),
    plot.title = element_text(size = 30),
    legend.title = element_text(size = 28),
    legend.text = element_text(size = 25),
    axis.title = element_text(size = 25)
    #,legend.key.size = unit(5, "lines")  # or "cm", "pt", etc.
  )+guides(
  color = "none" 
) 
  
    plots_no_pca[[my_model]] <- p
  
  
  #print(p)
}
wrap_plots(plots_no_pca)

```

# instruction C: ablation de t_stat et t_end
```{r}
p_att = 0.1
proto= "Udp"
models_dispo = c( "THRESHOLD", "INTERVAL_DELAY", "SVM",  "REGLOG",  "DAE", "VAE")
group = 9
dtf_C <- dtf_flow_boxplot[temporal_cov == FALSE
                          & cross_seed == FALSE
                          & feature_set == "full"]
```

## parasite rate
```{r}
detour = "0" #0_1_3_5_7_9"
path = 0

plot_flow <- dtf_C[group_id == group 
                      & prop_att == p_att 
                      & path_length == path
                      &  nb_detour == detour 
                      & protocol == proto 
                      & !is.na(parasite_rate)
                      & model %in% models_dispo
                      & do_evolution == F
                      & directory == "eleventh" #"ninth"
                      & comment == "basic"
                      #& ( dataset == "dtf_16")
                      ]
min_score = 0
max_score = 1

par(mfrow = c(4,2))
theta = 190 #180#220
phi = 320 #280
cex = 1

plot_flow[approach == "baseline", approach := "Baseline"]
plot_flow[approach == "unsupervised", approach := "Unsupervised"]
plot_flow[approach == "supervised", approach := "Supervised"]
plot_flow[, facet_label := paste(approach, model, sep = ": ")]
plot_flow[, facet_label := factor(facet_label, levels = c(
  "Baseline: THRESHOLD",
  "Supervised: SVM",
  "Unsupervised: DAE",
  "Baseline: INTERVAL_DELAY",
  "Supervised: REGLOG",
  "Unsupervised: VAE"
,"Supervised: XGBOOST"
))]
# Create the faceted plot
ggplot(plot_flow, aes(x = parasite_rate, y = F1_score, color= approach, shape = approach)) +
  geom_boxplot(outlier.color = "black", show.legend = F, notch = F
               , staplewidth = 0.7, varwidth = T, aes(fill = approach), color = "black"
               #,coef = 0
               #,width = 0.4
               )+
  
    scale_color_manual(
      values = c(
        "Supervised" = "#f8766d",
        "Unsupervised" = "#619cff",
        "Baseline" = "#00ba38"
      )) +
  scale_fill_manual(
      values = c(
        "Supervised" = "#f8766d",
        "Unsupervised" = "#619cff",
        "Baseline" = "#00ba38"
      )) +
  scale_shape_manual(
      values = c(
        "Supervised" = 15,
        "Unsupervised" = 16,
        "Baseline" = 17
      )) +
    coord_cartesian(ylim = c(min_score, max_score)) +  # ← la bonne méthode
    labs(
      x = "Parasite Rate (Mbps)",
      y = TeX("$F_1$-Score")
      ) +
  facet_wrap(~ facet_label, nrow = 3, ncol = 3)+
  theme_minimal(base_size = 20)+
  theme(
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, size = 15),
    axis.text.y = element_text(size = 15),
    panel.background = element_rect(fill = "transparent", color = NA),
  plot.background = element_rect(fill = "transparent", color = NA),
  panel.grid.major = element_line(color = "grey", linewidth = 0.1),
  panel.grid.minor = element_line(color = "grey", linewidth = 0.1)
  )
length(unique(plot_flow$seed))
```

## path length
```{r}
detour = "0" #0_1_3_5_7_9"
path = 0
para_rate ="120Mbps"

graduation = c(0,2,4,6,8,10) #,1,3,5,7,9 )#, )
plot_flow <- dtf_C[group_id == group & prop_att == p_att 
                      &  nb_detour == detour & protocol == proto
                      & parasite_rate == para_rate
                      & model %in% models_dispo
                      & path_length %in% graduation
                      &do_evolution == F
                      & directory == "eleventh" 
                      & (comment == "basic" | comment == "basic2")
                      #& dataset == "dtf_16"
                      ]
plot_flow$nb_detour = as.numeric(plot_flow$nb_detour)
plot_flow$path_length = as.factor(plot_flow$path_length)

min_score = 0
max_score = 1

min_detour =plot_flow[, min(nb_detour, na.rm = TRUE)]
max_detour = plot_flow[, max(nb_detour, na.rm = TRUE)]

par(mfrow = c(4,2))
theta = 190
phi = 320 
cex = 1

plot_flow[approach == "baseline", approach := "Baseline"]
plot_flow[approach == "unsupervised", approach := "Unsupervised"]
plot_flow[approach == "supervised", approach := "Supervised"]
plot_flow[, facet_label := paste(approach, model, sep = ": ")]
plot_flow[, facet_label := factor(facet_label, levels = c(
  "Baseline: THRESHOLD",
  "Supervised: SVM",
  "Unsupervised: DAE",
  "Baseline: INTERVAL_DELAY",
  "Supervised: REGLOG",
  "Unsupervised: VAE",
  "Supervised: XGBOOST"
))]
# Create the faceted plot
ggplot(plot_flow, aes(x = path_length, y = F1_score, color= approach, shape = approach)) +
  geom_boxplot(outlier.color = "black", show.legend = F, notch = F
               , staplewidth = 0.7, varwidth = T
               , aes(fill = approach)
               , color = "black"
               #,coef = 0
               ,width = 0.4
               )+
    scale_color_manual(
      values = c(
        "Supervised" = "#f8766d",
        "Unsupervised" = "#619cff",
        "Baseline" = "#00ba38"
      )) +
  scale_fill_manual(
      values = c(
        "Supervised" = "#f8766d",
        "Unsupervised" = "#619cff",
        "Baseline" = "#00ba38"
      )) +
  scale_shape_manual(
      values = c(
        "Supervised" = 15,
        "Unsupervised" = 16,
        "Baseline" = 17
      )) +
    coord_cartesian(ylim = c(min_score, max_score)) +  # ← la bonne méthode
    labs(
      x = "Number of on-path routers",
      y = TeX("$F_1$-Score")) +
    scale_x_discrete(#breaks = graduation, 
                     labels = graduation + 4
                     #, limits = graduation
                     )+
  facet_wrap(~ facet_label, nrow = 3, ncol = 3)+
  theme_minimal(base_size = 20)+
  theme(
    axis.text.y = element_text(size = 15),
    panel.background = element_rect(fill = "transparent", color = NA),
  plot.background = element_rect(fill = "transparent", color = NA),
  panel.grid.major = element_line(color = "grey", linewidth = 0.1),
  panel.grid.minor = element_line(color = "grey", linewidth = 0.1)
  )
length(unique(plot_flow$seed))
```

## detour length



```{r}
detour = 0
path = 0
para_rate ="120Mbps"

graduation <- c("0","1","3","5","7","9") #, 2,4,6,8,10)
plot_flow <- dtf_C[group_id == group & prop_att == p_att 
                      &  path_length == path & protocol == proto
                      & parasite_rate == para_rate #& nb_detour <= 10
                      & model %in% models_dispo
                      & nb_detour ==detour
                      &nb_detour == trainondetour
                      & do_evolution == F
                      & comment == "basic"
                      & directory == "eleventh" #"ninth"
                      #& dataset == "dtf_16"
                      ]
plot_flow <- plot_flow[nb_detour %in% graduation]
plot_flow$nb_detour = as.factor(plot_flow$nb_detour)
graduation = as.numeric(graduation)

min_score = 0
max_score = 1

par(mfrow = c(4,2))
theta = 190 #180#220
phi = 320 #280
cex = 1

plot_flow[approach == "baseline", approach := "Baseline"]
plot_flow[approach == "unsupervised", approach := "Unsupervised"]
plot_flow[approach == "supervised", approach := "Supervised"]
plot_flow[, facet_label := paste(approach, model, sep = ": ")]
plot_flow[, facet_label := factor(facet_label, levels = c(
  "Baseline: THRESHOLD",
  "Supervised: SVM",
  "Unsupervised: DAE",
  "Baseline: INTERVAL_DELAY",
  "Supervised: REGLOG",
  "Unsupervised: VAE"
))]
# Create the faceted plot
ggplot(plot_flow, aes(x = nb_detour, y = F1_score, color= approach, shape = approach)) +
  geom_boxplot(outlier.color = "black", show.legend = F, notch = F
               , staplewidth = 0.7, varwidth = T
               , aes(fill = approach)
               , color = "black"
               #,coef = 0
               ,width = 0.4
               )+
    scale_color_manual(
      values = c(
        "Supervised" = "#f8766d",
        "Unsupervised" = "#619cff",
        "Baseline" = "#00ba38"
      )) +
  scale_fill_manual(
      values = c(
        "Supervised" = "#f8766d",
        "Unsupervised" = "#619cff",
        "Baseline" = "#00ba38"
      )) +
  scale_shape_manual(
      values = c(
        "Supervised" = 15,
        "Unsupervised" = 16,
        "Baseline" = 17
      )) +
    coord_cartesian(ylim = c(min_score, max_score)) +  # ← la bonne méthode
    labs(
      x = "Number of on-detour routers",
      y = TeX("$F_1$-Score")) +
    scale_x_discrete(#breaks = graduation, 
                     labels = as.numeric(graduation) +1
                    # , limits = graduation
                    )+
  facet_wrap(~ facet_label, nrow = 2, ncol = 3)+
  theme_minimal(base_size = 20)+
  theme(
    axis.text.y = element_text(size = 15),
    panel.background = element_rect(fill = "transparent", color = NA),
  plot.background = element_rect(fill = "transparent", color = NA),
  panel.grid.major = element_line(color = "grey", linewidth = 0.1),
  panel.grid.minor = element_line(color = "grey", linewidth = 0.1)
  )
length(unique(plot_flow$seed))
```




# instruction D: cross seed

```{r}
p_att = 0.1
proto= "Udp"
models_dispo = c( "THRESHOLD", "INTERVAL_DELAY", "SVM",  "REGLOG",  "DAE", "VAE")
group = 9
dtf_D <- dtf_flow_boxplot[cross_seed == T
                          #& temporal_cov == T
                          & feature_set == "full"]
```


## parasite rate
```{r}
detour = "0" #0_1_3_5_7_9"
path = 0

plot_flow <- dtf_D[group_id == group 
                      & prop_att == p_att 
                      & path_length == path
                      &  nb_detour == detour 
                      & protocol == proto 
                      & !is.na(parasite_rate)
                      & model %in% models_dispo
                      & do_evolution == F
                      & directory == "eleventh" #"ninth"
                      & comment == "basic"
                      #& ( dataset == "dtf_16")
                      ]
min_score = 0
max_score = 1

par(mfrow = c(4,2))
theta = 190 #180#220
phi = 320 #280
cex = 1

plot_flow[approach == "baseline", approach := "Baseline"]
plot_flow[approach == "unsupervised", approach := "Unsupervised"]
plot_flow[approach == "supervised", approach := "Supervised"]
plot_flow[, facet_label := paste(approach, model, sep = ": ")]
plot_flow[, facet_label := factor(facet_label, levels = c(
  "Baseline: THRESHOLD",
  "Supervised: SVM",
  "Unsupervised: DAE",
  "Baseline: INTERVAL_DELAY",
  "Supervised: REGLOG",
  "Unsupervised: VAE"
,"Supervised: XGBOOST"
))]
# Create the faceted plot
ggplot(plot_flow, aes(x = parasite_rate, y = F1_score, color= approach, shape = approach)) +
  geom_boxplot(outlier.color = "black", show.legend = F, notch = F
               , staplewidth = 0.7, varwidth = T, aes(fill = approach), color = "black"
               #,coef = 0
               #,width = 0.4
               )+
  
    scale_color_manual(
      values = c(
        "Supervised" = "#f8766d",
        "Unsupervised" = "#619cff",
        "Baseline" = "#00ba38"
      )) +
  scale_fill_manual(
      values = c(
        "Supervised" = "#f8766d",
        "Unsupervised" = "#619cff",
        "Baseline" = "#00ba38"
      )) +
  scale_shape_manual(
      values = c(
        "Supervised" = 15,
        "Unsupervised" = 16,
        "Baseline" = 17
      )) +
    coord_cartesian(ylim = c(min_score, max_score)) +  # ← la bonne méthode
    labs(
      x = "Parasite Rate (Mbps)",
      y = TeX("$F_1$-Score")
      ) +
  facet_wrap(~ facet_label, nrow = 3, ncol = 3)+
  theme_minimal(base_size = 20)+
  theme(
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, size = 15),
    axis.text.y = element_text(size = 15),
    panel.background = element_rect(fill = "transparent", color = NA),
  plot.background = element_rect(fill = "transparent", color = NA),
  panel.grid.major = element_line(color = "grey", linewidth = 0.1),
  panel.grid.minor = element_line(color = "grey", linewidth = 0.1)
  )
length(unique(plot_flow$seed))
```

## path length
```{r}
detour = "0" #0_1_3_5_7_9"
path = 0
para_rate ="120Mbps"

graduation = c(0,2,4,6,8,10) #,1,3,5,7,9 )#, )
plot_flow <- dtf_D[group_id == group & prop_att == p_att 
                      &  nb_detour == detour & protocol == proto
                      & parasite_rate == para_rate
                      & model %in% models_dispo
                      & path_length %in% graduation
                      &do_evolution == F
                      & directory == "eleventh" 
                      & (comment == "basic" | comment == "basic2")
                      #& dataset == "dtf_16"
                      ]
plot_flow$nb_detour = as.numeric(plot_flow$nb_detour)
plot_flow$path_length = as.factor(plot_flow$path_length)

min_score = 0
max_score = 1

min_detour =plot_flow[, min(nb_detour, na.rm = TRUE)]
max_detour = plot_flow[, max(nb_detour, na.rm = TRUE)]

par(mfrow = c(4,2))
theta = 190
phi = 320 
cex = 1

plot_flow[approach == "baseline", approach := "Baseline"]
plot_flow[approach == "unsupervised", approach := "Unsupervised"]
plot_flow[approach == "supervised", approach := "Supervised"]
plot_flow[, facet_label := paste(approach, model, sep = ": ")]
plot_flow[, facet_label := factor(facet_label, levels = c(
  "Baseline: THRESHOLD",
  "Supervised: SVM",
  "Unsupervised: DAE",
  "Baseline: INTERVAL_DELAY",
  "Supervised: REGLOG",
  "Unsupervised: VAE",
  "Supervised: XGBOOST"
))]
# Create the faceted plot
ggplot(plot_flow, aes(x = path_length, y = F1_score, color= approach, shape = approach)) +
  geom_boxplot(outlier.color = "black", show.legend = F, notch = F
               , staplewidth = 0.7, varwidth = T
               , aes(fill = approach)
               , color = "black"
               #,coef = 0
               ,width = 0.4
               )+
    scale_color_manual(
      values = c(
        "Supervised" = "#f8766d",
        "Unsupervised" = "#619cff",
        "Baseline" = "#00ba38"
      )) +
  scale_fill_manual(
      values = c(
        "Supervised" = "#f8766d",
        "Unsupervised" = "#619cff",
        "Baseline" = "#00ba38"
      )) +
  scale_shape_manual(
      values = c(
        "Supervised" = 15,
        "Unsupervised" = 16,
        "Baseline" = 17
      )) +
    coord_cartesian(ylim = c(min_score, max_score)) +  # ← la bonne méthode
    labs(
      x = "Number of on-path routers",
      y = TeX("$F_1$-Score")) +
    scale_x_discrete(#breaks = graduation, 
                     labels = graduation + 4
                     #, limits = graduation
                     )+
  facet_wrap(~ facet_label, nrow = 3, ncol = 3)+
  theme_minimal(base_size = 20)+
  theme(
    axis.text.y = element_text(size = 15),
    panel.background = element_rect(fill = "transparent", color = NA),
  plot.background = element_rect(fill = "transparent", color = NA),
  panel.grid.major = element_line(color = "grey", linewidth = 0.1),
  panel.grid.minor = element_line(color = "grey", linewidth = 0.1)
  )
length(unique(plot_flow$seed))
```

## detour length

### eleventh

#### basic scenario
```{r}
detour = 0
path = 0
para_rate ="120Mbps"

graduation <- c("0","1","3","5","7","9") #, 2,4,6,8,10)
plot_flow <- dtf_D[group_id == group & prop_att == p_att 
                      &  path_length == path & protocol == proto
                      & parasite_rate == para_rate #& nb_detour <= 10
                      & model %in% models_dispo
                      & nb_detour == trainondetour
                      & do_evolution == F
                      & comment == "basic"
                      & directory == "eleventh" #"ninth"
                      #& dataset == "dtf_16"
                      ]
plot_flow <- plot_flow[nb_detour %in% graduation]
plot_flow$nb_detour = as.factor(plot_flow$nb_detour)
graduation = as.numeric(graduation)

min_score = 0
max_score = 1

par(mfrow = c(4,2))
theta = 190 #180#220
phi = 320 #280
cex = 1

plot_flow[approach == "baseline", approach := "Baseline"]
plot_flow[approach == "unsupervised", approach := "Unsupervised"]
plot_flow[approach == "supervised", approach := "Supervised"]
plot_flow[, facet_label := paste(approach, model, sep = ": ")]
plot_flow[, facet_label := factor(facet_label, levels = c(
  "Baseline: THRESHOLD",
  "Supervised: SVM",
  "Unsupervised: DAE",
  "Baseline: INTERVAL_DELAY",
  "Supervised: REGLOG",
  "Unsupervised: VAE"
))]
# Create the faceted plot
ggplot(plot_flow, aes(x = nb_detour, y = F1_score, color= approach, shape = approach)) +
  geom_boxplot(outlier.color = "black", show.legend = F, notch = F
               , staplewidth = 0.7, varwidth = T
               , aes(fill = approach)
               , color = "black"
               #,coef = 0
               ,width = 0.4
               )+
    scale_color_manual(
      values = c(
        "Supervised" = "#f8766d",
        "Unsupervised" = "#619cff",
        "Baseline" = "#00ba38"
      )) +
  scale_fill_manual(
      values = c(
        "Supervised" = "#f8766d",
        "Unsupervised" = "#619cff",
        "Baseline" = "#00ba38"
      )) +
  scale_shape_manual(
      values = c(
        "Supervised" = 15,
        "Unsupervised" = 16,
        "Baseline" = 17
      )) +
    coord_cartesian(ylim = c(min_score, max_score)) +  # ← la bonne méthode
    labs(
      x = "Number of on-detour routers",
      y = TeX("$F_1$-Score")) +
    scale_x_discrete(#breaks = graduation, 
                     labels = as.numeric(graduation) +1
                    # , limits = graduation
                    )+
  facet_wrap(~ facet_label, nrow = 2, ncol = 3)+
  theme_minimal(base_size = 20)+
  theme(
    axis.text.y = element_text(size = 15),
    panel.background = element_rect(fill = "transparent", color = NA),
  plot.background = element_rect(fill = "transparent", color = NA),
  panel.grid.major = element_line(color = "grey", linewidth = 0.1),
  panel.grid.minor = element_line(color = "grey", linewidth = 0.1)
  )
length(unique(plot_flow$seed))
```

#### X several training with boxplot for several trainingdetour
```{r}

detour = 0
path = 0
para_rate ="120Mbps"

trainingdetour = "0_1_3_5_7_9"
trainingdetourplus = "1_2_4_6_8_10"
graduation <- c(trainingdetour, "0","1","3","5","7","9") # ,"2","4","6","8","10") #, #"0","1","3","5","7","9")#, "0_1_3_5_7","0_1_3_5","0_1_3","0_1",
plot_flow <- dtf_D[group_id == group & prop_att == p_att 
                      &  path_length == path & protocol == proto
                      & parasite_rate == para_rate 
                      & model %in% models_dispo
                      & nb_detour %in% graduation
                     & trainondetour  %in% c(trainingdetour) 
                     & do_evolution == T 
                     & (comment == "basic")
                      & directory == "eleventh" 
                      #& dataset == "dtf_16"
                     ]
min_score = 0
max_score = 1

par(mfrow = c(4,2))
theta = 190 #180#220
phi = 320 #280
cex = 1

plot_flow[approach == "baseline", approach := "Baseline"]
plot_flow[approach == "unsupervised", approach := "Unsupervised"]
plot_flow[approach == "supervised", approach := "Supervised"]
plot_flow[, facet_label := paste(approach, model, sep = ": ")]
plot_flow[, facet_label := factor(facet_label, levels = c(
  "Baseline: THRESHOLD",
  "Supervised: SVM",
  "Unsupervised: DAE",
  "Baseline: INTERVAL_DELAY",
  "Supervised: REGLOG",
  "Unsupervised: VAE",
  "Supervised: XGBOOST"
))]
plot_flow[,nb_detour := factor(nb_detour, 
                               levels = c(trainingdetour,"0","1","3","5","7","9"),
                               labels = c(trainingdetourplus, "1","2","4","6","8","10"), ordered = T)]
# Create the faceted plot
ggplot(plot_flow, aes(x = nb_detour, y = F1_score, color= approach, shape = approach)) +
  geom_boxplot(outlier.color = "black", show.legend = F, notch = F
               , staplewidth = 0.7
               , aes(fill = approach)
               , color = "black"
               ,width = 0.4
               )+
    scale_color_manual(
      values = c(
        "Supervised" = "#f8766d",
        "Unsupervised" = "#619cff",
        "Baseline" = "#00ba38"
      )) +
  scale_fill_manual(
      values = c(
        "Supervised" = "#f8766d",
        "Unsupervised" = "#619cff",
        "Baseline" = "#00ba38"
      )) +
  scale_shape_manual(
      values = c(
        "Supervised" = 15,
        "Unsupervised" = 16,
        "Baseline" = 17
      )) +
    coord_cartesian(ylim = c(min_score, max_score)) +  # ← la bonne méthode
    labs(
      x = "Number of on-detour routers",
      y = TeX("$F_1$-Score")) +
  facet_wrap(~ facet_label, nrow = 3, ncol = 3)+
  theme_minimal(base_size = 20)+
  theme(
    axis.text.x = element_text(angle = 40,  hjust = 1), #vjust = 0.5,
    axis.text.y = element_text(size = 15),
    panel.background = element_rect(fill = "transparent", color = NA),
  plot.background = element_rect(fill = "transparent", color = NA),
  panel.grid.major = element_line(color = "grey", linewidth = 0.1),
  panel.grid.minor = element_line(color = "grey", linewidth = 0.1)
  )
length(unique(plot_flow$seed))
```



### twelveth

```{r}
detour = 0
path = 0
para_rate ="120Mbps"

names_no_pca <- models_dispo[!grepl("^PCAthen", models_dispo)]
names_pca <- models_dispo[grepl("^PCAthen", models_dispo)]
trainingdetour = "0_1_3_5_7_9"
trainingdetourplus = "1_2_4_6_8_10"
graduation <- c(trainingdetour, "0","1","3","5","7","9") 
plot_flow <- dtf_D[group_id == group & prop_att == p_att 
                      &  path_length == path 
                      & protocol == proto
                      #& parasite_rate == para_rate #& nb_detour <= 10
                      #
                      & model %in% models_dispo
                      & nb_detour %in% graduation
                     & trainondetour  %in% c(trainingdetour) 
                     & do_evolution == T #F #F #T#F
                     & directory == "twelveth" #"tenth"
                     & comment == "basic"
                     #& dataset == "dtf_16"
                     ]
min_score = 0
max_score = 1

par(mfrow = c(4,2))
theta = 190 #180#220
phi = 320 #280
cex = 1

plot_flow[approach == "baseline", approach := "Baseline"]
plot_flow[approach == "unsupervised", approach := "Unsupervised"]
plot_flow[approach == "supervised", approach := "Supervised"]
plot_flow[, facet_label := paste(approach, model, sep = ": ")]
plot_flow[, facet_label := factor(facet_label, levels = c(
  "Baseline: THRESHOLD",
  "Supervised: SVM",
  "Unsupervised: DAE",
  "Baseline: INTERVAL_DELAY",
  "Supervised: REGLOG",
  "Unsupervised: VAE",
  "Supervised: XGBOOST"
))]
plot_flow[,nb_detour := factor(nb_detour, 
                               levels = c(trainingdetour,"0","1","3","5","7","9"), 
                               labels = c(trainingdetourplus, "1","2","4","6","8","10"), ordered = T)] 
# Create the faceted plot
ggplot(plot_flow, aes(x = nb_detour, y = F1_score, color= approach, shape = approach)) +
  geom_boxplot(outlier.color = "black", show.legend = F, notch = F
               , staplewidth = 0.7
               #, varwidth = T
               , aes(fill = approach)
               , color = "black"
               #,coef = 0
               ,width = 0.4
               # ,position = position_dodge2(preserve = "single"
               #                             , padding = 1)
               )+
    scale_color_manual(
      values = c(
        "Supervised" = "#f8766d",
        "Unsupervised" = "#619cff",
        "Baseline" = "#00ba38"
      )) +
  scale_fill_manual(
      values = c(
        "Supervised" = "#f8766d",
        "Unsupervised" = "#619cff",
        "Baseline" = "#00ba38"
      )) +
  scale_shape_manual(
      values = c(
        "Supervised" = 15,
        "Unsupervised" = 16,
        "Baseline" = 17
      )) +
    coord_cartesian(ylim = c(min_score, max_score)) +  # ← la bonne méthode
    labs(
      x = "Number of on-detour routers",
      y = TeX("$F_1$-Score")) +
  facet_wrap(~ facet_label, nrow = 3, ncol = 3)+
  theme_minimal(base_size = 20)+
  theme(
    axis.text.x = element_text(angle = 40,  hjust = 1), #vjust = 0.5,
    axis.text.y = element_text(size = 15),
    panel.background = element_rect(fill = "transparent", color = NA),
  plot.background = element_rect(fill = "transparent", color = NA),
  panel.grid.major = element_line(color = "grey", linewidth = 0.1),
  panel.grid.minor = element_line(color = "grey", linewidth = 0.1)
  )
length(unique(plot_flow$seed))
```























