---
title: "Feature analysis — synthesis report"
subtitle: "Detour-attack detection at flow size n = 9"
author: "Anne"
date: today
date-format: "YYYY-MM-DD"
format:
  html:
    toc: true
    toc-depth: 3
    toc-location: left
    code-fold: true
    code-tools: true
    theme: cosmo
    number-sections: true
    fig-width: 10
    fig-height: 6
    df-print: paged
    embed-resources: true
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
#| include: false

setwd("~/Documents/ns-3.45")
# ============================================================
#  USAGE
#  -----
#  1. Run feature_analysis.R first → produces a directory like
#     ./<ipaddr>/_pid<pid>_feature_analysis/ with the CSVs.
#  2. Set `results_dir` below to that directory (or pass it
#     via the environment variable FEATURE_RESULTS_DIR).
#  3. Render :  quarto render feature_analysis_report.qmd
# ============================================================

# --- Configuration : where are the CSVs? ---
results_dir <- "scratch/data/" #Sys.getenv("FEATURE_RESULTS_DIR", unset = "")
if (results_dir == "") {
  # Fallback : auto-detect under the current working directory.
  candidates <- list.dirs(".", recursive = TRUE, full.names = TRUE)
  candidates <- candidates[grepl("_feature_analysis$", candidates)]
  if (length(candidates) > 0) {
    # Pick the most recently modified
    mtimes <- file.info(candidates)$mtime
    results_dir <- candidates[order(mtimes, decreasing = TRUE)][1]
  } else {
    stop("No results directory found. Set FEATURE_RESULTS_DIR or place the report next to the *_feature_analysis/ folder.")
  }
}

stopifnot(dir.exists(results_dir))

# --- Libraries ---
suppressPackageStartupMessages({
  library(data.table)
  library(ggplot2)
  library(knitr)
  library(kableExtra)
  library(scales)
})

theme_set(theme_minimal(base_size = 11))

# --- Helpers ---
read_or_null <- function(name) {
  fp <- file.path(results_dir, name)
  if (!file.exists(fp)) return(NULL)
  fread(fp, sep = ";")
}

# Try the canonical names produced by feature_analysis.R
reliability   <- read_or_null("01_reliability_n9.csv")
discrim       <- read_or_null("02_discrimination.csv")
clusters      <- read_or_null("03_redundancy_clusters.csv")
rf_imp        <- read_or_null("03_redundancy_rf_importance.csv")
mrmr          <- read_or_null("03_redundancy_mrmr.csv")
robust_perscn <- read_or_null("04_robustness_per_scenario.csv")
robust_summ   <- read_or_null("04_robustness_summary.csv")
drift_summ    <- read_or_null("04_drift_summary.csv")
scorecard     <- read_or_null("05_feature_scorecard.csv")
# master_flow_dataset.csv is intentionally NOT loaded here — it can be
# very large (millions of rows) and the synthesis tables don't need it.

# Sanity print - shows up only in dev console
have <- function(x) !is.null(x) && nrow(x) > 0
status_tbl <- data.table(
  artifact = c("reliability", "discrimination", "clusters",
               "rf_importance", "mrmr", "robustness_per_scenario",
               "robustness_summary", "drift_summary", "scorecard"),
  rows = c(
    if (have(reliability))   nrow(reliability)   else 0L,
    if (have(discrim))       nrow(discrim)       else 0L,
    if (have(clusters))      nrow(clusters)      else 0L,
    if (have(rf_imp))        nrow(rf_imp)        else 0L,
    if (have(mrmr))           nrow(mrmr)           else 0L,
    if (have(robust_perscn)) nrow(robust_perscn) else 0L,
    if (have(robust_summ))   nrow(robust_summ)   else 0L,
    if (have(drift_summ))    nrow(drift_summ)    else 0L,
    if (have(scorecard))     nrow(scorecard)     else 0L
  )
)
```

::: {.callout-note collapse="true"}
## Source data

```{r show-status}
status_tbl[, status := ifelse(rows > 0, "✓ loaded", "✗ missing")]
kable(status_tbl, caption = paste0("Files read from `", results_dir, "`"))
```
:::

# Executive summary

```{r exec-summary}
#| results: asis

if (!have(scorecard)) {
  cat("**No scorecard available.** The synthesis tables below cannot be produced. Re-run `feature_analysis.R` first.\n")
} else {
  n_total <- nrow(scorecard)
  n_with_score <- scorecard[is.finite(global_score), .N]
  med_score <- scorecard[is.finite(global_score), median(global_score)]
  q3_score <- scorecard[is.finite(global_score), quantile(global_score, 0.75)]
  n_top <- scorecard[is.finite(global_score) & global_score >= q3_score, .N]
  n_clusters <- if (have(clusters)) uniqueN(clusters$cluster_id) else NA_integer_
  n_reps <- if (have(clusters)) clusters[is_cluster_rep == TRUE, .N] else NA_integer_

  cat(sprintf(
"- **%d candidate features** evaluated; **%d** have a finite global score.\n",
    n_total, n_with_score))
  cat(sprintf(
"- Median global score: **%.2f**, top quartile threshold: **%.2f** (top %d features).\n",
    med_score, q3_score, n_top))
  if (!is.na(n_clusters)) {
    cat(sprintf(
"- Redundancy clustering identifies **%d clusters** at |Spearman| > 0.8 → **%d cluster representatives**.\n",
      n_clusters, n_reps))
  }
}
```

::: {.callout-warning}
## Read this first

The composite score is a **decision aid**, not the decision itself.
A high score on six aggregated indicators may still hide a feature that
is degenerate in a specific scenario or that overlaps strongly with a
better-ranked sibling. Always cross-check with the per-pillar tables
below before defending a feature in the manuscript.
:::

# Pillar 1 — Reliability at flow size 9

The first criterion is whether each candidate is **definable** and
**stable** when computed over a flow of nine packets. Two diagnostics
are reported : the fraction of flows on which the feature is `NA`
(definition rate) and the inter-flow coefficient of variation within
the benign class, aggregated across scenarios.

```{r p1-table}
#| eval: !expr "have(reliability)"

p1 <- copy(reliability)
p1[, na_rate_pct := scales::percent(na_rate, accuracy = 0.1)]
p1[, cv_str := sprintf("%.2f [%.2f, %.2f]",
                        cv_median,
                        cv_q25, cv_q75)]
p1_view <- p1[, .(feature, na_rate_pct, cv_str, cv_max, n_scen_ok)]
setnames(p1_view, c("Feature", "NA rate", "CV median [Q1, Q3]",
                    "CV max", "N scen"))
setorder(p1_view, -.I)  # keep file order
kable(p1_view, caption = "Reliability — sorted as in source file (best first).") |>
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE, font_size = 11) |>
  row_spec(which(p1$na_rate >= 0.5), background = "#fde2e1") |>
  row_spec(which(p1$cv_median > 1 & is.finite(p1$cv_median)), background = "#fff3cd")
```

```{r p1-flagged, results='asis'}
#| eval: !expr "have(reliability)"

flag_na   <- reliability[na_rate >= 0.5, feature]
flag_cv   <- reliability[is.finite(cv_median) & cv_median > 1 &
                          !(feature %in% flag_na), feature]

cat("**Features with NA rate ≥ 50 %** — *eliminated by the implicit filter in `mix_to_flow_fast`* :\n\n")
if (length(flag_na) == 0) {
  cat("- (none)\n")
} else {
  cat(paste0("- `", flag_na, "`\n", collapse = ""))
}

cat("\n**Features with high inter-flow CV (> 1)** — defined but noisy at n = 9 :\n\n")
if (length(flag_cv) == 0) {
  cat("- (none)\n")
} else {
  cat(paste0("- `", flag_cv, "`\n", collapse = ""))
}
```

```{r p1-plot}
#| eval: !expr "have(reliability)"
#| fig-cap: "Reliability map. Top-right region (low NA, low CV) is the safe zone."

ggplot(reliability, aes(x = na_rate, y = pmin(cv_median, 5, na.rm = TRUE))) +
  geom_point(alpha = 0.7, size = 2.5) +
  geom_text(aes(label = feature),
            check_overlap = TRUE, vjust = -0.6, size = 2.5) +
  geom_vline(xintercept = 0.5, color = "red", linetype = "dashed") +
  geom_hline(yintercept = 1.0, color = "orange", linetype = "dashed") +
  labs(x = "NA rate (proportion of flows where the feature is NA)",
       y = "Inter-flow CV (median across scenarios, capped at 5)",
       caption = "Red line: NA filter (≥0.5 → dropped). Orange line: CV = 1 threshold.")
```

::: {.callout-tip collapse="true"}
## What "low CV" means here

The CV is computed within the **benign class** at each fixed scenario
and then aggregated. Within a fixed scenario, the benign distribution
should be tight; a high CV signals that the feature itself injects a
lot of noise even when nothing is happening on the network. That noise
will limit any classifier built on top.
:::

# Pillar 2 — Class separability

For each feature, four marginal indicators of separation between
benign and detoured flows are computed on the pooled, multi-scenario
data : univariate AUC, Mann–Whitney p-value, Cliff's δ effect size, and
mutual information.

```{r p2-table}
#| eval: !expr "have(discrim)"

p2 <- copy(discrim)
setorder(p2, -auc_abs)
p2[, auc_str := sprintf("%.3f", auc_abs)]
p2[, mw_str := scales::pvalue(mw_p, accuracy = 1e-4)]
p2[, cliff_str := sprintf("%.3f", cliff_d)]
p2[, ks_str := sprintf("%.3f", ks_stat)]
p2[, mi_str := sprintf("%.3f", mi)]
p2_view <- p2[, .(feature, n_obs, auc_str, mw_str, cliff_str, ks_str, mi_str)]
setnames(p2_view,
         c("Feature", "N obs", "|AUC-0.5|+0.5", "MW p-value",
           "Cliff's δ", "KS stat", "MI"))
kable(p2_view,
      caption = "Discrimination indicators — sorted by descending AUC.") |>
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE, font_size = 11)
```

```{r p2-thresholds, results='asis'}
#| eval: !expr "have(discrim)"

q_auc_strong <- discrim[is.finite(auc_abs) & auc_abs >= 0.70, feature]
q_auc_weak   <- discrim[is.finite(auc_abs) & auc_abs <  0.55, feature]

cat("**Strong discriminators (|AUC-0.5|+0.5 ≥ 0.70) :**\n\n")
if (length(q_auc_strong) == 0) {
  cat("- (none — feature set is weak in marginal terms)\n")
} else {
  cat(paste0("- `", q_auc_strong, "`\n", collapse = ""))
}

cat("\n**Marginally indistinguishable from noise (|AUC-0.5|+0.5 < 0.55) :**\n\n")
if (length(q_auc_weak) == 0) {
  cat("- (none)\n")
} else {
  cat(paste0("- `", q_auc_weak, "`\n", collapse = ""))
}
```

```{r p2-plot}
#| eval: !expr "have(discrim)"
#| fig-cap: "Top-15 features by univariate AUC. Cliff's δ is shown as a colour to flag direction (positive = higher in attacked, negative = lower)."

top15 <- discrim[is.finite(auc_abs)][order(-auc_abs)][1:min(15, .N)]
ggplot(top15, aes(x = auc_abs, y = reorder(feature, auc_abs),
                  fill = cliff_d)) +
  geom_col() +
  scale_fill_gradient2(low = "#3a86ff", mid = "white", high = "#d62828",
                        midpoint = 0, name = "Cliff's δ") +
  geom_vline(xintercept = 0.5, color = "grey50") +
  geom_vline(xintercept = 0.7, color = "red", linetype = "dashed") +
  labs(x = "|AUC - 0.5| + 0.5", y = NULL,
       caption = "Dashed line at 0.7 marks a common 'usable feature' threshold.")
```

::: {.callout-warning}
## A high AUC alone is not enough

A feature can have a high pooled AUC because it perfectly separates
classes in a small subset of scenarios and is uninformative everywhere
else. Pillar 4 (cross-scenario robustness) is the corrective lens for
this : compare the per-feature AUC distribution across scenarios in
section 5 below.
:::

# Pillar 3 — Non-redundancy

Three complementary views of redundancy are presented : hierarchical
clustering on Spearman correlation, Random-Forest variable importance,
and a greedy mRMR ranking.

## Redundancy clusters

```{r p3a-clusters}
#| eval: !expr "have(clusters)"

clusters_view <- copy(clusters)
clusters_view[, label := ifelse(is_cluster_rep, paste0("**", feature, "**"), feature)]

# Per cluster, list members with the representative bolded
cluster_summary <- clusters_view[, .(
  size = .N,
  members = paste(label[order(-auc_abs)], collapse = ", "),
  best_auc = max(auc_abs, na.rm = TRUE)
), by = cluster_id][order(-size, -best_auc)]

cluster_summary[, best_auc := sprintf("%.3f", best_auc)]
setnames(cluster_summary,
         c("Cluster ID", "Size", "Members (rep. in **bold**)", "Best AUC"))
kable(cluster_summary,
      caption = "Redundancy clusters at |Spearman| > 0.8. The bolded feature in each row is the cluster representative selected on the basis of best univariate AUC.",
      escape = FALSE) |>
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE, font_size = 10)
```

```{r p3a-singletons, results='asis'}
#| eval: !expr "have(clusters)"

n_singleton <- clusters[, .N, by = cluster_id][N == 1, .N]
n_total_cl <- uniqueN(clusters$cluster_id)
cat(sprintf(
"Among %d clusters, **%d are singletons** (= features with no near-duplicate). The %d non-singleton clusters concentrate the redundancy of the candidate set.\n",
  n_total_cl, n_singleton, n_total_cl - n_singleton))
```

## Random-Forest importance

```{r p3b-rf}
#| eval: !expr "have(rf_imp)"

rf_view <- copy(rf_imp)
setorder(rf_view, -MeanDecreaseGini)
rf_top <- rf_view[1:min(20, .N)]
ggplot(rf_top, aes(x = MeanDecreaseGini, y = reorder(feature, MeanDecreaseGini))) +
  geom_col(fill = "#06a77d") +
  labs(x = "Mean Decrease in Gini", y = NULL,
       title = "Top 20 features by Random-Forest variable importance")
```

```{r p3b-cross}
#| eval: !expr "have(rf_imp) && have(discrim)"

# Compare RF importance vs univariate AUC
cmp <- merge(rf_imp[, .(feature, MeanDecreaseGini)],
             discrim[, .(feature, auc_abs)], by = "feature")
ggplot(cmp, aes(x = auc_abs, y = MeanDecreaseGini, label = feature)) +
  geom_point(alpha = 0.6) +
  geom_text(check_overlap = TRUE, size = 2.5, vjust = -0.6) +
  labs(x = "|AUC - 0.5| + 0.5  (univariate)",
       y = "Mean Decrease Gini  (multivariate)",
       title = "Univariate vs multivariate informativeness",
       caption = "Top-right = strong both ways. Bottom-right = univariately strong, redundant in RF. Top-left = weak alone but useful in interaction.")
```

## mRMR greedy ranking

```{r p3c-mrmr}
#| eval: !expr "have(mrmr)"

mrmr_view <- copy(mrmr)
mrmr_view[, score := sprintf("%.3f", score)]
mrmr_view[, mi_y  := sprintf("%.3f", mi_y)]
mrmr_view[, mean_redundancy := sprintf("%.3f", mean_redundancy)]
setnames(mrmr_view,
         c("Rank", "Feature", "mRMR score", "MI(f, y)", "Mean redundancy"))
kable(mrmr_view,
      caption = "mRMR greedy ranking — higher rank = added latest = lower marginal contribution.") |>
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE, font_size = 11)
```

::: {.callout-tip collapse="true"}
## How to read the three views together

A feature that is :

- a **cluster representative** AND
- in the **RF top-15** AND
- in the **mRMR top-15**

is a strong candidate for retention. A feature that fails any one of the
three deserves a closer look : it may be useful in interaction (RF picks
it but mRMR doesn't, because mRMR uses marginal MI), or it may be a
redundant sibling of a slightly better feature (cluster non-rep but high
RF importance).
:::

# Pillar 4 — Cross-scenario robustness

The discrimination obtained on pooled data may collapse outside the
parameter region in which it was measured. Below we report, for each
feature : the median AUC across scenarios, the relative variability of
that AUC, and the fraction of scenarios where AUC ≥ 0.7.

## Per-feature summary

```{r p4-summary}
#| eval: !expr "have(robust_summ)"

robust_view <- copy(robust_summ)
setorder(robust_view, -auc_dist_median)
robust_view[, auc_med_str := sprintf("%.3f", auc_median)]
robust_view[, auc_dist_str := sprintf("%.3f", auc_dist_median)]
robust_view[, cv_str := sprintf("%.2f",
                                  ifelse(is.finite(auc_dist_cv),
                                         auc_dist_cv, NA))]
robust_view[, frac_str := scales::percent(frac_auc_ge_07, accuracy = 1)]
robust_view_show <- robust_view[, .(feature, n_scen, auc_med_str,
                                     auc_dist_str, cv_str, frac_str)]
setnames(robust_view_show,
         c("Feature", "N scen", "AUC median", "|AUC-0.5| median",
           "CV(|AUC-0.5|)", "Frac. AUC ≥ 0.7"))
kable(robust_view_show,
      caption = "Cross-scenario AUC summary — sorted by descending median |AUC-0.5|.") |>
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE, font_size = 11)
```

## Per-scenario heatmap (top features)

```{r p4-heatmap}
#| eval: !expr "have(robust_perscn) && have(discrim)"
#| fig-height: 8

# Restrict to the 25 best pooled-AUC features for legibility
top25_feats <- discrim[is.finite(auc_abs)][order(-auc_abs)][1:min(25, .N), feature]
hm <- robust_perscn[feature %in% top25_feats]
hm[, feature := factor(feature, levels = top25_feats)]

ggplot(hm, aes(x = scenario_id, y = feature, fill = auc_scen)) +
  geom_tile(color = "white", linewidth = 0.1) +
  scale_fill_gradient2(low = "#3a86ff", mid = "white", high = "#d62828",
                        midpoint = 0.5, limits = c(0, 1),
                        na.value = "grey85", name = "AUC") +
  labs(x = "Scenario", y = NULL,
       title = "Per-scenario AUC for the 25 best pooled features",
       caption = "Grey cells = AUC undefined (not enough data). Blue/red asymmetry around 0.5 reveals scenarios where the feature inverts its discriminative direction.") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 6),
        axis.text.y = element_text(size = 7))
```

## Distributional drift vs baseline

```{r p4-drift}
#| eval: !expr "have(drift_summ)"

drift_view <- copy(drift_summ)
setorder(drift_view, -drift_median)
drift_view[, drift_med_str := sprintf("%.3f", drift_median)]
drift_view[, drift_max_str := sprintf("%.3f", drift_max)]
drift_view_show <- drift_view[, .(feature, drift_med_str, drift_max_str)]
setnames(drift_view_show,
         c("Feature", "Drift median", "Drift max"))

# Show top 10 drift only
kable(drift_view_show[1:min(10, .N)],
      caption = "10 features with the largest distributional drift between baseline and other scenarios. High drift = the feature's distribution moves a lot when network parameters change.") |>
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE, font_size = 11)
```

::: {.callout-important}
## Drift is double-edged

A high drift on a discriminative feature means the **decision boundary
moves with the scenario**. Two consequences :

- if the model is trained on one regime and deployed on another (the
  *evolution* mode in your pipeline), it will likely fail on this
  feature unless retraining is triggered;
- in supervised mode, drift correlates with leakage of the
  parasite-rate / hop / detour parameters into the feature itself,
  which is fine for in-distribution accuracy but inflates the apparent
  performance.
:::

# Composite scorecard

```{r scorecard-top}
#| eval: !expr "have(scorecard)"

sc <- copy(scorecard)
setorder(sc, -global_score)

# Top 25 view
sc_view <- sc[1:min(25, .N)]
fmt2 <- function(x) ifelse(is.finite(x), sprintf("%.2f", x), "—")
sc_view[, `:=`(
  rel  = fmt2(rel_score),
  cv   = fmt2(cv_score),
  disc = fmt2(disc_score),
  rf   = fmt2(rf_score),
  rob  = fmt2(rob_score),
  drift = fmt2(drift_score),
  global = fmt2(global_score)
)]

sc_show <- sc_view[, .(feature, rel, cv, disc, rf, rob, drift, global,
                        cluster_id, is_cluster_rep)]
setnames(sc_show,
         c("Feature", "Reliability", "CV-stability", "Discrimination",
           "RF importance", "Robustness", "Drift", "Global",
           "Cluster", "Rep ?"))

kable(sc_show,
      caption = "Top 25 features by composite global score.") |>
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE, font_size = 10) |>
  row_spec(which(sc_view$is_cluster_rep), background = "#e8f5e8")
```

```{r scorecard-distrib}
#| eval: !expr "have(scorecard)"
#| fig-cap: "Distribution of the global score over all candidates."

ggplot(scorecard[is.finite(global_score)],
       aes(x = global_score)) +
  geom_histogram(bins = 30, fill = "#3a86ff", alpha = 0.7,
                  color = "white") +
  geom_vline(xintercept = quantile(scorecard$global_score, 0.75,
                                   na.rm = TRUE),
              color = "red", linetype = "dashed") +
  labs(x = "Global score", y = "Count",
       caption = "Red line = top quartile threshold.")
```

# Recommended retention list

The following synthesis is automatically derived from the four pillars
and the redundancy clusters. **It is a proposal, not a final list :
review each line before committing it to the manuscript.**

```{r retention-rule}
#| eval: !expr "have(scorecard)"

# Decision rule (explicit and conservative) :
#   RETAIN if :
#     - is_cluster_rep == TRUE     (no near-duplicate ranks higher)
#     - na_rate < 0.5              (definable on most flows at n=9)
#     - cv_median < 1.5            (sampling noise under control)
#     - disc_score >= 0.10         (i.e. |AUC-0.5| >= 0.05 — minimal)
#     - rob_score >= 0.30          (works in at least 30 % of scen.)
#     - global_score >= median     (above-median composite)
#
#   FLAG (review) if :
#     - is_cluster_rep == FALSE but rf_score >= 0.50  (interaction)
#     - high disc but high drift (scenario-specific)
#
#   DROP otherwise.

med_global <- scorecard[is.finite(global_score), median(global_score)]

# scorecard already contains na_rate, cv_median, auc_abs, etc.
# (cf. feature_analysis.R lines 583-599). No merge needed.
ret <- copy(scorecard)

ret[, decision := fcase(
  is_cluster_rep == TRUE
    & is.finite(na_rate) & na_rate < 0.5
    & is.finite(cv_median) & cv_median < 1.5
    & is.finite(disc_score) & disc_score >= 0.10
    & is.finite(rob_score) & rob_score >= 0.30
    & is.finite(global_score) & global_score >= med_global,
  "RETAIN",
  is.finite(rf_score) & rf_score >= 0.50,
  "REVIEW (interaction)",
  is.finite(disc_score) & is.finite(drift_score) & disc_score >= 0.30 & drift_score < 0.30,
  "REVIEW (drift)",
  default = "DROP"
)]

setorder(ret, decision, -global_score)
ret_show <- ret[, .(feature, decision, global_score, cluster_id,
                     is_cluster_rep, na_rate, cv_median,
                     auc_abs, rob_score, drift_score)]
ret_show[, `:=`(
  global_score = sprintf("%.2f", global_score),
  na_rate = scales::percent(na_rate, accuracy = 0.1),
  cv_median = sprintf("%.2f", cv_median),
  auc_abs = sprintf("%.3f", auc_abs),
  rob_score = sprintf("%.2f", rob_score),
  drift_score = sprintf("%.2f", drift_score)
)]
setnames(ret_show,
         c("Feature", "Decision", "Score", "Cluster", "Rep ?",
           "NA rate", "CV median", "AUC", "Robustness", "Drift score"))

kable(ret_show, caption = "Retention proposal. Adjust thresholds in the chunk above to align with your manuscript's selection criteria.") |>
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE, font_size = 10) |>
  row_spec(which(ret$decision == "RETAIN"), background = "#d4edda") |>
  row_spec(which(grepl("REVIEW", ret$decision)), background = "#fff3cd") |>
  row_spec(which(ret$decision == "DROP"), background = "#fde2e1")
```

```{r retention-summary, results='asis'}
#| eval: !expr "have(scorecard)"

cnt <- ret[, .N, by = decision]
cat("**Decision counts :**\n\n")
for (i in seq_len(nrow(cnt))) {
  cat(sprintf("- %s : **%d**\n", cnt$decision[i], cnt$N[i]))
}
```

::: {.callout-warning}
## Decision rule transparency

The decision rule used to fill the *Decision* column is **explicit and
visible in the source of this report** (`retention-rule` chunk). Modify
the thresholds in that chunk if your manuscript uses different ones,
then re-render. Do **not** copy the table into the manuscript without
re-reading the rule alongside it.
:::

# Cross-checks against the manuscript's current Table 3.1

The current Section 3.2 of the manuscript declares a feature set used
by REG_LOG, SVM, VAE and DAE. The following table flags the features
that the present analysis would mark as problematic at flow size 9.

```{r manuscript-crosscheck, results='asis'}
#| eval: !expr "have(reliability) && have(robust_summ)"

# Features declared in Table 3.1 of the manuscript (for n = 9 review)
table31_features <- c(
  "fmedian_delay", "fmad_delay", "fIQR_delay", "fCV_delay",
  "fQ095_delay", "fQ095_Q005", "fmeanTRIM10_delay",
  "fMASD_delay", "fRMSJ_delay", "fsd_diff_delay",
  "fIPDV_pos_delay", "fIPDV_neg_delay",
  paste0("facf_lag", 0:10), "fACF_sum",
  "fslope_t", "fCUSUM_max", "fearly_diff",
  "alpha_hat", "beta_hat", "r2", "sigma_eps",
  "rho_tilde", "lambda_hat",
  "fkurtosis_delay", "fskew_delay", "fhill",
  "delay", "flow_size",
  "fmean_delay", "t_start", "t_end",
  "duty", "run_max",
  "d_alpha", "d_masd", "d_cv", "d_beta",
  "fsd_delay", "fQ005_delay", "fmin_delay", "fmax_delay",
  "fSpec_peak_freq", "fSpec_entropy"
)

flag_dt <- merge(
  data.table(feature = table31_features),
  reliability[, .(feature, na_rate, cv_median)],
  by = "feature", all.x = TRUE
)
if (have(robust_summ)) {
  flag_dt <- merge(flag_dt,
                    robust_summ[, .(feature, frac_auc_ge_07)],
                    by = "feature", all.x = TRUE)
} else {
  flag_dt[, frac_auc_ge_07 := NA_real_]
}

flag_dt[, manuscript_status := fcase(
  is.na(na_rate),
  "❌ NOT IN OUTPUT (check feature name)",
  na_rate >= 0.5,
  "❌ NA-eliminated at n = 9",
  is.finite(cv_median) & cv_median > 2,
  "⚠ very noisy at n = 9",
  is.finite(frac_auc_ge_07) & frac_auc_ge_07 < 0.1,
  "⚠ rarely useful across scenarios",
  default = "✓ ok"
)]

problems <- flag_dt[manuscript_status != "✓ ok"]
if (nrow(problems) == 0) {
  cat("\n✅ All features declared in Table 3.1 pass the basic sanity checks at n = 9. No correction required.\n")
} else {
  problems[, na_rate_str := scales::percent(na_rate, accuracy = 0.1)]
  problems[, cv_str := sprintf("%.2f", cv_median)]
  problems[, frac_str := scales::percent(frac_auc_ge_07, accuracy = 1)]
  problems_show <- problems[, .(feature, manuscript_status,
                                 na_rate_str, cv_str, frac_str)]
  setnames(problems_show,
           c("Feature in Table 3.1", "Status", "NA rate",
             "CV median", "Frac AUC ≥ 0.7"))
  print(kable(problems_show,
              caption = "Features in the manuscript's Table 3.1 that fail one of the n=9 sanity checks.") |>
        kable_styling(bootstrap_options = c("striped", "hover"),
                      full_width = FALSE, font_size = 11))
}
```

# Reproducibility

```{r repro}
#| results: asis

cat("- **Results directory :** `", results_dir, "`\n", sep = "")
cat("- **Quarto file :** ", knitr::current_input(dir = TRUE), "\n", sep = "")
cat("- **Rendered on :** ", format(Sys.time(), "%Y-%m-%d %H:%M:%S %Z"), "\n", sep = "")
cat("- **R version :** ", R.version.string, "\n", sep = "")
```

```{r session-info}
#| code-fold: true

sessionInfo()
```
